---
title: |
  List of Empirical Results:
  "Tax-Price Elasticities of Charitable Giving and Selection of Declaration:
  Panel Study of South Korea"
author:
  - Hiroki Kato
  - Tsuyoshi Goto
  - Youngrok Kim
output:
  bookdown::pdf_document2:
    latex_engine: pdflatex
    keep_tex: false
    toc: false
    extra_dependencies: ["here"]
base-strech: 1.5
fontsize: 12pt
---

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  error = FALSE,
  message = FALSE,
  dev = "pdf",
  fig.pos = "H",
  fig.width = 10,
  fig.height = 5,
  out.extra = ""
)

options(
  knitr.table.format = "latex",
  knitr.kable.NA = "",
  modelsummary_stars_note = FALSE,
  modelsummary_factory_default = "latex"
)
```

```{r library, include=FALSE}
library(here)
source(here("R/R6_StartAnalysis.r"))
```

```{r data, include=FALSE}
rawdt <- read_csv(here("data/shaped2.csv")) %>%
  employee() %>%
  donut_hole(cut = 50) %>%
  log_inc()

dt <- rawdt %>%
  remove_highest_bracket() %>%
  set_donate_bound()
```

```{r write-dta, include=FALSE, eval=FALSE}
library(readstata13)
save.dta13(
  rawdt,
  file = here("stata/rawdata.dta"),
  version = 16,
  convert.factors = FALSE
)
```

\clearpage
# Data
\clearpage

```{r summary-class, include=FALSE}
main <- StartAnalysis$new(dt)
data_summary <- main$summary()
```

```{r summary-covariate}
# [Paper] Table 2
tab <- data_summary$stats(
  title = "Descriptive Statistics",
  notes = "Notes: Our data is unbalanced panel data consisting of 4,422 unique individuals and 8 years period (2010--2017). The number of dependents in household do not include the number of children."
)

tab

out.file <- file(here("export", "tables", "summary-stats.tex"), open = "w")
writeLines(tab, out.file)
close(out.file)
```

```{r figure1, fig.cap="Income Distribution in 2013 and Relative Giving Price"}
# [Paper] Figure 1
data_summary$income_dist()

ggsave(
  here("export", "figures", "price-income-dist.pdf"),
  width = 10,
  height = 6
)
```

```{r figure2, fig.cap = "Average Givine Amount and Proportion of Donors"}
# [Paper] Figure 2
data_summary$ts_giving()

ggsave(
  here("export", "figures", "intensive-extensive-tax-reform.pdf"),
  width = 10,
  height = 6
)
```

```{r level-giving}
plot_data <- data_summary$data %>%
  dplyr::filter(!is.na(bracket13)) %>%
  mutate(bracket13 = if_else(
    str_detect(bracket13, "C|D|E"),
    "(C), (D) and (E) [4600, 30000)",
    bracket13
  )) %>%
  group_by(year, bracket13) %>%
  summarize(
    amount = mean(donate, na.rm = TRUE),
    donor = mean(d_donate * 100, na.rm = TRUE)
  )

plot_data %>%
  ggplot(aes(x = year, y = amount, group = bracket13)) +
  geom_vline(aes(xintercept = 2013.5), linetype = 3) +
  geom_point(aes(shape = bracket13), size = 4) +
  geom_line() +
  scale_shape_manual(values = c(16, 15, 17, 18)) +
  scale_x_continuous(breaks = seq(2010, 2018, 1)) +
  # scale_y_continuous(breaks = seq(-30, 20, by = 10), limits = c(-30, 20)) +
  labs(
    title = "Panel A. Amount of Giving",
    x = "Year",
    y = "Average giving(unit: 10,000KRW)",
    shape = "Income bracket (unit: 10,000KRW)"
  ) +
  ggtemp(size = list(axis_title = 15, axis_text = 13, title = 13))

ggsave(
  here("not-for-pub", "figures", "level-intensive-extensive-tax-reform.pdf"),
  width = 10,
  height = 6
)
```

```{r figureA1, fig.cap = "Event-study Analysis (Wage Earners)"}
# [Supplementary Material A] Figure A1
data_summary$event_study(include_pid = TRUE)

ggsave(
  here("export", "figures", "event-study.pdf"),
  width = 10,
  height = 6
)
```

```{r figure3, fig.cap = "Proportion Having Applied for Tax Incentives"}
# [Paper] Figure 3
data_summary$ts_claim()

ggsave(
  here("export", "figures", "summary-tax-relief.pdf"),
  width = 10,
  height = 6
)
```

```{r figureA2, fig.cap = "Proportion Having Applied for Tax Incentives"}
# [Supplementary Material A] Figure A2
data_summary$ts_claim(d_donate == 1)

ggsave(
  here("export", "figures", "summary-tax-relief-cond-donors.pdf"),
  width = 10,
  height = 6
)
```

```{r normalize-ts-claim}
plot_data <- data_summary$data %>%
  # dplyr::filter(d_donate == 1) %>%
  dplyr::filter(!is.na(bracket13)) %>%
  mutate(bracket13 = if_else(
    str_detect(bracket13, "C|D|E"),
    "(C), (D) and (E) [4600, 30000)",
    bracket13
  )) %>%
  group_by(year, bracket13) %>%
  summarize(mu = mean(d_relief_donate * 100, na.rm = TRUE)) %>%
  pivot_wider(names_from = year, values_from = mu) %>%
  mutate(base = `2013`) %>%
  select(bracket13, base, everything()) %>%
  pivot_longer(-(bracket13:base), names_to = "year", values_to = "mu") %>%
  mutate(
    mu = mu - base,
    year = as.numeric(year)
  )

plot_data %>%
  ggplot(aes(x = year, y = mu, group = bracket13)) +
  geom_vline(aes(xintercept = 2013.5), linetype = 3) +
  geom_point(aes(shape = bracket13), size = 4) +
  geom_line() +
  scale_shape_manual(values = c(16, 15, 17, 18)) +
  scale_x_continuous(breaks = seq(2010, 2018, 1)) +
  scale_y_continuous(limits = c(-30, 10), breaks = seq(-30, 10, by = 10)) +
  labs(
    x = "Year",
    y = "Normalized Proportion of claimants\n(unit: percent change)",
    shape = "Income bracket (unit:10,000KRW)"
  ) +
  ggtemp(size = list(axis_title = 15, axis_text = 13, title = 13)) +
  guides(shape = guide_legend(title.position = "top", title.hjust = 0.5))
```

```{r donor-ts-pattern}
lead_dt <- main$data %>%
  dplyr::filter(year >= 2013) %>%
  group_by(pid) %>%
  arrange(year) %>%
  mutate(
    l_claim = if_else(year - lead(year) > 1, NA_real_, lead(d_relief_donate)),
    l_d_donate = if_else(year - lead(year) > 1, NA_real_, lead(d_donate))
  ) %>%
  ungroup()

pattern_summary <- lead_dt %>%
  dplyr::filter(year == 2013) %>%
  dplyr::filter(
    !is.na(d_relief_donate) & !is.na(l_claim) &
    !is.na(d_donate) & !is.na(l_d_donate)
  ) %>%
  dplyr::filter(str_detect(bracket13, "A")) %>%
  group_by(d_donate, l_d_donate) %>%
  summarize(
    n = n(),
    mu_claim0 = mean(d_relief_donate),
    mu_claim1 = mean(l_claim)
  )

pattern_summary %>%
  knitr::kable(
    col.names = c("2013", "2014", "N", "2013", "2014"),
    digits = 3,
    align = "ccccc"
  ) %>%
  kableExtra::kable_styling() %>%
  add_header_above(c("Donate or not" = 2, " " = 1, "Mean Report" = 2)) %>%
  footnote(
    general_title = "",
    general = "Notes: We use wage earners whose donation status and reporting status are observed in both 2013 and 2015 in income bracket (A), where taxable income is between 0 and 12 million KRW.",
    threeparttable = TRUE,
    escape = FALSE
  )
```

\clearpage
# Results
## Estimation Results
\clearpage

```{r first-price-class, include=FALSE}
fp_main <- main$first_price()
```

```{r main-stage1}
# [Supplementary Material A] Table A1
tab <- fp_main$stage1(
  title = "First-Stage Models",
  notes = "Notes: * $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$. Standard errors clustered at household level are in parentheses. We only use wage earners. The outcome variable is the logged value of the actual price. In addition to logged income shown in table, covariates consist of squared age (divided by 100), number of household members, number of children, number of dependents, a dummy that indicates the highest income in a household, a dummy that indicates that a taxpayer is household head, a dummy that indicates a wage earner, a set of industry dummies, a set of residential area dummies, and individual and time fixed effects. The excluded instrument is the logged value of simulated price."
)

tab

out.file <- file(here("export", "tables", "main-stage1.tex"), open = "w")
writeLines(tab, out.file)
close(out.file)
```

```{r main}
# [Paper] Table 3
tab <- fp_main$stage2(
  title = "Estimation Results of First-Price Elasticities",
  notes = "Notes: * $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$. Standard errors clustered at the household level are in parentheses. We only use wage earners. In column (1)--(3), an outcome variable is the transformed logged value of donation, which is defined as $\\\\log(\\\\tilde{g})$ for $g > 0$ and $-1$ for $g=0$, where $\\\\tilde{g}=g/\\\\min_{g>0}[g]$. The value of the minimum nonzero donation, $\\\\min_{g>0}[g]$, in our data is 2,000KRW. In column (4)--(6), an outcome variable is an indicator of donor. In addition to logged income, covariates consist of squared age (divided by 100), number of household members, number of children, number of dependents, a dummy that indicates the highest income in a household, a dummy that indicates that a taxpayer is household head, a set of industry dummies, a set of residential area dummies, and individual and time fixed effects. The excluded instrument is a logged value of simulated price in columns (3) and (6). To obtain the extensive-margin price elasticities in columns (4)--(6), we calculate implied price elasticities by dividing the estimated coefficient on price by the sample proportion of donors."
)

tab

out.file <- file(here("export", "tables", "main.tex"), open = "w")
writeLines(tab, out.file)
close(out.file)
```

```{r sufficient-stats}
tab <- fp_main$sufficient_stats(
  title = "Overall Price Elasticities Using Extensive-Margin Elasticities",
  notes = "Notes: * $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$. Standard errors clustered at the household level are in parentheses. We only use wage earners. An outcome variable is the transformed logged value of donation, which is defined as $\\\\log(\\\\tilde{g})$ for $g > 0$ and $-x$ for $g=0$, where $\\\\tilde{g}=g/\\\\min_{g>0}[g]$ and $x$ is absolute values of extensive-margin elasticities. Covariates consist of logged disposal income, squared age (divided by 100), number of household members, number of children, number of dependents, a dummy that indicates the highest income in a household, a dummy that indicates that a taxpayer is household head, a set of industry dummies, a set of residential area dummies, and individual and time fixed effects. The excluded instrument is a logged value of simulated price in column (2)."
)

tab

out.file <- file(here("export", "tables", "sufficient-stats.tex"), open = "w")
writeLines(tab, out.file)
close(out.file)
```

\clearpage
## Robustness
### Last-Price Elasticities
\clearpage

```{r last-price-class, include=FALSE}
lp <- main$last_price()
```

```{r last-overall}
# [Supplementary Material D] Table D1
tab <- lp$overall(
  title = "Last-Price Elasticities for Overall Donations",
  notes = "Notes: * $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$. Standard errors clustered at the household level are in parenthesis. We use only wage earners. an outcome variable is the transformed logged value of donation, which is defined as $\\\\log(\\\\tilde{g})$ for $g > 0$ and $-1$ for $g=0$, where $\\\\tilde{g}=g/\\\\min_{g>0}[g]$. The value of the minimum nonzero donation, $\\\\min_{g>0}[g]$, in our data is 2,000KRW. In addition to logged income, covariates consist of squared age (divided by 100), number of household members, number of children, number of dependents, a dummy that indicates the highest income in a household, a dummy that indicates that a taxpayer is household head, a set of industry dummies, a set of residential area dummies, and individual and time fixed effects. For FE-2SLS, we use the logged value of simulated first-price as an instrument."
)

tab

out.file <- file(here("export", "tables", "last-overall.tex"), open = "w")
writeLines(tab, out.file)
close(out.file)
```

```{r last-ext}
# [Supplementary Material D] Table D2
tab <- lp$extensive(
  title = "Last-Price Elasticities for Extensive-Margin",
  notes = "Notes: * $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$. Standard errors clustered at the household level are in parentheses. We use only wage earners. The outcome variable is a dummy indicating a donor. In addition to logged income, covariates consist of squared age (divided by 100), number of household members, number of children, number of dependents, a dummy that indicates the highest income in a household, a dummy that indicates that a taxpayer is household head, a set of industry dummies, a set of residential area dummies, and individual and time fixed effects. For FE-2SLS, we use the logged value of simulated first-price as an instrument. We calculate implied price elasticities by dividing the estimated coefficient on price by the sample proportion of donors."
)

tab

out.file <- file(here("export", "tables", "last-ext.tex"), open = "w")
writeLines(tab, out.file)
close(out.file)
```

\clearpage
### Remove Price Variation in Income Deduction Period
\clearpage

```{r remove-bracket-shift-data, include=FALSE}
dt2 <- rawdt %>%
  remove_bracket_shift() %>%
  set_donate_bound()

fp_robust1 <- StartAnalysis$new(dt2)$first_price()
```

```{r remove-bracket-shift}
# [Supplementary Material D] Table D3
tab <- fp_robust1$stage2(
  title = "First-Price Elasticities Removing Price Variation in Income Deduction Period",
  notes = "Notes: * $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$. Standard errors clustered at the household level are in parentheses. We use only wage earners. We exclude those whose prices changed during the income deduction period. In column (1)--(3), an outcome variable is the transformed logged value of donation, which is defined as $\\\\log(\\\\tilde{g})$ for $g > 0$ and $-1$ for $g=0$, where $\\\\tilde{g}=g/\\\\min_{g>0}[g]$. The value of the minimum nonzero donation, $\\\\min_{g>0}[g]$, in our data is 2,000KRW. In column (4)--(6), an outcome variable is an indicator of donor. In addition to logged income, covariates consist of squared age (divided by 100), number of household members, number of children, number of dependents, a dummy that indicates the highest income in a household, a dummy that indicates that a taxpayer is household head, a set of industry dummies, a set of residential area dummies, and individual and time fixed effects. The excluded instrument is a logged value of simulated price in columns (3) and (6). To obtain the extensive-margin price elasticities in columns (4)--(6), we calculate implied price elasticities by dividing the estimated coefficient on price by the sample proportion of donors."
)

tab

out.file <- file(here("export", "tables", "remove-bracket-shift.tex"), open = "w")
writeLines(tab, out.file)
close(out.file)
```

\clearpage
### Excluding Announcement Effect
\clearpage

```{r exclude-announcement-effect, include=FALSE}
dt3 <- dt %>%
  remove_around_reform()

fp_robust2 <- StartAnalysis$new(dt3)$first_price()
```

```{r announcement}
# [Supplementary Material D] Table D4
tab <- fp_robust2$stage2(
  title = "First-Price Elasticities Excluding Announcement Effect",
  notes = "Notes: * $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$. Standard errors clustered at the household level are in parentheses. We use only wage earners. To exclude the announcement effect, we exclude observations from 2013 and 2014. In column (1)--(3), an outcome variable is the transformed logged value of donation, which is defined as $\\\\log(\\\\tilde{g})$ for $g > 0$ and $-1$ for $g=0$, where $\\\\tilde{g}=g/\\\\min_{g>0}[g]$. The value of the minimum nonzero donation, $\\\\min_{g>0}[g]$, in our data is 2,000KRW. In column (4)--(6), an outcome variable is an indicator of donor. In addition to logged income, covariates consist of squared age (divided by 100), number of household members, number of children, number of dependents, a dummy that indicates the highest income in a household, a dummy that indicates that a taxpayer is household head, a set of industry dummies, a set of residential area dummies, and individual and time fixed effects. The excluded instrument is a logged value of simulated price in columns (3) and (6). To obtain the extensive-margin price elasticities in columns (4)--(6), we calculate implied price elasticities by dividing the estimated coefficient on price by the sample proportion of donors."
)

tab

out.file <- file(here("export", "tables", "announcement.tex"), open = "w")
writeLines(tab, out.file)
close(out.file)
```

\clearpage
### Changing Extensive-margin Value
\clearpage

```{r ext-margin-value}
# [Supplementary Material D] Table D5
tab <- fp_main$ext_margin_value(
  c(0, 0.5, 3),
  title = "Overall First-Price Elasticities Changing Extensive-Margin Value",
  notes = "Notes: * $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$. Standard errors clustered at the household level are in parentheses. We only use wage earners. An outcome variable is the transformed logged value of donation, which is defined as $\\\\log(\\\\tilde{g})$ for $g > 0$ and $-x$ for $g=0$, where $\\\\tilde{g}=g/\\\\min_{g>0}[g]$. The value of the minimum nonzero donation, $\\\\min_{g>0}[g]$, in our data is 2,000KRW. In addition to logged income, covariates consist of squared age (divided by 100), number of household members, number of children, number of dependents, a dummy that indicates the highest income in a household, a dummy that indicates that a taxpayer is household head, a dummy that indicates a wage earner, a set of industry dummies, a set of residential area dummies, and individual and time fixed effects. The excluded instrument is a logged value of simulated price."
)

tab

out.file <- file(here("export", "tables", "ext-margin-value.tex"), open = "w")
writeLines(tab, out.file)
close(out.file)
```

\clearpage
### Removing Upper Bound of Donation
\clearpage

```{r remove-upper-bound-class, include=FALSE}
dt3 <- rawdt %>% remove_highest_bracket()
fp_robust3 <- StartAnalysis$new(dt3)$first_price()
```

```{r remove-upper-bound}
tab <- fp_robust3$stage2(
  title = "First-Price Elasticities Removing Upper Bound of Donation",
  notes = "Notes: * $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$. Standard errors clustered at the household level are in parentheses. We use only wage earners. We include wage earners those amount of giving is greater than the upper bound of tax incentives (10\\\\% of income). In column (1)--(3), an outcome variable is the transformed logged value of donation, which is defined as $\\\\log(\\\\tilde{g})$ for $g > 0$ and $-1$ for $g=0$, where $\\\\tilde{g}=g/\\\\min_{g>0}[g]$. The value of the minimum nonzero donation, $\\\\min_{g>0}[g]$, in our data is 2,000KRW. In column (4)--(6), an outcome variable is an indicator of donor. In addition to logged income, covariates consist of squared age (divided by 100), number of household members, number of children, number of dependents, a dummy that indicates the highest income in a household, a dummy that indicates that a taxpayer is household head, a set of industry dummies, a set of residential area dummies, and individual and time fixed effects. The excluded instrument is a logged value of simulated price in columns (3) and (6). To obtain the extensive-margin price elasticities in columns (4)--(6), we calculate implied price elasticities by dividing the estimated coefficient on price by the sample proportion of donors."
)

tab

out.file <- file(here("export", "tables", "remove-upper-bound.tex"), open = "w")
writeLines(tab, out.file)
close(out.file)
```

\clearpage
### Tobit Regression
\clearpage

\input{export/tables/tobit.tex}

\clearpage
### Poisson Regression
\clearpage

```{r poisson}
poisson <- list(
  donate ~ applicable + after_tax_tinc_ln + sqage +
    hhnum + hhnum_child + dependent_num +
    hh_max_inc + I(family_position == 1) +
    factor(indust) + factor(area) | pid + year,
  I(1 - d_relief_donate * (1 - price)) ~ applicable + after_tax_tinc_ln + sqage +
    hhnum + hhnum_child + dependent_num +
    hh_max_inc + I(family_position == 1) +
    factor(indust) + factor(area) | pid + year
)

est_poisson <- poisson %>%
  map(~ feglm(., data = fp_main$data, cluster = ~ hhid, family = "poisson"))

est_poisson %>%
  setNames(paste0("(", seq(length(.)), ")")) %>%
  modelsummary(
    title = "Poisson Regression",
    coef_map = c(
      "applicable" = "Simulated price",
      "after_tax_tinc_ln" = "Log disposal income"
    ),
    gof_omit = "R2 Pseudo|R2 Within|AIC|BIC|Log|Std|FE|R2|RMSE",
    stars = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
    escape = FALSE
  ) %>%
  kable_styling(font_size = 9) %>%
  add_header_above(c(" " = 1, "Donation" = 1, "Actual Price" = 1)) %>%
  column_spec(1, width = "20em") %>%
  column_spec(2:3, width = "10em") %>%
  footnote(
    general_title = "",
    general = "Notes: * $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$. Standard errors clustered at the household level are in parentheses. We use only wage earners. In addition to logged income, covariates consist of squared age (divided by 100), number of household members, number of children, number of dependents, a dummy that indicates the highest income in a household, a dummy that indicates that a taxpayer is household head, a set of industry dummies, a set of residential area dummies, and individual and time fixed effects. In column (1), we removed 2,573 individuals (8,372 observations) because we observed only 0 outcomes.",
    threeparttable = TRUE,
    escape = FALSE
  )
```

\clearpage
### Price Elasticity of Expenditure Donation Rates

- Amount of giving: $g(y, p)$, where $p = 1 - Rq$ and $y$ is after-tax income
- Expenditure Donation Rate: $e(y, p) = g(y, p) / y$

\begin{align}
\begin{split}
  &\frac{\partial e(y, p)}{\partial p} \frac{p}{e(y, p)} \\
  =& \left(\frac{1}{y} \frac{\partial g(y, p)}{\partial p} \right)
  \left( p \frac{y}{g(y, p)} \right) \\
  =& \frac{\partial g(y, p)}{\partial p} \frac{p}{g(y, p)} \\
  =& e_A
\end{split}
\end{align}

\clearpage

```{r expenditure-rates}
dt <- fp_main$data
dt$donate_share <- dt$donate / dt$after_tax_tinc
min_donate_share <- with(subset(dt, donate_share > 0), min(donate_share))
dt$donate_share <- dt$donate_share / min_donate_share
dt$donate_share_ln <- ifelse(dt$donate_share == 0, -1, log(dt$donate_share))

mods <- list(
  donate_share_ln ~ applicable + ..stage2,
  donate_share_ln ~ effective + ..stage2,
  donate_share_ln ~ ..stage2 | effective ~ applicable
)

est_mods <- mods %>%
  map(~feols(., data = dt, vcov = ~ hhid))

ivf <- est_mods %>%
  sapply(function(x) get_fitstat(x, "ivf", "stat")) %>%
  sapply(function(x) ifelse(is.na(x), "", sprintf("\\num{%1.3f}", x)))

addtab <- data.frame(rbind(ivf))
addtab <- cbind(
  term = c("F-statistics of instrument"),
  addtab
)

attr(addtab, "position") <- 9

est_mods %>%
  setNames(paste0("(", seq(length(.)), ")")) %>%
  modelsummary(
    title = "Elasticity of Expenditure Ratio",
    coef_map = c(
      "applicable" = "Simulated price ($\\beta_S$)",
      "effective" = "Actual price ($\\beta^{FE}_A$)",
      "fit_effective" = "Actual price ($\\beta^{IV}_A$)",
      "after_tax_tinc_ln" = "Log disposal income"
    ),
    gof_omit = "R2 Pseudo|R2 Within|AIC|BIC|Log|Std|FE|R2|RMSE",
    stars = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
    add_rows = addtab,
    escape = FALSE
  ) %>%
  kable_styling(font_size = 9) %>%
  add_header_above(c(
    " " = 1, "FE" = 2, "FE-2SLS" = 1
  )) %>%
  add_header_above(c(" " = 1, "Log expenditure donation ratio" = 3)) %>%
  group_rows(
    "1st stage information (Excluded instrument: Simulated price)",
    9, 9,
    bold = FALSE, italic = TRUE
  ) %>%
  column_spec(2:4, width = "5em") %>%
  footnote(
    general_title = "",
    general = "Notes: * $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$. Standard errors clustered at the household level are in parentheses. We only use wage earners. In column (1)--(3), an outcome variable is the transformed logged value of expenditure raio of donation, which is defined as $\\\\log(\\\\tilde{e})$ for $e > 0$ and $-1$ for $e=0$, where $\\\\tilde{e}=e/\\\\min_{e>0}[e]$. The value of the minimum nonzero rate, $\\\\min_{e>0}[e]$, in our data is $0.005$%. In addition to logged income, covariates consist of squared age (divided by 100), number of household members, number of children, number of dependents, a dummy that indicates the highest income in a household, a dummy that indicates that a taxpayer is household head, a set of industry dummies, a set of residential area dummies, and individual and time fixed effects. The excluded instrument is a logged value of simulated price in columns (3) and (6).",
    threeparttable = TRUE,
    escape = FALSE
  )
```

\clearpage
## Comparison with Price Elasticities of Reported Giving
\clearpage

```{r reported-donation}
# [Supplementary Material D] Table D6
tab <- fp_main$claimant_only(
  title = "First-Price Elasticities of Reported Donations",
  notes = "Notes: * $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$. Standard errors clustered at the household level are in parentheses. We use only wage earners. An outcome variable is the transformed logged value of the reported donation, which is a product of an indicator of report and an amount of donation and is defined as $\\\\log(R\\\\tilde{g})$ for $Rg > 0$ and $-1$ for $Rg=0$, where $\\\\tilde{g}=g/min_{g>0}[g]$. The value of the minimum nonzero donation, $min_{g>0}[g]$, in our data is 2,000KRW. In addition to logged income, covariates consist of squared age (divided by 100), number of household members, number of children, number of dependents, a dummy that indicates the highest income in a household, a dummy that indicates that a taxpayer is household head, a set of industry dummies, a set of residential area dummies, and individual and time fixed effects."
)

tab

out.file <- file(here("export", "tables", "reported-donation.tex"), open = "w")
writeLines(tab, out.file)
close(out.file)
```

```{r claim-elasticity}
# [Supplementary Material D] Table D7
tab <- fp_main$claim_elasticity(
  title = "First-Price Elasticity of Declaration",
  notes = "Notes: * $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$. Standard errors clustered at the household level are in parentheses. We use only wage earners. The outcome variable is a dummy of report. In addition to logged income, covariates consist of squared age (divided by 100), number of household members, number of children, number of dependents, a dummy that indicates the highest income in a household, a dummy that indicates that a taxpayer is household head, a set of industry dummies, a set of residential area dummies, and individual and time fixed effects. To obtain the price elasticity, we calculate implied price elasticities by dividing the estimated coefficient on price by the sample proportion of claimants."
)

tab

out.file <- file(here("export", "tables", "claim-elasticity.tex"), open = "w")
writeLines(tab, out.file)
close(out.file)
```

\clearpage
## Policy Implications
\clearpage

```{r policy-effect-class, include=FALSE}
policy <- main$policy_effect()
```

```{r policy-effect}
# [Paper] Table 4
tab <- policy$effective(
  e = -3.493,
  title = "Policy Effect of 2014 Tax Reform",
  notes = "Notes: We use wage earners whose status of report is observed for 2013 and 2014. Column (1) shows the sample size by income bracket for 2013. Columns (2) and (3) are the report rates for each year. Columns (4) and (5) are the average actual price for each year. Column (6) reports the percentage change in the actual price. Columns (7) shows the average contribution in 2013. Column (8) shows the percentage change in contributions, which is the product of the value in Column (6) and the overall actual price elasticity ($-3.493$). Columns (2)--(8) divide the sample by income bracket, reporting status in 2013, and reporting status in 2014, calculate the corresponding indicator in each subset, and then calculate the average of each indicator weighted by the subset sample size in each income bracket. The bottom row shows the average weighted by the bracket sample size."
)

tab

out.file <- file(here("export", "tables", "policy-effect.tex"), open = "w")
writeLines(tab, out.file)
close(out.file)
```
