---
title: "Charitable Giving, Tax Reform, and Political Trust"
author: 
    - Hiroki Kato$^1$
    - Tsuyoshi Goto$^2$
    - Yong-Rok Kim$^3$
institute:
    - $^1$Osaka University
    - $^2$Chiba University
    - $^3$Kobe University
date: "`r format(Sys.time(), '%Y/%m/%d')`"
output: 
  beamer_presentation:
    latex_engine: xelatex
    keep_tex: true
    toc: false
    includes:
      in_header: template/header.tex
---

```{r setup, include = FALSE, echo = FALSE}
library(here)
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  echo = FALSE, 
  cache = FALSE,
  include = FALSE,
  fig.width = 10, fig.height = 6
)
knitr::opts_knit$set(root.dir = here())

library(kableExtra)
options(knitr.kable.NA = "")
```

# Introduction
## Background of South Korea Tax Reform

To investigate the price effect, we use the 2014 tax reform in the South Korea.

- Before 2014, tax deduction was adopted to subsidize charitable donation behavior.
- After 2014, tax credit have been adopted.

The main difference is that tax credits reduce taxes directly, while tax deductions indirectly lower the tax burden by decreasing the taxpayer’s marginal tax rate, which increases with gross income

<!--
## Charitable Giving and Governement Policy

There are huge literatures to investigate relationship bewteen chariable giving and governement policies

1. price elasticity of charitable giving using the tax benefit
1. the crowd-out effect of government expenditure

Even though tax benefits directly affect government expenditure,
there is no literature to try to connect the tax benefit with governement expenditure as far as we know.

We investigate the price effect and the crowd-out effect simultaneously,
and connect two effects through political trust.

## Why Political Trust?

We conjecture that the political trust is key driver to determine the price effect and the crowd-out effect 

- Price effect: If people untrust politicians, then they may also suspect the system of tax banefit. If people trust politicians sufficiently, then they may try to send money to government. Thus, they do not use the tax benefit which decreases governement's revenue.
- Crowd-out effect: If people untrust politicians, then they may expect that governement does not invest the public goods. This is related with the strategic uncertainty.
-->

# Data
## National Survey of Tax and Benefit (NaSTaB)

- The Korea Institute of Taxation and Finance implements the financial panel survey to study the tax burden of households and the benefits that households receive from goverment.
- The subjects of this survey are general household and household members living in 15 cities and provinces nationwide.
- This survey is based on a face-to-face interview. If it is difficult for investigators to meet subjects, another family member answers on behalf of him.
- Survey items: Annual taxable income (last year), charitable donations (last year), trust for politicians (5-Likert scale), and other covariates (age, education, gender etc.).
- Survey period: 2008 ~ 2019
    - We use survey data after 2013 to focus on tax policy change in 2014.

<!--
## MIS data

- MIS of South Korean collects data on local governement finance.
- From this data, we obtain infomation about tax revenue and expenditure for social welfare.
- Using the population data, we calculate the local governement expenditure per capita and use this variable as main explanatory variable.
- Since the NaSTab includes residence area of respondents, it merges with the data on local governement finance. 
-->

```{r CallR_summary}
knitr::read_chunk("script/R/#0summary.r")
```

```{r library}

```

```{r GGTemp}

```

```{r ReadData}

```

## Time Series of Chariable Giving

```{r SummaryOutcome, include = TRUE, fig.cap="Proportion of Donors (bar chart) and Average Donations among Donors (blue line)"}

```

## Summary Statistics of Covariates

```{r SummaryCovariate}

```

```{r kableSummaryCovariate, include=TRUE}
knitr::kable(
    tabsum[,1:5],
    format = "latex",
    caption = "Summary Statistics of Covariates",
    col.names = c("", "2012", "2013", "2014", "2015"),
    row.names = FALSE,
    align = "lccccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 9) %>% 
pack_rows("Education", 4, 6)
```

## Summary Statistics of Covariates (Cont'd)

```{r kableSummaryCovariate2, include=TRUE}
knitr::kable(
    tabsum[,c(1,6:8)],
    format = "latex",
    caption = "Summary Statistics of Covariates (Continued)",
    col.names = c("", "2016", "2017", "2018"),
    row.names = FALSE,
    align = "lccccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 9) %>% 
pack_rows("Education", 4, 6)
```

## Variable of Giving Price

In the South Korea, the tax policy about charitable giving drastically changed in 2014.
Before 2014, the **tax deduction** adpoted.
After 2014, the **tax credit** adopted.
Under two systems, the giving price is 

- tax deduction: $\text{Price} = 1 - \tau$
- tax credit: $\text{Price} = 1 - r$

$\tau$ is the marginal income tax rate calculated by annual taxable income reported in the NaSTaB, and
$r$ is the tax credit rate determined exogeneity.
In the South Korea, $r = 0.15$.

## Income Distribution and Giving Price

```{r SummaryPriceChange, include=TRUE, fig.cap="Income Distribution and Giving Price"}

```

# Trust Index

```{r CallR}
knitr::read_chunk("script/R/#1baseline.r")
```

## Make Trust Index

The trust for politicans is time-varying variable because it depends on governments' policies.
We make time-invarying trust index using the fixed effect model.

$$
    \text{Trust}_{ijt} = \text{Trustid}_{ij} + c_j \cdot \lambda_t + \lambda_t + \epsilon_{ijt}.
$$

- $\text{Trust}_{ijt}$: trust for politicians (5-Likert scale)
- $\text{Trustid}_i$: individual fixed effect (**Trust index**)
- $c_j \cdot \lambda_t$ captures local governments' policies effect
- $\lambda_t$ captures the central government policies effect

```{r EstimateTrustIndex}

```

```{r MergedWithTrustid}

```

## Histrogram of Trust Index

```{r HistogramTrustid, include = TRUE, fig.cap = "Histogram of Trust Index"}

```

## Relationship between Donations and Trust Index 

```{r ScatterTrusidDonations, include=TRUE, fig.cap="Scatter Plot between Donations and Trust Index"}

```

## Relationship between Receving Tax Benefit and Trust Index

```{r BoxpTrustidByBenefit, include=TRUE, fig.cap="Box Plot of Trust Index Grouped By Tax Benefit"}

```

## Regression of Trust Index on Covariates

```{r RegTrustidOnCovariate}

```

```{r kableRegTrustidOnCovariate, include = TRUE}
knitr::kable(
    tab.indexreg,
    format = "latex",
    caption = "Regression of Trust Index (Year = 2018)",
    col.names = c("Variables", "Coefficients", "S.E."),
    row.names = FALSE,
    align = "lcc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling()
```

## Presidential Transition and Trust Index

In May 2017, South Korean president changed from Park Geun-hye to Moon Jae-in.
This presidential transition was due to the impeachment charge against Park Geun-hye.
People became distrustful of Park Geun-hye due to the shinking of MV Sewol (April 2014).

Even though we control time fixed effect to estimate trust index, 
we are concerned whether time fixed effect can rule out this presidential transition effect.

To check it, we estimate trust index using both data in 2015 and 2016 (Park's Trust index) and 
data in 2017 and 2018 (Moon's Trust index).

## Scatter Plot b/w Park's and Moon's Trust Index

```{r Scatter1Trustid, include=TRUE, fig.cap = "Scatter Plot between Trust Index under Park Geun-hye and Moon Jae-in"}

```

## Scatter Plot b/w Park's Trust Index and Original One

```{r Scatter2Trustid, include=TRUE, fig.cap = "Scatter Plot between Trust Index under Park Geun-hye and Original One"}

```

## Scatter Plot b/w Moon's Trust Index and Original One

```{r Scatter3Trustid, include=TRUE, fig.cap = "Scatter Plot between Trust Index under Moon Jae-in and Original One"}

```

## Regressions of Trust Index on Separated Trust Index

```{r RegTrusidonSepTrustid}

```

```{r kableRegTrusidonSepTrustid, include = TRUE}
knitr::kable(
    tab.regset,
    format = "latex",
    caption = "Regressions of Trust Index on Park's and Moon's Trust Index",
    col.names = c("", "(1)", "(2)", "(3)"),
    row.names = FALSE,
    align = "lccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling()
```

# Price Elasticity

## Baseline Regressions

Our baseline regression equation is 

$$
    \log(\text{Giving}_{ijt}) = 
    \alpha_i + \beta_1 \log(\text{Price}_{ijt}) + \delta X_{ijt} + \lambda_t + \epsilon_{ijt}.
$$

- $\log(\text{Giving}_{ijt})$ is logarithm of individual $i$'s charitable giving in year $t$.
- $\log(\text{Price}_{ijt})$ is logarithm of individual $i$'s giving price in year $t$.
- $\beta_1$ represents the price elasticity of giving.
- $\alpha_i$ and $\lambda_t$ are individual and time fixed effect, respectively.

```{r EstimatePElast}

```

## Result of Baseline Regressions

We found the **price effect** of giving (1\% price increase leads to about 1.1\% giving decrease)

```{r kableEstimatePElast, include=TRUE}
knitr::kable(
    tab.basereg[,c(1,2,5,6)],
    format = "latex",
    caption = "Baseline Regressions",
    col.names = c("", "(1)", "(2)", "(3)"),
    row.names = FALSE,
    align = "lccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling()
```

## Subgroup Regressions

We estimate the baseline regression equation,
using sample grouped by the trust index.

- Lowest: 0 ~ 20\% quantile of trust index
- Lower: 20 ~ 40\% quantile of trust index
- Neutral: 40 ~ 60\% quantile of trust index
- Higher: 60 ~ 80\% quantile of trust index
- Highest: 80 ~ 100\% quantile of trust index

We include the logarithm of income, age, interactions b/w year and education,
interactions b/w year and gender, and living are dummy into covariates.

```{r EstimatePElastByTrustid}

```

## Results of Subgroup Regressions

We cound **NOT** find the price effect for respondents whose trust is very low.

```{r kableEstimatePElastByTrustid, include = TRUE}
knitr::kable(
    tab.trustreg,
    format = "latex",
    caption = "Subgroup Regressions",
    col.names = c("", "Lowest", "Lower", "Neutral", "Higher", "Highest"),
    row.names = FALSE,
    align = "lccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 9)
```

## Heterogenity By Political Trust

To capture heterogeneity precisely,
we estimate the following regression equations:

\begin{align*}
    \log(\text{Giving}_{ijt}) = 
    &\alpha_i + \beta_1 \log(\text{Price}_{ijt}) + \beta_2 \log(\text{Price}_{ijt})\cdot\text{Trustid}_{ij} \\
    &+ \delta X_{ijt} + \lambda_t + \epsilon_{ijt}.
\end{align*}

Price elasticity is obtained by $\beta_1 + \beta_2\cdot\text{Trust}_{ij}$.

```{r EstimateHeteroPEstByTrusid}

```

## Result of Heterogeneity of Political Trust

The price elasticity is **convex** in the trust index.
Those whose trust index is low and high do not respond to the price incentive.

```{r kableEstimateHeteroPEstByTrusid, include=TRUE}
knitr::kable(
    tab.heteroreg,
    format = "latex",
    caption = "Heterogeneity of Political Trust",
    col.names = c("", "(1)", "(2)"),
    row.names = FALSE,
    align = "lcc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling() %>% 
add_indent(c(3,5))
```

## Graphical Representation of Heterogeneity Effect

```{r PlotHeteroPElast, include=TRUE, fig.cap="Relationship between Trust Index and Predicted Elasticity"}

```

# Conclusions

## Conclusions

<!--
Our primitive result can be summarized as follows:

- Low trust: Since people untrust governement's behavior, they act regardless of governement's policies (expenditure and tax benefit)
- Middle trust: Since people have strategic uncertainty, they take a strategy of conditional cooperation. That is, they increase donations and use tax benefit to boost their giving if a local governement increases expenditures.
- High trust (very weak evidence): Since people believe that governement contributes to social welfare, they send money to governement (not charities). Thus, they hestitate to use a tax benefit compared with those whose trust is middle level. 

## Avenue of Our Research

Our primitive results have several serious problem.

1. Endogeneity of giving price. The giving price includes decision-making of use of tax benefit.
1. Does charitable giving contributes to local social welfare? To examine the crowd-out effect of local government expenditure, we need to assume that peole send money to charities which work for local social welfare.
1. Does people believe that a tax benefit decreases the **local** governement's revenue? To interpret our primitive results, we assume that people believe that a tax benefit decreases the budget of local governement.

In future, we need to solve these problems.
-->