---
title: |
  Estimating Effect of Tax Incentives on Charitable Giving Considering Self-Selection of Tax Relief in South Korea
author: 
  - name: Hiroki Kato
    number: 1
  - name: Tsuyoshi Goto
    number: 2
  - name: Yong-Rok Kim
    number: 3
institute:
  - number: 1
    name: Osaka University
  - number: 2
    name: Chiba University
  - number: 3
    name: Kansai University
date: "`r format(Sys.time(), '%Y/%m/%d')`"
bibliography: Rmarkdown/ref_main.bib
csl: template/csl/elsevier-harvard.csl
aspectratio: 169
graphics: yes
output:
  bookdown::pdf_book:
    base_format: "function(..., number_sections) rmarkdown::beamer_presentation(...)"
    number_sections: false
    latex_engine: xelatex
    keep_tex: true
    toc: false
    slide_level: 2
    template: template/tex/plain.tex
params:
  preview: false
---

```{r knit_command, eval = FALSE, include = FALSE, echo = FALSE}
# If you want to knit draft, please run following command manually!!
rmarkdown::render(
  "slide.Rmd",
  output_file = "slide.pdf",
  output_dir = "paper"
)
```

```{r setup, include = FALSE, echo = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  cache = FALSE,
  include = TRUE,
  fig.width = 10, fig.height = 6,
  fig.align = "center", fig.pos = "t"
)

library(here)
knitr::opts_knit$set(root.dir = here())

options(
  knitr.kable.NA = " ",
  knitr.table.format = "latex",
  modelsummary_stars_note = FALSE
)
```

```{r include = FALSE}
library(xfun)
xfun::pkg_attach2(c(
  "tidyverse", "rlist", "modelsummary", "kableExtra",
  "estimatr", "fixest"
))

lapply(Sys.glob(file.path("script/R/functions", "*.r")), source)
```

## Introduction

- In many countries, tax relief for charitable giving are implemented.
- The elasticity of giving tax relief is known as a key parameter to evaluate the welfare implication [@Saez2004].
  - Intuitively, if the elasticity is more than 1 in absolute value, \$1 of tax relief make more than \$1 of charitable giving.
- Many papers investigate the elasticity based on tax return data [@Almunia2020; @Auten2002].

## Introduction

- However, the tax return data record only the declared charitable giving.
	- First issue: **Actual donations is different from declared donations.** [@Fack2016; @Gillitzer2018]
  - We use panel survey data in South Korea to deal with this issue.
- Tax payers decide the amount of donation and whether to declare tax relief based on the size of tax incentive and declaration cost.
  - Second issue: Neglect of this declaration cost may bias the estimations of elasticity.
  - We use instrumental variable (IV) and control function approach for this issue.
- Based on DID as an identification strategy, we investigate the giving price elasticity of South Korea.

## Introduction

Result

1. Baseline results show that the giving price elasticity is less than -1.4 in terms of intensive margins and less than -1.7 in terms of extensive margins in Korea.
2. The estimated giving price elasticity for those who declare charitable giving is around -1.2 -1.6.
    - These estimates are more elastic than the estimates in the extant research, many of which show around -1.
3. By reducing application cost, we can increase charitable giving. 
4. Given our estimates, increasing the subsidy on charitable giving will be desirable in Korea.

# Conceptual Framework

## Optimization Problem

Following @Almunia2020,
consider allocation problem between private consumption ($x_{it}$) and charitable giving ($g_{it}$)

\begin{align}
  \max_{x_{it}, g_{it}, R_{it}} &U(x_{it}, g_{it}, G_t)
  = u_i(x_{it}, g_{it}, G_t) - R_{it}K(Z_{it}), \\
  \text{s.t.}\:\:
  &x_{it} + g_{it}
  = y_{it} - R_{it} T_{it}(y_{it}, g_{it}) - (1 - R_{it}) T_{it}(y_{it}), \\
  &G_t = g_{it} + G_{-it},
\end{align}

where $y_{it}$ is pre-tax total income, $R_{it}$ is a dummy of declaration of tax relief and $T_{it}(y_{it})$ and $T_{it}(y_{it}, g_{it})$ are respectively the amount of tax when $i$ does not declare tax relief and when $i$ declares tax relief in year $t$. $G_{-it}$ is public goods supplied by others. $K(Z_{it})$ is application cost which is a function of instrument $Z_{it}$.

## Remarks on Optimization Problem

We assume

- No saving
- $G_{-it}$ is large enough to $\frac{\partial u_i}{\partial G}(x, g, G) \approx 0$

Given $R_{it}$, optimal level of donations sloves

\begin{align}
  \max_{g_{it}} u_i(
    y_{it} - R_{it} T_{it}(y_{it}, g_{it}) - (1 - R_{it}) T_{it}(y_{it}) - g_{it}, g_{it}, g_{it} + G_{-it}
  ).
\end{align}

- We can ignore application cost $K(Z_{it})$ when solving optimal giving level because the application cost does not depend on $g_{it}$

## First-Order Condition

\begin{align}
  - \frac{\partial u_i}{\partial x_{it}}
  \left( R_{it} \frac{\partial T_{it}}{\partial g_{it}}(y_{it}, g_{it}) + 1 \right)
  + \frac{\partial u_i}{\partial g_{it}} = 0
\end{align}

- $\partial T_{it} / \partial g_{it} < 0$ is tax incentive of charitable giving.
  - Let $s_{it} \equiv |\partial T_{it} / \partial g_{it}|$ be size of tax incentive.
  - Relative giving price is $1 - s_{it}$
  - As we explain later, there is *within* variation of $s_{it}$ due to tax reform.

Define $g_i(1 - s_{it}, y_{it})$ and $g_i(1, y_{it})$ to be the optimal levels of donations (potential outcomes) for choices $R_{it} = 1, 0$ respectively.

## Self-Selection of Tax Relief

We can write indirect utility as

\begin{align}
  &v_i(1 - s_{it}, y_{it}, G_{-it}) - K(Z_{it}),  \\
  &v_i(1, y_{it}, G_{-it}).
\end{align}

Thus, individual $i$ applies for tax relief in year $t$,
that is, $R_{it} = 1$ iff

\begin{align}
  \Delta v_{it} \equiv
  v_i(1 - s_{it}, y_{it}, G_{-it}) - v_i(1, y_{it}, G_{-it})
  \ge K(Z_{it}).
\end{align}


# Identification Strategy
## Outcome Equation

We assume the demand function $g_i(1 - s_{it}, y_{it})$ and $g_i(1, y_{it})$ can be written as the following log-log demand function with two-way FEs:

\begin{align}
  \ln g_i(1 - s_{it}, y_{it}) &= \theta_i + \gamma \ln (1 - s_{it}) + \beta X'_{it} + \iota_t + u_{it}, \\
  \ln g_i(1, y_{it}) &= \theta_i + \beta X'_{it} + \iota_t + u_{it}.
\end{align}

Thus, observed outcome equation is

\begin{align}
  \ln g_{it} = \theta_i + \gamma R_{it} \times \ln(1 - s_{it}) + \beta X'_{it} + \iota_t + u_{it}.
\end{align}

- $\theta_i$ and $\iota_t$ are individual and time FE, respectively.
- $X_{it}$ includes pre-tax income ($y_{it}$) and others.
- If $R_{it} = 0$, the relative price is one (its logged value is $\ln 1 = 0$).
- Our parameter of interest is $\gamma$, which represents the price elasticity of charitable giving.

## Source of Price Variation

1. Within variation of tax incentive ($s_{it}$)
    - Major variation comes from the 2014 tax reform
    - Before 2014, tax deduction (所得控除) was used for tax relief on charitable giving.
    -	After 2014, tax credit (税額控除) started to be used for tax relief on charitable giving. 
1. Within variation of application for tax relief ($R_{it}$)
    - This variation is endogenous.
    - We use **wage earner dummy** and **number of tax accountant** as instrumental variables (IV).

## Background: 2014 Tax Reform in South Korea

**Tax deduction system (until 2013)**

\begin{align}
  T_{it}(y_{it}, g_{it}) = T_{it}(y_{it} - g_{it})
\end{align}

- In 2012 and 2013, the marginal tax rate was the same, though it was different from ones before 2011.
- Tax incentive is $s_{it} = T'(y_{it} - g_{it})$
- The giving price depended on income level and giving level

**Tax credit system (from 2014)**

\begin{align}
  T_{it}(y_{it}, g_{it}) = T_{it}(y_{it}) - m g_{it}
\end{align}

- $m$ is tax credit rate and is $m = 0.15$
- Tax incentive is $s_{it} = m$

## Background: Application System for Wage Earners

## Background: Application System for Non Wage Earners

# Data

```{r}
knitr::spin_child("script/R/1-summary.R")
```

# First-Stage Result: Who Applied for Tax Relief?

```{r}
knitr::spin_child("script/R/2-stage1.R")
```

# Estimating Conventional Price Elasticities

```{r}
knitr::spin_child("script/R/3-elasticity.R")
```

# Control Function Approach

```{r}
knitr::spin_child("script/R/4-cf_approach.R")
```

# Welfare Implication

```{r}
knitr::spin_child("script/R/5-welfare.R")
```

# Conclusion

# References {-}
