---
title: "Charitable Giving, Tax Reform, and Political Trust"
author: 
    - Hiroki Kato$^1$
    - Tsuyoshi Goto$^2$
    - Yong-Rok Kim$^3$
institute:
    - $^1$Osaka University
    - $^2$Chiba University
    - $^3$Kobe University
date: "`r format(Sys.time(), '%Y/%m/%d')`"
output: 
  beamer_presentation:
    latex_engine: xelatex
    keep_tex: true
    toc: false
    includes:
      in_header: template/header.tex
---

```{r setup, include = FALSE, echo = FALSE}
library(here)
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  echo = FALSE, 
  cache = FALSE,
  include = FALSE,
  fig.width = 10, fig.height = 6
)
knitr::opts_knit$set(root.dir = here())

library(tidyverse)
library(readstata13)
library(kableExtra)
options(knitr.kable.NA = "")
```

# Introduction
## Background of South Korea Tax Reform

To investigate the price effect, we use the 2014 tax reform in the South Korea.

- Before 2014, tax deduction was adopted to subsidize charitable donation behavior.
- After 2014, tax credit have been adopted.

The main difference is that tax credits reduce taxes directly, while tax deductions indirectly lower the tax burden by decreasing the taxpayer’s marginal tax rate, which increases with gross income

<!--
## Charitable Giving and Governement Policy

There are huge literatures to investigate relationship bewteen chariable giving and governement policies

1. price elasticity of charitable giving using the tax benefit
1. the crowd-out effect of government expenditure

Even though tax benefits directly affect government expenditure,
there is no literature to try to connect the tax benefit with governement expenditure as far as we know.

We investigate the price effect and the crowd-out effect simultaneously,
and connect two effects through political trust.

## Why Political Trust?

We conjecture that the political trust is key driver to determine the price effect and the crowd-out effect 

- Price effect: If people untrust politicians, then they may also suspect the system of tax banefit. If people trust politicians sufficiently, then they may try to send money to government. Thus, they do not use the tax benefit which decreases governement's revenue.
- Crowd-out effect: If people untrust politicians, then they may expect that governement does not invest the public goods. This is related with the strategic uncertainty.
-->

# Data
## National Survey of Tax and Benefit (NaSTaB)

- The Korea Institute of Taxation and Finance implements the financial panel survey to study the tax burden of households and the benefits that households receive from goverment.
- The subjects of this survey are general household and household members living in 15 cities and provinces nationwide.
- This survey is based on a face-to-face interview. If it is difficult for investigators to meet subjects, another family member answers on behalf of him.
- Survey items: Annual taxable income (last year), charitable donations (last year), trust for politicians (5-Likert scale), and other covariates (age, education, gender etc.).
- Survey period: 2008 ~ 2019
    - We use survey data after 2013 to focus on tax policy change in 2014.

<!--
## MIS data

- MIS of South Korean collects data on local governement finance.
- From this data, we obtain infomation about tax revenue and expenditure for social welfare.
- Using the population data, we calculate the local governement expenditure per capita and use this variable as main explanatory variable.
- Since the NaSTab includes residence area of respondents, it merges with the data on local governement finance. 
-->

```{stata dataset, collectcode=TRUE, results = "hide"}
cd "C:\Users\vge00\Desktop\nastab"  //root path

** ---- ReadData
use "data\shaped.dta", clear

gen price = .
replace price = 1 - mtr if year < 2014
replace price = 1 - 0.15 if year >= 2014
gen log_price = ln(price)
gen log_total_g = ln(i_total_giving + 1)
gen log_pinc_all = ln(lincome + 100000)
replace gender = gender - 1
gen univ = (educ == 3) if !missing(educ)
gen highschool = (educ == 2) if !missing(educ)
gen juniorhigh = (educ == 1) if !missing(educ)
gen sqage = age^2/100

** ---- LagOperation
tsset pid year

gen lag1_price = l.price
gen lag2_price = l2.price
gen lag3_price = l3.price
gen lag4_price = l4.price

gen lag1iv = ln(price/lag1_price)
gen lag2iv = ln(price/lag2_price)
gen lag3iv = ln(price/lag3_price)
gen lag4iv = ln(price/lag4_price)

keep if year >= 2012

** ---- ConstructTaxBalance
gen now_welfare = 1
replace now_welfare = 2 if avg_welfare_tax < 3 & avg_welfare_tax <= 6
replace now_welfare = 3 if avg_welfare_tax <= 3
replace now_welfare = . if missing(avg_welfare_tax)

gen now_tax = 1
replace now_tax = 2 if avg_welfare_tax == 2 | avg_welfare_tax == 5 | avg_welfare_tax == 8
replace now_tax = 3 if avg_welfare_tax == 3 | avg_welfare_tax == 6 | avg_welfare_tax == 9
replace now_tax = . if missing(avg_welfare_tax)

gen now_balance = 0
replace now_balance = 2 if avg_welfare_tax == 1
replace now_balance = 1 if avg_welfare_tax == 2 | avg_welfare_tax == 4
replace now_balance = -1 if avg_welfare_tax == 6 | avg_welfare_tax == 8
replace now_balance = -2 if avg_welfare_tax == 9
replace now_balance = . if missing(avg_welfare_tax)

gen now_balance3 = 0
replace now_balance3 = 1 if now_balance > 0
replace now_balance3 = -1 if now_balance < 0
replace now_balance3 = . if missing(now_balance)
```

## Time Series of Chariable Giving

```{stata SummaryOutcome, results = "hide"}
frame copy default avgdt
frame avgdt: by year, sort: egen meanext = mean(i_ext_giving)
frame avgdt: by year, sort: egen meanint = mean(i_total_giving) if i_ext_giving == 1
frame avgdt: keep year meanext meanint
frame avgdt: duplicates drop
frame avgdt: keep if meanint != .

frame avgdt: {
    twoway ///
	(bar meanext year, color(gs10) lcolor(black) barwidth(0.9) yaxis(1)) ///
	(connected meanint year, color(blue) yaxis(2)), ///
	xline(2013.5, lcolor(red) lpattern(-)) ///
	yscale(range(0 .) axis(1)) ///
	yscale(range(0 .) axis(2)) ///
	ylabel(0(.05).2, axis(1)) ///
	ylabel(0(50)200, axis(2)) ///
	ytitle("Proportion of donors", axis(1)) ///
	ytitle("Average donations among donors", axis(2)) ///
	xlabel(2012(1)2018) xtitle("Year")  ///
	legend(label(1 "Extensive margin") label(2 "Intensive margin")) ///
	graphregion(fcolor(white))

  graph export "_assets/SummaryOutcome.pdf", replace
}
```

```{r, include = TRUE, out.width="90%", fig.cap="Proportion of Donors and Average Donations among Donors"}
knitr::include_graphics(paste(here(), "_assets/SummaryOutcome.pdf", sep= "/"))
```

## Summary Statistics of Covariates

```{stata SummaryCovariate, results = "hide"}
matrix sumcov = J(7, 7, .)

label variable gender "Female"
label variable age "Age"
label variable lincome "Annual taxable income"
label variable univ "University graduate"
label variable highschool "High School Graduate"
label variable pid "#.Respondents"
label variable hhid "#.Households"

local j = 0
foreach v in gender age lincome univ highschool {
    local k = 1
	local j = `++j'
	di "j = `j'"
	forvalues y = 2012(1)2018 {
	    di "k = `k'"
		summarize `v' if year == `y'
		matrix sumcov[`j',`k'] = r(mean)
		local k = `++k'
	}
}

local k = 1
forvalues y = 2012(1)2018 {
    di = "k = `k'"
	summarize pid if year == `y'
	matrix sumcov[6, `k'] = r(N)
	local k = `++k'
}

frame copy default temp
frame temp: keep year hhid
frame temp: duplicates drop
local k = 1
forvalues y = 2012(1)2018 {
    di = "k = `k'"
	frame temp: summarize hhid if year == `y'
	matrix sumcov[7, `k'] = r(N)
	local k = `++k'
}

matrix rownames sumcov = gender age lincome univ highschool pid hhid 
xsvmat sumcov, saving(_assets/SummaryCovariate.dta) rownames(xvar)
```

```{r shapeSummaryCovariate}
tabsum <- read.dta13("_assets/SummaryCovariate.dta") %>% data.frame()
tabsum <- tabsum %>% 
	mutate_at(vars(-xvar), 
		list(
			~case_when(
				xvar == "pid" | xvar == "hhid" ~ sprintf("%1d", as.integer(.)),
				TRUE ~ sprintf("%1.2f", .)
			)
		)
	) %>% 
	mutate(
		xvar = recode(
			xvar,
			"gender" = "Female",
			"age" = "Age",
			"lincome" = "Annual taxable income",
			"univ" = "University graduate",
			"highschool" = "High school graduate",
			"pid" = "#.Respondents",
			"hhid" = "#.Households" 
		)
	)
```

```{r kableSummaryCovariate, include=TRUE}
knitr::kable(
    tabsum[,1:5],
    format = "latex",
    caption = "Summary Statistics of Covariates",
    col.names = c("", "2012", "2013", "2014", "2015"),
    row.names = FALSE,
    align = "lccccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling() 
```

## Summary Statistics of Covariates (Cont'd)

```{r kableSummaryCovariate2, include=TRUE}
knitr::kable(
    tabsum[,c(1,6:8)],
    format = "latex",
    caption = "Summary Statistics of Covariates (Continued)",
    col.names = c("", "2016", "2017", "2018"),
    row.names = FALSE,
    align = "lccccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling() 
```


## What is Giving Price?

Consider allocation between private consumptions ($x_i$) and charitable giving ($g_i$).
Let $y_i$ be pre-tax total income.
Then, the budget constraint is 

$$
    x_i + g_i = y_i - T_i(y_i, g_i),
$$

where $T_i$ is tax amount depending on the pre-tax income and charitable giving.

## Determination of Tax Amount

Tax deduction reduces taxable income by giving, that is,

$$
    T_i = \tau(y_i - g_i) \cdot (y_i - g_i),
$$

where $\tau(\cdot)$ is the marginal income tax rate which is determined by $y_i - g_i$.

Tax credit reduces tax amount directly, that is,

$$
    T_i = \tau(y_i)\cdot y_i - m g_i,
$$

where $m \in [0, 1]$ is the tax credit rate.

## Derive Giving Price

Under the tax deduction system, the budget constraint is 

$$
    x_i + [1 - \tau(y_i - g_i)]g_i = [1 - \tau(y_i - g_i)] y_i.
$$

Thus, the giving price of tax deduction system is $p_i^{d} = 1 - \tau(y_i - g_i)$.

Under the tax credit system, the budget constraint is 

$$
    x_i + (1 - m) g_i = [1 - \tau(y_i)] y_i.
$$

Thus, the giving price of tax credit system is $p_i^c = 1 - m$.

## Construct Giving Price

In the South Korea, the tax policy about charitable giving drastically changed in 2014.

- tax deduction (before 2014): $\text{Price}_i = 1 - \tau(y_i - g_i)$
    - the giving price is endogenous because people can manipulate $\tau(y_i - g_i)$ using the charitable giving $g_i$. Since this problem is caused by *last* donations, we use the giving price applying to the *first* donations (**first price**). The first price is calculate by $\tau(y_i)$ where $y_i$ is the annual taxable income reported in the NaSTaB.
- tax credit (after 2014): $\text{Price}_i = 1 - m$
    - In the South Korea, the tax credit rate determines exogeneity, $m = 0.15$.

## Income Distribution and Giving Price

```{stata SummaryPriceChange, results = "hide"}
frame copy default sump
frame sump: keep if year == 2013
frame sump: keep lincome price

frame sump: {
    twoway ///
	(line price lincome, yaxis(1) connect(stairstep) sort(lincome) lcolor(blue)) ///
	(histogram lincome, freq yaxis(2) color(gs10%50) lcolor(black)), ///
	yline(0.85, lcolor(red) lpattern(-)) ///
	xline(1200, lcolor(black) lpattern(-))  ///
	xline(4600, lcolor(black) lpattern(-))  ///
	ytitle("Giving Price", axis(1)) ///
	ytitle("Count", axis(2)) ///
	xlabel(1200 4600 8800 30000) ///
	xtitle("Annual taxable income (unit: 10,000KRW)")  ///
	legend(label(1 "Giving Price in 2013")) ///
	graphregion(fcolor(white))

  graph export "_assets/SummaryPriceChange.pdf", replace
}
```

```{r, include = TRUE, out.width="90%", fig.cap="Income Distribution and Giving Price in 2013"}
knitr::include_graphics(paste(here(), "_assets/SummaryPriceChange.pdf", sep= "/"))
```

# Price Elasticity

## Baseline Regressions

Our baseline regression equation is 

$$
    \log(\text{Giving}_{ijt}) = 
    \alpha_i + \beta_1 \log(\text{Price}_{ijt}) + \delta X_{ijt} + \lambda_t + \epsilon_{ijt}.
$$

- $\log(\text{Giving}_{ijt})$ is logarithm of individual $i$'s charitable giving in year $t$.
- $\log(\text{Price}_{ijt})$ is logarithm of individual $i$'s giving price in year $t$.
- $\beta_1$ represents the price elasticity of giving.
- $\alpha_i$ and $\lambda_t$ are individual and time fixed effect, respectively.

```{stata EstimateElasticity, results = "hide"}
label variable log_price "ln(giving price)"

xtreg log_total_g log_price log_pinc_all i.year, fe vce(cluster pid)
mat coef1 = r(table)
mat coef1 = coef1[1..rowsof(coef1), 1]
mat colnames coef1 = model1
mat stat1 = (e(N) \ e(r2_a))
mat colnames stat1 = model1
mat rownames stat1 = N r2a

xtreg log_total_g log_price log_pinc_all age i.year, fe vce(cluster pid)
mat coef2 = r(table)
mat coef2 = coef2[1..rowsof(coef2), 1]
mat colnames coef2 = model2
mat stat2 = (e(N) \ e(r2_a))
mat colnames stat2 = model2
mat rownames stat2 = N r2a

xtreg log_total_g log_price log_pinc_all age i.year##i.educ, fe vce(cluster pid)
mat coef3 = r(table)
mat coef3 = coef3[1..rowsof(coef3), 1]
mat colnames coef3 = model3
mat stat3 = (e(N) \ e(r2_a))
mat colnames stat3 = model3
mat rownames stat3 = N r2a

xtreg log_total_g log_price log_pinc_all age i.year##i.gender i.year##i.educ, fe vce(cluster pid)
mat coef4 = r(table)
mat coef4 = coef4[1..rowsof(coef4), 1]
mat colnames coef4 = model4
mat stat4 = (e(N) \ e(r2_a))
mat colnames stat4 = model4
mat rownames stat4 = N r2a

xtreg log_total_g log_price log_pinc_all age i.living_area i.year##i.gender i.year##i.educ, fe vce(cluster pid)
mat coef5 = r(table)
mat coef5 = coef5[1..rowsof(coef5), 1]
mat colnames coef5 = model5
mat stat5 = (e(N) \ e(r2_a))
mat colnames stat5 = model5
mat rownames stat5 = N r2a

mat_capp coef : coef1 coef2
mat_capp coef : coef coef3
mat_capp coef : coef coef4
mat_capp coef : coef coef5

mat_capp stat : stat1 stat2
mat_capp stat : stat stat3
mat_capp stat : stat stat4
mat_capp stat : stat stat5

mat_rapp model : coef stat

xsvmat model, saving(_assets/EstimateElasticity.dta) rownames(xvar)
```


## Result of Baseline Regressions

We found the **price effect** of giving (1\% price increase leads to about 1.1\% giving decrease)


```{r shapeEstimateElasticity}
org.basereg <- read.dta13("_assets/EstimateElasticity.dta") %>% data.frame()

coef.basereg <- org.basereg %>% 
	filter(xvar %in% c("b", "se", "pvalue")) %>% 
	pivot_longer(-xvar, values_to = "value", names_to = "reg") %>% 
	pivot_wider(values_from = "value", names_from = "xvar") %>% 
	mutate(
		b = case_when(
			pvalue <= 0.01 ~ sprintf("%1.3f***", b),
			pvalue <= 0.05 ~ sprintf("%1.3f**", b),
			pvalue <= 0.1 ~ sprintf("%1.3f*", b),
			TRUE ~ sprintf("%1.3f", b)
		),
		se = sprintf("(%1.3f)", se)
	) %>% 
	select(reg, b, se) %>% 
	pivot_longer(-reg, values_to = "value", names_to = "stat") %>% 
	pivot_wider(values_from = "value", names_from = "reg") %>% 
	select(-stat) %>% 
	cbind(xvar = c("ln(giving price)", ""), .)

stat.basereg <- org.basereg %>% filter(xvar == "N") 

addline <- rbind(
  c("Logged Income", "Y", "Y", "Y", "Y", "Y"),
  c("Age", "N", "Y", "Y", "Y", "Y"),
  c("Year X Educ", "N", "N", "Y", "Y", "Y"),
  c("Year X Gender", "N", "N", "N", "Y", "Y"),
  c("Resident Area", "N", "N", "N", "N", "Y")
)

tab.basereg <- rbind(as.matrix(coef.basereg), addline) %>% 
	rbind(as.matrix(stat.basereg)) %>% 
	data.frame()
```

```{r kableEstimateElasticity, include = TRUE}
knitr::kable(
    tab.basereg,
    format = "latex",
    caption = "Baseline Regressions",
    col.names = c("", "(1)", "(2)", "(3)", "(4)", "(5)"),
    row.names = FALSE,
    align = "lccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 9)
```

## Robustness Check 

We addressed the following two potential concerns:

1. Income and donations are determined simultaneously
    - This causes both a change of giving price and a change of an amount of donations
    - Gruber and Saez (2002) provided that we should use $\log(\text{Price}_{ijt}/\text{Price}_{ij(t-k)})$ as an insturment.
    - Following Alumina et al. (2020), we estimated the model (5) in the previous slide, using the panel IV model for $k = 1, 2, 3, 4$.
2. The effect of presidential transition on donations 
    - The presidential transition is one of our major ommited factor to affect both political trust and charitable giving.
    - To shed light on this concern, we used data in 2013 and 2014 (President was Park Geun-hye in both years), and estimated the model (5) in the previous slide, using the fixed effect model and the panel IV model for $k = 1, 2, 3, 4$.

```{stata Robust1EstimateElasticity, results = "hide", eval = FALSE}
forvalues i = 1(1)4 {
	xtreg log_price lag`i'iv log_pinc_all age i.living_area i.year##i.gender i.year##i.educ, ///
		fe vce(cluster pid)
	mat fstage`i' = r(table)
	mat fstage`i' = fstage`i'[1..rowsof(fstage`i'), 1]
	mat fstage`i' = (fstage`i'[1,1] \ fstage`i'[3,1]^2)
	mat colnames fstage`i' = model`i'
	mat rownames fstage`i' = ivcoef ivf
}

forvalues i = 1(1)4 {
	xtivreg log_total_g log_pinc_all age i.living_area i.year##i.gender i.year##i.educ ///
		(log_price = lag`i'iv), fe first vce(cluster pid)
	mat coef`i' = r(table)
	mat coef`i' = coef`i'[1..rowsof(coef`i'), 1]
	mat colnames coef`i' = model`i'
	mat stat`i' = (e(N) \ e(r2_w))
	mat colnames stat`i' = model`i'
	mat rownames stat`i' = N r2w
}

mat_capp coef : coef1 coef2
mat_capp coef : coef coef3
mat_capp coef : coef coef4
mat coef = coef'

mat_capp stat : stat1 stat2
mat_capp stat : stat stat3
mat_capp stat : stat stat4
mat stat = stat'

mat_capp fstage : fstage1 fstage2
mat_capp fstage : fstage fstage3
mat_capp fstage : fstage fstage4
mat fstage = fstage'

mat_capp model : coef stat
mat_capp model : model fstage

xsvmat model, saving(_assets/Robust1EstimateElasticity.dta) rownames(xvar) names(col)
```

```{stata Robust2EstimateElasticity, results = "hide", eval = FALSE}
xtreg log_total_g log_price log_pinc_all age i.living_area i.year##i.gender i.year##i.educ ///
	if year == 2013|year == 2014, fe vce(cluster pid)
mat coef0 = r(table)
mat coef0 = coef0[1..rowsof(coef0), 1]
mat colnames coef0 = model0
mat stat0 = (e(N) \ e(r2_a))
mat colnames stat0 = model0
mat rownames stat0 = N r2a
mat_rapp model0 : coef0 stat0

forvalues i = 1(1)4 {
	xtreg log_price lag`i'iv log_pinc_all age i.living_area i.year##i.gender i.year##i.educ ///
		if year == 2013|year == 2014, fe vce(cluster pid)
	mat fstage`i' = r(table)
	mat fstage`i' = fstage`i'[1..rowsof(fstage`i'), 1]
	mat fstage`i' = (fstage`i'[1,1] \ fstage`i'[3,1]^2)
	mat colnames fstage`i' = model`i'
	mat rownames fstage`i' = ivcoef ivf
}

forvalues i = 1(1)4 {
	xtivreg log_total_g log_pinc_all age i.living_area i.year##i.gender i.year##i.educ ///
		(log_price = lag`i'iv) if year == 2013|year == 2014, fe first vce(cluster pid)
	mat coef`i' = r(table)
	mat coef`i' = coef`i'[1..rowsof(coef`i'), 1]
	mat colnames coef`i' = model`i'
	mat stat`i' = (e(N) \ e(r2_w))
	mat colnames stat`i' = model`i'
	mat rownames stat`i' = N r2w
}

mat_capp coef : coef1 coef2
mat_capp coef : coef coef3
mat_capp coef : coef coef4

mat_capp stat : stat1 stat2
mat_capp stat : stat stat3
mat_capp stat : stat stat4

mat_capp fstage : fstage1 fstage2
mat_capp fstage : fstage fstage3
mat_capp fstage : fstage fstage4

mat_rapp model : coef stat
mat_rapp model : model fstage

mat_capp model : model0 model, miss(.)
mat model = model'

xsvmat model, saving(_assets/Robust2EstimateElasticity.dta) rownames(xvar) names(col)
```

## Result of Robustness Check 1

We obtained similar value of price elasticity to baseline results (1\% price increase leads to about 1.1\% giving decrease)

```{r shapeRobust1EstimateElasticity}
org.pivreg <- read.dta13("_assets/Robust1EstimateElasticity.dta") %>% data.frame()

coef.pivreg <- org.pivreg %>% 
	select(xvar, b, se, pvalue) %>% 
	mutate(
		b = case_when(
			pvalue <= 0.01 ~ sprintf("%1.3f***", b),
			pvalue <= 0.05 ~ sprintf("%1.3f**", b),
			pvalue <= 0.1 ~ sprintf("%1.3f*", b),
			TRUE ~ sprintf("%1.3f", b)
		),
		se = sprintf("(%1.3f)", se)
	) %>% 
	select(xvar, b, se) %>% 
	pivot_longer(-xvar, values_to = "value", names_to = "stat") %>% 
	pivot_wider(values_from = "value", names_from = "xvar") %>% 
	select(-stat) %>% 
	cbind(xvar = c("ln(giving price)", ""), .)

stat.pivreg <- org.pivreg %>% 
	select(xvar, ivf, N) %>% 
	mutate(ivf = sprintf("%1.2f", ivf), N = sprintf("%1d", as.integer(N))) %>%
	pivot_longer(-xvar, values_to = "value", names_to = "stat") %>% 
	pivot_wider(values_from = "value", names_from = "xvar") %>% 
	select(-stat) %>% 
	cbind(xvar = c("F-stat of IV", "N"), .)

tab.pivreg <- rbind(coef.pivreg, stat.pivreg)
```

```{r kableRobust1EstimateElasticity, include = TRUE}
knitr::kable(
    tab.pivreg,
    format = "latex",
    caption = "Panel IV Regressions",
    col.names = c("", "k = 1", "k = 2", "k = 3", "k = 4"),
    row.names = FALSE,
    align = "lcccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling()
```

## Result of Robustness Check 2

We obtained **stonger** price effect than baseline (1\% price increase leads to about 1.2 ~ 1.6\% giving decrease)

```{r shapeRobust2EstimateElasticity}
org.pivreg <- read.dta13("_assets/Robust2EstimateElasticity.dta") %>% data.frame()

coef.pivreg <- org.pivreg %>% 
	select(xvar, b, se, pvalue) %>% 
	mutate(
		b = case_when(
			pvalue <= 0.01 ~ sprintf("%1.3f***", b),
			pvalue <= 0.05 ~ sprintf("%1.3f**", b),
			pvalue <= 0.1 ~ sprintf("%1.3f*", b),
			TRUE ~ sprintf("%1.3f", b)
		),
		se = sprintf("(%1.3f)", se)
	) %>% 
	select(xvar, b, se) %>% 
	pivot_longer(-xvar, values_to = "value", names_to = "stat") %>% 
	pivot_wider(values_from = "value", names_from = "xvar") %>% 
	select(-stat) %>% 
	cbind(xvar = c("ln(giving price)", ""), .)

stat.pivreg <- org.pivreg %>% 
	select(xvar, ivf, N) %>% 
	mutate(ivf = if_else(is.na(ivf), "", sprintf("%1.2f", ivf)), N = sprintf("%1d", as.integer(N))) %>%
	pivot_longer(-xvar, values_to = "value", names_to = "stat") %>% 
	pivot_wider(values_from = "value", names_from = "xvar") %>% 
	select(-stat) %>% 
	cbind(xvar = c("F-stat of IV", "N"), .)

tab.pivreg <- rbind(coef.pivreg, stat.pivreg)
```

```{r kableRobust2EstimateElasticity, include=TRUE}
knitr::kable(
    tab.pivreg,
    format = "latex",
    caption = "Results with data in 2013 and 2014",
    col.names = c("", "", "k = 1", "k = 2", "k = 3", "k = 4"),
    row.names = FALSE,
    align = "lccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 9) %>% 
add_header_above(c(" " = 1, "FE" = 1, "Panel IV with FE" = 4))
```
