---
title: "Giving Price, Governement Expenditure, and Political Trust"
author: 
    - Hiroki Kato$^1$
    - Tsuyoshi Goto$^2$
    - Yong-Rok Kim$^3$
institute:
    - $^1$Osaka University
    - $^2$Chiba University
    - $^3$Kobe University
date: "`r format(Sys.time(), '%Y/%m/%d')`"
output: 
  beamer_presentation:
    latex_engine: xelatex
    keep_tex: true
    toc: false
    includes:
      in_header: template/header.tex
---

```{r setup, include = FALSE, echo = FALSE}
library(here)
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  echo = FALSE, 
  cache = FALSE,
  include = FALSE,
  fig.width = 10, fig.height = 6
)
knitr::opts_knit$set(root.dir = here())

library(kableExtra)
options(knitr.kable.NA = "")
```

# Introduction
## Price Effect of Tax Policy

# Data

```{r CallR}
knitr::read_chunk("script/R/#1baseline.r")
```

```{r library}

```

```{r GGTemp}

```

```{r ReadData}

```

# Results

## Trust Index

The trust for politicans is time-varying variable because it depends on governments' policies.
We make time-invarying trust index using the fixed effect model.

$$
    \text{Trust}_{ijt} = \text{Trustid}_i + c_j \cdot \lambda_t + \lambda_t + \epsilon_{ijt}.
$$

- $\text{Trust}_{ijt}$: trust for politicians (5-Likert scale)
- $\text{Trustid}_i$: individual fixed effect (**Trust index**)
- $c_j \cdot \lambda_t$ captures local governments' policies effect
- $\lambda_t$ captures the central government policies effect

We rescale the trust index to an interval $[0,1]$.

## Histrogram of Trust Index

```{r TrustIndex, include = TRUE, fig.cap = "Histogram of Trust Index"}

```

## Regression of Trust Index

```{r TrustReg}

```

```{r TabTrustReg}

```

```{r kableTabTrustReg, include = TRUE}
knitr::kable(
    tab.indexreg,
    format = "latex",
    caption = "Regression of Trust Index (Year = 2018)",
    col.names = c("Variables", "Coefficients", "S.E."),
    row.names = FALSE,
    align = "lcc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling()
```

## Baseline Regressions

Our baseline regression equation is 

\begin{align*}
    \log(\text{Giving}_{ijt}) = 
    &\alpha_i + \beta_1 \log(\text{Price}_{ijt}) + \beta_2 \log(\text{Expend}_{jt}) \\
    &+ \delta X_{ijt} + \lambda_t + \epsilon_{ijt}.
\end{align*}

- $\log(\text{Giving}_{ijt})$ is logarithm of individual $i$'s charitable giving in year $t$.
- $\log(\text{Price}_{ijt})$ is logarithm of individual $i$'s giving price in year $t$.
- $\log(\text{Expend}_{jt})$ is local government $j$'s expenditure for social welfare in year $t$.
- $\beta_1$ represents the price elasticity of giving.
- $\beta_2$ represents the local government expenditure elasticity of giving.
- $\alpha_i$ and $\lambda_t$ are individual and time fixed effect, respectively.

```{r BaseReg, cache = TRUE}

```

## Result of Baseline Regressions

```{r TabBaseReg}

```

```{r kableTabBaseReg, include=TRUE}
knitr::kable(
    tab.basereg[-c(3:4),c(1,2,5,6)],
    format = "latex",
    caption = "Baseline Regressions",
    col.names = c("", "(1)", "(2)", "(3)"),
    row.names = FALSE,
    align = "lccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling()
```

## Interpretations of Baseline Regression

- We found the **price effect** of giving (1\% price increase leads to about 1.1\% giving decrease)
- We found the **crowd-in effect** of local government expenditure (1\% expenditure increase leads to 0.8\% increase giving)
    - This effect is heterogenous by the level of government expenditure. As local government expenditure increases, the crowd-in effect vanish, and the crowd-out effect emerges.

## Subgroup Regressions

We estimate the baseline regression equation,
using sample grouped by the trust index.

- Lowest: 0 ~ 20\% quantile of trust index
- Lower: 20 ~ 40\% quantile of trust index
- Neutral: 40 ~ 60\% quantile of trust index
- Higher: 60 ~ 80\% quantile of trust index
- Highest: 80 ~ 100\% quantile of trust index

We include the logarithm of income, age, interactions b/w year and education,
interactions b/w year and gender, and living are dummy into covariates.

```{r TrustGroupReg, cache = TRUE}

```

## Results of Subgroup Regressions

```{r TabTrustGroupReg}

```

```{r kableTabTrustGroupReg, include = TRUE}
knitr::kable(
    tab.trustreg,
    format = "latex",
    caption = "Subgroup Regressions",
    col.names = c("", "Lowest", "Lower", "Neutral", "Higher", "Highest"),
    row.names = FALSE,
    align = "lccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 9)
```

## Interpretations of Subgroup Regressions

- We could **NOT** find the crowd-in (crowd-out) effect for respondents whose trust is very low and very high.
    - We found the crowd-in effect for middle group.
    - If the trust for politicians is low, respondents have a willingness to provide public goods without governement help.
    - If the trust for politicians is very high, respondents take a strategy of free-rides.
- We cound **NOT** find the price effect for respondents whose trust is very low.
    - If the trust is very low, respondents do not want to use a tax benefit policies.

## Heterogenity By Political Trust

To capture heterogeneity precisely,
we estimate the following regression equations:

\begin{align*}
    \log(\text{Giving}_{ijt}) = 
    &\alpha_i + \beta_0 \text{Trust}_{ij} \\
    &+ \beta_1 \log(\text{Price}_{ijt}) + \beta_2 \log(\text{Price}_{ijt})\cdot\text{Trust}_{ij} \\
    &+ \beta_3 \log(\text{Expend}_{jt}) + \beta_4 \log(\text{Expend}_{ijt})\cdot\text{Trust}_{ij}\\
    &+ \delta X_{ijt} + \lambda_t + \epsilon_{ijt}.
\end{align*}

- Price elasticity is obtained by $\beta_1 + \beta_2\cdot\text{Trust}_{ij}$.
- Governement expenditure elasticity is obtained by $\beta_3 + \beta_4\cdot\text{Trust}_{ij}$.

```{r TrustHeteroReg, cache = TRUE}

```

```{r TrustHetero2Reg, cache = TRUE}

```

## Result of Heterogeneity By Political Trust (1)

```{r TabTrustHeteroReg}

```

```{r kableTabTrustHeteroReg, include=TRUE}
knitr::kable(
    tab.heteroreg,
    format = "latex",
    caption = "Heterogeneity of Political Trust",
    col.names = c("Variables", "Coefficients", "S.E."),
    row.names = FALSE,
    align = "lcc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling() %>% 
add_indent(c(2, 4))
```

## Result of Heterogeneity of Political Trust (2)

```{r TabTrustHetero2Reg}

```

```{r kableTabTrustHetero2Reg, include=TRUE}
knitr::kable(
    tab.hetero2reg,
    format = "latex",
    caption = "Heterogeneity of Political Trust (include squared term)",
    col.names = c("Variables", "Coefficients", "S.E."),
    row.names = FALSE,
    align = "lcc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling() %>% 
add_indent(c(2,3,5,6))
```

## Graphical Representation of Heterogeneity Effect

```{r PlotPredictedElast, include=TRUE, fig.cap="Relationship between Trust Index and Predicted Elasticity"}

```

# Conclusions

## Conclusions
