---
title: |
  Estimating Effect of Tax Incentives on Charitable Giving Considering Self-Selection of Tax Relief in South Korea
author: 
  - name: Hiroki Kato
    number: 1
  - name: Tsuyoshi Goto
    number: 2
  - name: Yong-Rok Kim
    number: 3
institute:
  - number: 1
    name: Osaka University
  - number: 2
    name: Chiba University
  - number: 3
    name: Kansai University
date: "`r format(Sys.time(), '%Y/%m/%d')`"
bibliography: Rmarkdown/ref_main.bib
csl: template/csl/elsevier-harvard.csl
aspectratio: 169
graphics: yes
output:
  bookdown::pdf_book:
    base_format: "function(..., number_sections) rmarkdown::beamer_presentation(...)"
    number_sections: false
    latex_engine: xelatex
    keep_tex: true
    toc: false
    slide_level: 2
    template: template/tex/plain.tex
---

```{r knit_command, eval = FALSE, include = FALSE, echo = FALSE}
# If you want to knit draft, please run following command manually!!
rmarkdown::render(
  "slide.Rmd",
  output_file = "slide.pdf",
  output_dir = "paper"
)
```

```{r setup, include = FALSE, echo = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  cache = FALSE,
  include = TRUE,
  fig.width = 10, fig.height = 6,
  fig.align = "center", fig.pos = "t"
)

library(here)
knitr::opts_knit$set(root.dir = here())
```

## Introduction

- In many countries, tax relief for charitable giving are implemented.
- The elasticity of giving tax relief is known as a key parameter to evaluate the welfare implication [@Saez2004].
  - Intuitively, if the elasticity is more than 1 in absolute value, \$1 of tax relief make more than \$1 of charitable giving.
- Many papers investigate the elasticity based on tax return data [@Almunia2020; @Auten2002].

## Introduction

- However, the tax return data record only the declared charitable giving.
	- First issue: **Actual donations is different from declared donations.** [@Fack2016; @Gillitzer2018]
  - We use panel survey data in South Korea to deal with this issue.
- Tax payers decide the amount of donation and whether to declare tax relief based on the size of tax incentive and declaration cost.
  - Second issue: Neglect of this declaration cost may bias the estimations of elasticity.
  - We use instrumental variable (IV) and control function approach for this issue.
- Based on DID as an identification strategy, we investigate the giving price elasticity of South Korea.

## Introduction

Result

1. Baseline results show that the giving price elasticity is less than -1.4 in terms of intensive margins and less than -1.7 in terms of extensive margins in Korea.
2. The estimated giving price elasticity for those who declare charitable giving is around -1.2 -1.6.
    - These estimates are more elastic than the estimates in the extant research, many of which show around -1.
3. (Not in the paper) The estimated declaration cost of giving is KRW (\$).
4. (Not in the paper) Given our estimates, increasing the subsidy on charitable giving will be desirable in Korea.

# Conceptual Frameworks

## Optimization Problem

Following @Almunia2020,
consider allocation problem between private consumption ($x_{it}$) and charitable giving ($g_{it}$)

\begin{align}
  \max_{x_{it}, g_{it}, R_{it}} &U(x_{it}, g_{it}, G_t)
  = u_i(x_{it}, g_{it}, G_t) - R_{it}K_{it}, \\
  \text{s.t.}\:\:
  &x_{it} + g_{it}
  = y_{it} - R_{it} T_{it}(y_{it}, g_{it}) - (1 - R_{it}) T_{it}(y_{it}), \\
  &G_t = g_{it} + G_{-it},
\end{align}

where $y_{it}$ is pre-tax total income, $R_{it}$ is a dummy of declaration of tax relief and $T_{it}(y_{it})$ and $T_{it}(y_{it}, g_{it})$ are respectively the amount of tax when $i$ does not declare tax relief and when $i$ declares tax relief in year $t$. $G_{-it}$ is public goods supplied by others.

## Remarks on Optimization Problem

We assume

- No saving
- $G_{-it}$ is large enough to $\frac{\partial u_i}{\partial G}(x, g, G) \approx 0$

Given $R_{it}$, optimal level of donations sloves

\begin{align}
  \max_{g_{it}} u_i(
    y_{it} - R_{it} T_{it}(y_{it}, g_{it}) - (1 - R_{it}) T_{it}(y_{it}) - g_{it}, g_{it}, g_{it} + G_{-it}
  ).
\end{align}

## First-Order Condition

\begin{align}
  - \frac{\partial u_i}{\partial x_{it}}
  \left( R_{it} \frac{\partial T_{it}}{\partial g_{it}}(y_{it}, g_{it}) + 1 \right)
  + \frac{\partial u_i}{\partial g_{it}} = 0
\end{align}

- $\partial T_{it} / \partial g_{it} < 0$ is tax incentive of charitable giving.
  - Let $s_{it} \equiv |\partial T_{it} / \partial g_{it}|$ be size of tax incentive.
  - Relative giving price is $1 - s_{it}$
  - As we explain later, there is *within* variation of $s_{it}$ due to tax reform.

Let $g_i(y_{it}, 1 - R_{it} s_{it})$ be a demand function of charitable giving.

- Define $g_i(1 - s_{it}, y_{it})$ and $g_i(1, y_{it})$ to be the optimal levels of donations (potential outcomes) for choices $R_{it} = 1, 0$ respectively.

## Self-Selection of Tax Relief

We can write indirect utility as

\begin{align}
  &v_i(1 - s_{it}, y_{it}, G_{-it}) - K_{it},  \\
  &v_i(1, y_{it}, G_{-it}).
\end{align}

Thus, individual $i$ applies for tax relief in year $t$,
that is, $R_{it} = 1$ iff

\begin{align}
  \Delta v_{it} \equiv
  v_i(1 - s_{it}, y_{it}, G_{-it}) - v_i(1, y_{it}, G_{-it})
  \ge K_{it}.
\end{align}

## Summary of Conceptual Framework

Potential outcomes: $g_i(1 - s_{it}, y_{it})$ if $R_{it} = 1$. $g_i(1, y_{it})$ if $R_{it} = 0$

Observed outcome:

\begin{align}
  g_i(1 - R_{it} s_{it}, y_{it}) = g_i(1, y_{it}) + R_{it}(g_i(1 - s_{it}, y_{it}) - g_i(1, y_{it}))
\end{align}

Selection of tax relief:

\begin{align}
  R_{it} = 1[\Delta v_{it} - K_{it} \ge 0]
\end{align}

# Identification Strategy

## Statistical Model

We assume the demand function $g_i(y_{it}, 1 - R_{it} s_{it})$ can be written as the following log-log demand function with two-way FEs:

\begin{align}
  \ln g_{it} = \theta_i + \gamma \ln(1 - R_{it}s_{it}) + \beta X'_{it} + \iota_t + u_{it}.
\end{align}

- $\theta_i$ and $\iota_t$ are individual and time FE, respectively.
- $X_{it}$ includes pre-tax income ($y_{it}$) and others.
- If $R_{it} = 1$, then the logged price of giving is $\ln(1 - s_{it})$. Otherwise, $\ln 1 = 0$.

## Within Price Variation for Identification $\gamma$

The *within* price variation can be decomposed into two variations:

1. Within variation of tax incentive ($s_{it}$)
    - Major source: 2014 tax reform
    - Before 2014, tax deduction (所得控除) was used for tax relief on charitable giving.
      - the giving price depended on income level.
    -	After 2014, tax credit (税額控除) started to be used for tax relief on charitable giving.
      - The tax credit rate was determined as 15\%.
      - Giving price is 0.85, irrespective of income level.
1. Within variation of application for tax relief ($R_{it}$)
    - This variation is endogenous (self-selection problem)

## 2014 Tax Reform in South Korea

**Tax deduction system (until 2013)**

\begin{align}
  T_{it}(y_{it}, g_{it}) = T_{it}(y_{it} - g_{it})
\end{align}

- In 2012 and 2013, the marginal tax rate was the same, though it was different from ones before 2011.
- Tax incentive is $s_{it} = T'(y_{it} - g_{it})$

**Tax credit system (from 2014)**

\begin{align}
  T_{it}(y_{it}, g_{it}) = T_{it}(y_{it}) - m g_{it}
\end{align}

- $m$ is tax credit rate and is $m = 0.15$
- Tax incentive is $s_{it} = m$

## Source of Endogenity

1. Usage of tax return data only captures declared charitable giving.
    - If the charitable giving is not declared, tax relief has a little effect.
    - Some papers use survey data to deal with this problem (e.g.~Rehavi and Shack, 2013).
    - **Following them, we use survey panel data of Korea.**
2. If the declaration cost is ignored, the estimation should be biased.
    -  The giving price depends not only on marginal tax rate and tax credit rate, but also on the declaration behavior.
    -  As far as we know, only Almunia et al.~(2020) deal with this problem, though they used tax return data.
    - **We use instrumental variable (IV) strategy to control this endogneity.**

# References {-}
