---
title: "Charitable Giving, Tax Reform, and Political Trust"
author: 
    - Hiroki Kato$^1$
    - Tsuyoshi Goto$^2$
    - Yong-Rok Kim$^3$
institute:
    - $^1$Osaka University
    - $^2$Chiba University
    - $^3$Kobe University
date: "`r format(Sys.time(), '%Y/%m/%d')`"
output: 
  beamer_presentation:
    latex_engine: xelatex
    keep_tex: true
    toc: false
    includes:
      in_header: template/header.tex
---

```{r setup, include = FALSE, echo = FALSE}
library(here)
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  echo = FALSE, 
  cache = FALSE,
  include = FALSE,
  fig.width = 10, fig.height = 6
)
knitr::opts_knit$set(root.dir = here())

library(kableExtra)
options(knitr.kable.NA = "")
```

# Introduction
## Background of South Korea Tax Reform

To investigate the price effect, we use the 2014 tax reform in the South Korea.

- Before 2014, tax deduction was adopted to subsidize charitable donation behavior.
- After 2014, tax credit have been adopted.

The main difference is that tax credits reduce taxes directly, while tax deductions indirectly lower the tax burden by decreasing the taxpayer’s marginal tax rate, which increases with gross income

<!--
## Charitable Giving and Governement Policy

There are huge literatures to investigate relationship bewteen chariable giving and governement policies

1. price elasticity of charitable giving using the tax benefit
1. the crowd-out effect of government expenditure

Even though tax benefits directly affect government expenditure,
there is no literature to try to connect the tax benefit with governement expenditure as far as we know.

We investigate the price effect and the crowd-out effect simultaneously,
and connect two effects through political trust.

## Why Political Trust?

We conjecture that the political trust is key driver to determine the price effect and the crowd-out effect 

- Price effect: If people untrust politicians, then they may also suspect the system of tax banefit. If people trust politicians sufficiently, then they may try to send money to government. Thus, they do not use the tax benefit which decreases governement's revenue.
- Crowd-out effect: If people untrust politicians, then they may expect that governement does not invest the public goods. This is related with the strategic uncertainty.
-->

# Data
## National Survey of Tax and Benefit (NaSTaB)

- The Korea Institute of Taxation and Finance implements the financial panel survey to study the tax burden of households and the benefits that households receive from goverment.
- The subjects of this survey are general household and household members living in 15 cities and provinces nationwide.
- This survey is based on a face-to-face interview. If it is difficult for investigators to meet subjects, another family member answers on behalf of him.
- Survey items: Annual taxable income (last year), charitable donations (last year), trust for politicians (5-Likert scale), and other covariates (age, education, gender etc.).
- Survey period: 2008 ~ 2019
    - We use survey data after 2013 to focus on tax policy change in 2014.

<!--
## MIS data

- MIS of South Korean collects data on local governement finance.
- From this data, we obtain infomation about tax revenue and expenditure for social welfare.
- Using the population data, we calculate the local governement expenditure per capita and use this variable as main explanatory variable.
- Since the NaSTab includes residence area of respondents, it merges with the data on local governement finance. 
-->

```{r CallR_summary}
knitr::read_chunk("script/R/#0summary.r")
```

```{r library}

```

```{r GGTemp}

```

```{r ReadData}

```

## Time Series of Chariable Giving

```{r SummaryOutcome, include = TRUE, fig.cap="Proportion of Donors (bar chart) and Average Donations among Donors (blue line)"}

```

## Summary Statistics of Covariates

```{r SummaryCovariate}

```

```{r kableSummaryCovariate, include=TRUE}
knitr::kable(
    tabsum[,1:5],
    format = "latex",
    caption = "Summary Statistics of Covariates",
    col.names = c("", "2012", "2013", "2014", "2015"),
    row.names = FALSE,
    align = "lccccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 9) %>% 
pack_rows("Education", 4, 6)
```

## Summary Statistics of Covariates (Cont'd)

```{r kableSummaryCovariate2, include=TRUE}
knitr::kable(
    tabsum[,c(1,6:8)],
    format = "latex",
    caption = "Summary Statistics of Covariates (Continued)",
    col.names = c("", "2016", "2017", "2018"),
    row.names = FALSE,
    align = "lccccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 9) %>% 
pack_rows("Education", 4, 6)
```

## What is Giving Price?

Consider allocation between private consumptions ($x_i$) and charitable giving ($g_i$).
Let $y_i$ be pre-tax total income.
Then, the budget constraint is 

$$
    x_i + g_i = y_i - T_i(y_i, g_i),
$$

where $T_i$ is tax amount depending on the pre-tax income and charitable giving.

## Determination of Tax Amount

Tax deduction reduces taxable income by giving, that is,

$$
    T_i = \tau(y_i - g_i) \cdot (y_i - g_i),
$$

where $\tau(\cdot)$ is the marginal income tax rate which is determined by $y_i - g_i$.

Tax credit reduces tax amount directly, that is,

$$
    T_i = \tau(y_i)\cdot y_i - m g_i,
$$

where $m \in [0, 1]$ is the tax credit rate.

## Derive Giving Price

Under the tax deduction system, the budget constraint is 

$$
    x_i + [1 - \tau(y_i - g_i)]g_i = [1 - \tau(y_i - g_i)] y_i.
$$

Thus, the giving price of tax deduction system is $p_i^{d} = 1 - \tau(y_i - g_i)$.

Under the tax credit system, the budget constraint is 

$$
    x_i + (1 - m) g_i = [1 - \tau(y_i)] y_i.
$$

Thus, the giving price of tax credit system is $p_i^c = 1 - m$.

## Construct Giving Price

In the South Korea, the tax policy about charitable giving drastically changed in 2014.

- tax deduction (before 2014): $\text{Price}_i = 1 - \tau(y_i - g_i)$
    - the giving price is endogenous because people can manipulate $\tau(y_i - g_i)$ using the charitable giving $g_i$. Since this problem is caused by *last* donations, we use the giving price applying to the *first* donations (**first price**). The first price is calculate by $\tau(y_i)$ where $y_i$ is the annual taxable income reported in the NaSTaB.
- tax credit (after 2014): $\text{Price}_i = 1 - m$
    - In the South Korea, the tax credit rate determines exogeneity, $m = 0.15$.

## Income Distribution and Giving Price

```{r SummaryPriceChange, include=TRUE, fig.cap="Income Distribution and Giving Price"}

```

# Price Elasticity

```{r callR_elasticity}
knitr::read_chunk("script/R/#1elasticity.r")
```

```{r ReadDataforElasticity}

```

## Baseline Regressions

Our baseline regression equation is 

$$
    \log(\text{Giving}_{ijt}) = 
    \alpha_i + \beta_1 \log(\text{Price}_{ijt}) + \delta X_{ijt} + \lambda_t + \epsilon_{ijt}.
$$

- $\log(\text{Giving}_{ijt})$ is logarithm of individual $i$'s charitable giving in year $t$.
- $\log(\text{Price}_{ijt})$ is logarithm of individual $i$'s giving price in year $t$.
- $\beta_1$ represents the price elasticity of giving.
- $\alpha_i$ and $\lambda_t$ are individual and time fixed effect, respectively.

```{r EstimateElasticity}

```

## Result of Baseline Regressions

We found the **price effect** of giving (1\% price increase leads to about 1.1\% giving decrease)

```{r kableEstimateElasticity, include=TRUE}
knitr::kable(
    tab.basereg,
    format = "latex",
    caption = "Baseline Regressions",
    col.names = c("", "(1)", "(2)", "(3)", "(4)", "(5)"),
    row.names = FALSE,
    align = "lccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 9)
```

## Robustness Check 

We addressed the following two potential concerns:

1. Income and donations are determined simultaneously
    - This causes both a change of giving price and a change of an amount of donations
    - Gruber and Saez (2002) provided that we should use $\log(\text{Price}_{ijt}/\text{Price}_{ij(t-k)})$ as an insturment.
    - Following Alumina et al. (2020), we estimated the model (5) in the previous slide, using the panel IV model for $k = 1, 2, 3, 4$.
2. The effect of presidential transition on donations 
    - The presidential transition is one of our major ommited factor to affect both political trust and charitable giving.
    - To shed light on this concern, we used data in 2013 and 2014 (President was Park Geun-hye in both years), and estimated the model (5) in the previous slide, using the fixed effect model and the panel IV model for $k = 1, 2, 3, 4$.

## Result of Robustness Check 1

We obtained similar value of price elasticity to baseline results (1\% price increase leads to about 1.1\% giving decrease)

```{r Robust1EstimateElasticity}

```

```{r kableRobust1EstimateElasticity, include = TRUE}
knitr::kable(
    tab.pivreg,
    format = "latex",
    caption = "Panel IV Regressions",
    col.names = c("", "k = 1", "k = 2", "k = 3", "k = 4"),
    row.names = FALSE,
    align = "lcccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling()
```


## Result of Robustness Check 2

We obtained **stonger** price effect than baseline (1\% price increase leads to about 1.2 ~ 1.6\% giving decrease)

```{r Robust2EstimateElasticity}

```

```{r kableRobust2EstimateElasticity, include=TRUE}
knitr::kable(
    tab.limitreg,
    format = "latex",
    caption = "Results with data in 2013 and 2014",
    col.names = c("", "", "k = 1", "k = 2", "k = 3", "k = 4"),
    row.names = FALSE,
    align = "lccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 9) %>% 
add_header_above(c(" " = 1, "FE" = 1, "Panel IV with FE" = 4))
```

# Political Trust and Price Elasticity

```{r CallR_trust}
knitr::read_chunk("script/R/#2trust.r")
```

## Estimation of Trust Index

The trust for politicans is time-varying variable because it depends on governments' policies.
We make time-invarying trust index using the fixed effect model.

$$
    \text{Trust}_{ijt} = \text{Trustid}_{ij} + c_j \cdot \lambda_t + \lambda_t + \epsilon_{ijt}.
$$

- $\text{Trust}_{ijt}$: trust for politicians (5-Likert scale)
- $\text{Trustid}_i$: individual fixed effect (**Trust index**)
- $c_j \cdot \lambda_t$ captures local governments' policies effect
- $\lambda_t$ captures the central government policies effect

```{r EstimateTrustIndex}

```

```{r MergedWithTrustid}

```

## Histrogram of Trust Index

```{r HistogramTrustid, include = TRUE, fig.cap = "Histogram of Trust Index"}

```

## Relationship with Donations and Covariates 

- We made a scatter plot b/w individual average donations and trust index
    - No linear relationship
- We tested difference in mean of individual average donations b/w among those whose trust index above and below threshold
    - The difference in mean is statistically siginificant at 5\% level if threshold is $\{2.9, 3.0, 3.1, 3.2, 3.3, 3.4, 3.5\}$.
- We regressed trust index on covariates, using data in 2018
    - trust among females < trust among males
    - the positive correlation between income and trust index
    - trust index is concave in age
    - Those having extreme political views have a distrust of politicians rather than those having moderate political views.

## Relationship b/w Donations and Trust Index 

```{r ScatterTrusidDonations, include=TRUE, fig.cap="Scatter Plot between Donations and Trust Index"}

```

## Difference in Mean b/w Two Trust Groups

```{r PlotDiffDonationsbwTrustGroup, include=TRUE, fig.cap = "Difference in Mean between Trust Group above and below Threshold"}

```

## Regression of Trust Index on Covariates

```{r RegTrustidOnCovariate}

```

```{r kableRegTrustidOnCovariate, include = TRUE}
knitr::kable(
    tab.indexreg,
    format = "latex",
    caption = "Regression of Standarized Trust Index (Year = 2018)",
    col.names = c("Variables", "Coefficients", "S.E."),
    row.names = FALSE,
    align = "lcc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling()
```

## Subgroup Regressions

To see the heterogenous price elasticity by political trust,
We estimated the baseline regression model (5) (see Table \ref{tab:kableEstimateElasticity}),
using sample grouped by the trust index.

- Lowest: 0 ~ 20\% quantile of trust index
- Lower: 20 ~ 40\% quantile of trust index
- Neutral: 40 ~ 60\% quantile of trust index
- Higher: 60 ~ 80\% quantile of trust index
- Highest: 80 ~ 100\% quantile of trust index

Covariates are the logarithm of income, age, interactions b/w year and education,
interactions b/w year and gender, and living are dummy into covariates.

```{r EstimateElasticityByTrustGroup}

```

## Results of Subgroup Regressions

We cound **NOT** find the price effect for respondents whose trust is very low.

```{r kableEstimateElasticityByTrustGroup, include = TRUE}
knitr::kable(
    tab.trustreg,
    format = "latex",
    caption = "Subgroup Regressions",
    col.names = c("", "Lowest", "Lower", "Neutral", "Higher", "Highest"),
    row.names = FALSE,
    align = "lccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 9)
```

## Regression on Interaction Term

To check whether price elasticity is statistically siginificant different among five trust groups,
we estimated the baseline regression model (5) including interation term between five trust groups and giving price.

\begin{align*}
    \log(\text{Giving}_{ijt}) 
    =& \alpha_i + \beta_1 \log(\text{Price}_{ijt}) \\
    &+ \sum_g \beta_g \log(\text{Price}_{ijt}) \cdot \text{TrustGroup}_{ijg}  \\
    &+ \delta X_{ijt} + \lambda_t + \epsilon_{ijt}.
\end{align*}

- $\text{TrustGroup}_{ijg}$: taking 1 if individual $i$ living in $j$ belongs to the trust group $g$.
- $g \in \{ \text{Lowest}, \text{Lower}, \text{Higher}, \text{Highest} \}$.

```{r EstimateInteractionByTrustGroup}

```

## Regression Result on Interation Term

There is statistically siginificant difference on price elasticity between the lowest group and the nuetral group.

```{r kableEstimateInteractionByTrustGroup, include=TRUE}
knitr::kable(
    tab.intreg,
    format = "latex",
    caption = "Heterogenous Price Elasticity",
    col.names = c("", "Coefficients", "S.E."),
    row.names = FALSE,
    align = "lcc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling() %>% 
add_indent(c(2:5))
```

## Potential Concerns of Heterogenous Price Elasticity

- There is one potential concern that the presidential transition affects both donation behavior and political trust.
    - In May 2017, South Korean president changed from Park Geun-hye to Moon Jae-in. This presidential transition was due to the impeachment charge against Park Geun-hye. People became distrustful of Park Geun-hye due to the shinking of MV Sewol (April 2014).
- To rule out this confounder, we constructed president-specific trust indexs using either in 2015 and 2016 (Park's Trust index) or 
data in 2017 and 2018 (Moon's Trust index).
    - We discussed how to use these indexs later.

## Relationship b/w President-specific Trust Indexs

- We made a scatter plot between Park's trust index and Moon's trust index.
    - Large variation of Moon's trust index among those who have same value of the Park's trust index.
- We tested the difference in mean between president-specific trust indexs.
    - The average Park's trust index is lower than the average Moon's trust index, which is statistically siginificant.

## Scatter Plot b/w President-specific Trust Indexs

```{r Scatter1Trustid, include=TRUE, fig.cap = "Scatter Plot between Trust Index under Park Geun-hye and Moon Jae-in"}

```

## Relationship among Three Trust Indexs

- We made a scatter plot between difference of president-specific trust indexs and the original trust index. 
    - there is large variation of difference of president-specific trust indexs, and there is large variation of the original trust index among those who have similar value of two president-specific trust indexs.
- We regressed the original trust index on difference of president-specific trust indexs. We restrict units whose aboslute value of president-specific trust index difference is less than 2 (Abs < 2), 1 (Abs < 1), and 0.5 (Abs < 0.5). 
    - the positive correlations between difference of president-specific trust indexs and the original one. However, this positive correlation is statistically insignigicant if we use units whose president-specific trust indexs have similar values.

## Scatter Plot b/w Difference of Separated Trust Indexs and Original One

```{r Scatter2Trustid, include=TRUE, fig.cap = "Scatter Plot between Difference of President-specific Trust Indexs and Original One"}

```

## Result of Regressions on Difference b/w President-specific Trust

```{r RegTrustidOnDiff2Trustid}

```

```{r kableRegTrustidOnDiff2Trustid, include = TRUE}
knitr::kable(
    tab.dfset,
    format = "latex",
    caption = "Regressions of Trust Index on President-specific Trust Index",
    col.names = c("", "Full", "Abs < 2", "Abs < 1", "Abs < 0.5"),
    row.names = FALSE,
    align = "lcccc",
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 9)
```

## Robustness Check of Heterogenous Price Elasticity

1. Using data in 2013 and 2014, we regressed the interaction model again
    - The president was Park Geun-hye in both 2013 and 2014. Thus, we can exclude the effect of presidential transition on donation behavior.
1. Using the park's trust index instead, we regressed the interaction model with data in 2013 and 2014.
    - Since the trust index represents the trust for politicians under the president Park (but scandalous period), we can rule out the effect of presidential transition on both donations and trust.
1. Restricting to units aboslute value of president-specific trust index difference is less than 1 or 0.5, we regressed the interaction model again (year > 2011)
    - Last method rules out the effect of presidential transition on political trust because the original trust index is not affected by presidential transition.
 
```{r Robust1EstimateInteractionByTrustGroup}

```

## Result of Robustness Check

```{r kableRobust1EstimateInteractionByTrustGroup, include=TRUE}
knitr::kable(
    tab.robintreg,
    format = "latex",
    caption = "Robustness Check of Heterogenous Price Elasticity",
    col.names = c("", "(1)", "(2)", "(3)", "(4)"),
    row.names = FALSE,
    align = "lcccc",
    booktabs = TRUE, escape = FALSE, linesep = ""
) %>% 
kable_styling(font_size = 8) %>% 
add_indent(c(3:10)) %>% 
add_header_above(c("Trust index" = 1, "Original" = 1, "Park" = 1, "Original(Abs<1)" = 1, "Original(Abs<0.5)" = 1)) %>% 
add_header_above(c("Year" = 1, "2013 and 2014" = 2, "After 2012" = 2))
```

<!--
## Heterogenity By Political Trust

To capture heterogeneity precisely,
we estimate the following regression equations:

\begin{align*}
    \log(\text{Giving}_{ijt}) = 
    &\alpha_i + \beta_1 \log(\text{Price}_{ijt}) + \beta_2 \log(\text{Price}_{ijt})\cdot\text{Trustid}_{ij} \\
    &+ \delta X_{ijt} + \lambda_t + \epsilon_{ijt}.
\end{align*}

Price elasticity is obtained by $\beta_1 + \beta_2\cdot\text{Trust}_{ij}$.

```{r EstimateHeteroPEstByTrusid, eval=FALSE}

```

## Result of Heterogeneity of Political Trust

The price elasticity is **convex** in the trust index.
Those whose trust index is low and high do not respond to the price incentive.

```{r kableEstimateHeteroPEstByTrusid, include=TRUE, eval=FALSE}
knitr::kable(
    tab.heteroreg,
    format = "latex",
    caption = "Heterogeneity of Political Trust",
    col.names = c("", "(1)", "(2)"),
    row.names = FALSE,
    align = "lcc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling() %>% 
add_indent(c(3,5))
```

## Graphical Representation of Heterogeneity Effect

```{r PlotHeteroPElast, include=TRUE, fig.cap="Relationship between Trust Index and Predicted Elasticity", eval=FALSE}

```

-->

# Conclusions

## Conclusions

<!--
Our primitive result can be summarized as follows:

- Low trust: Since people untrust governement's behavior, they act regardless of governement's policies (expenditure and tax benefit)
- Middle trust: Since people have strategic uncertainty, they take a strategy of conditional cooperation. That is, they increase donations and use tax benefit to boost their giving if a local governement increases expenditures.
- High trust (very weak evidence): Since people believe that governement contributes to social welfare, they send money to governement (not charities). Thus, they hestitate to use a tax benefit compared with those whose trust is middle level. 

## Avenue of Our Research

Our primitive results have several serious problem.

1. Endogeneity of giving price. The giving price includes decision-making of use of tax benefit.
1. Does charitable giving contributes to local social welfare? To examine the crowd-out effect of local government expenditure, we need to assume that peole send money to charities which work for local social welfare.
1. Does people believe that a tax benefit decreases the **local** governement's revenue? To interpret our primitive results, we assume that people believe that a tax benefit decreases the budget of local governement.

In future, we need to solve these problems.
-->