# Price Elasticity

## Baseline Regressions

Our baseline regression equation is 

$$
    \log(\text{Giving}_{ijt}) = 
    \alpha_i + \beta_1 \log(\text{Price}_{ijt}) + \delta X_{ijt} + \lambda_t + \epsilon_{ijt}.
$$

- $\log(\text{Giving}_{ijt})$ is logarithm of individual $i$'s charitable giving in year $t$.
- $\log(\text{Price}_{ijt})$ is logarithm of individual $i$'s giving price in year $t$.
- $\beta_1$ represents the price elasticity of giving.
- $\alpha_i$ and $\lambda_t$ are individual and time fixed effect, respectively.

```{stata EstimateElasticity, results = "hide", eval = FALSE}
label variable log_price "ln(giving price)"

* baseline
xtreg log_total_g log_price log_pinc_all i.year, fe vce(cluster pid)
mat coef = r(table)["b".."pvalue", "log_price"]
mat colnames coef = model0
mat stat = e(N) \ e(r2_a)
mat colnames stat = model0
mat rownames stat = N r2a
mat_rapp model0 : coef stat
mat tabular = model0'

* with covariates
local cov sqage i.year##i.educ i.year##i.gender i.living_area
local xvars 
local k = 1
foreach v of local cov {
	di "model `k'"
    
	*make set of covariates
	local xvars `xvars' `v'
	
	*estimate fixed effect model
	xtreg log_total_g log_price log_pinc_all i.year age `xvars', fe vce(cluster pid)
	
	*matrix of regression result
	mat coef = r(table)["b".."pvalue","log_price"]
	mat colnames coef = model`k'
	mat stat = e(N) \ e(r2_a)
	mat colnames stat = model`k'
	mat rownames stat = N r2a
	mat_rapp model`k' : coef stat
	mat model`k' = model`k''
	
	*combined with previous results
	mat_rapp tabular : tabular model`k'

	local k = `++k'
}

xsvmat tabular, saving(_assets/EstimateElasticity.dta, replace) rownames(xvar) names(col)
```


## Baseline Regressions: Result

We found the **price effect** of giving (1\% price increase leads to about 1.1\% giving decrease)


```{r shapeEstimateElasticity}
org.basereg <- read.dta13("_assets/EstimateElasticity.dta") %>% data.frame()

coef.basereg <- org.basereg %>% 
	mutate(
		b = case_when(
			pvalue <= 0.01 ~ sprintf("%1.3f***", b),
			pvalue <= 0.05 ~ sprintf("%1.3f**", b),
			pvalue <= 0.1 ~ sprintf("%1.3f*", b),
			TRUE ~ sprintf("%1.3f", b)
		),
		se = sprintf("(%1.3f)", se)
	) %>% 
	select(xvar, b, se) %>% 
	pivot_longer(-xvar, values_to = "value", names_to = "stat") %>% 
	pivot_wider(values_from = "value", names_from = "xvar") %>% 
	select(-stat) %>% 
	cbind(xvar = c("ln(giving price)", ""), .)

stat.basereg <- org.basereg %>% select(N) %>% unlist() %>% c("N", .)

addline <- rbind(
  c("Logged Income", "Y", "Y", "Y", "Y", "Y"),
  c("Age", "N", "Y", "Y", "Y", "Y"),
  c("Year X Educ", "N", "N", "Y", "Y", "Y"),
  c("Year X Gender", "N", "N", "N", "Y", "Y"),
  c("Resident Area", "N", "N", "N", "N", "Y")
)

tab.basereg <- rbind(as.matrix(coef.basereg), addline) %>% 
	rbind(stat.basereg) %>% 
	data.frame()
```

```{r kableEstimateElasticity, include = TRUE}
knitr::kable(
    tab.basereg,
    format = "latex",
    caption = "Baseline Regressions",
    col.names = c("", "(1)", "(2)", "(3)", "(4)", "(5)"),
    row.names = FALSE,
    align = "lccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 9)
```

## Intensive Margin and Extensive Margin

Let $D_{ijt}$ be a dummy variable taking 1 if individual $i$ whose resident area $j$ in year $t$ donate in year $t$

- Intensive margin: Estiamte $\beta_1$ where outcome variable is $\log(\text{Giving}_{ijt})$, using units with $D_{ijt} = 1$.
- Extensive margin: Estimate $\beta_1$ where outcome variable is $D_{ijt}$.
	- Extensive-margin price elasticity can be calculated by $\beta_1/\bar{D}$ where $\bar{D}$ is the sample mean of $D_{ijt}$.

Covariates in each column corresponds to a column in a previous slide.

```{stata EstimateElasticityIntensive, results = "hide", eval = FALSE}
label variable log_price "ln(giving price)"

* baseline
xtreg log_total_g log_price log_pinc_all i.year if i_ext_giving == 1, fe vce(cluster pid)
mat coef = r(table)["b".."pvalue", "log_price"]
mat colnames coef = model0
mat stat = e(N) \ e(r2_a)
mat colnames stat = model0
mat rownames stat = N r2a
mat_rapp model0 : coef stat
mat tabular = model0'

* with covariates
local cov sqage i.year##i.educ i.year##i.gender i.living_area
local xvars 
local k = 1
foreach v of local cov {
	di "model `k'"
    
	*make set of covariates
	local xvars `xvars' `v'
	
	*estimate fixed effect model
	xtreg log_total_g log_price log_pinc_all i.year age `xvars' if i_ext_giving == 1, /// 
		fe vce(cluster pid)
	
	*matrix of regression result
	mat coef = r(table)["b".."pvalue","log_price"]
	mat colnames coef = model`k'
	mat stat = e(N) \ e(r2_a)
	mat colnames stat = model`k'
	mat rownames stat = N r2a
	mat_rapp model`k' : coef stat
	mat model`k' = model`k''
	
	*combined with previous results
	mat_rapp tabular : tabular model`k'

	local k = `++k'
}


xsvmat tabular, saving(_assets/EstimateElasticityIntensive.dta, replace) rownames(xvar) names(col)
```

```{stata EstimateElasticityExtensive, results = "hide", eval = FALSE}
label variable log_price "ln(giving price)"

* baseline
xtreg i_ext_giving log_price log_pinc_all i.year, fe vce(cluster pid)
mat coef = r(table)["b".."pvalue", "log_price"]
mat colnames coef = model0
mat stat = e(N) \ e(r2_a)
mat colnames stat = model0
mat rownames stat = N r2a

* proportion of donors
summarize i_ext_giving
local mu = r(mean)

* implied elasticity
lincom log_price*(1/`mu')
mat elas = r(estimate) \ r(se) \ ttail(r(df), abs(r(estimate)/r(se)))*2
mat colnames elas = model0
mat rownames elas = e_b e_se e_pval

* baseline result
mat_rapp model0 : coef stat
mat_rapp model0 : model0 elas
mat tabular = model0'

* with covariates
local cov sqage i.year##i.educ i.year##i.gender i.living_area
local xvars 
local k = 1
foreach v of local cov {
	di "model `k'"
    
	*make set of covariates
	local xvars `xvars' `v'
	
	*estimate fixed effect model
	xtreg i_ext_giving log_price log_pinc_all i.year age `xvars', fe vce(cluster pid)
	
	*matrix of regression result
	mat coef = r(table)["b".."pvalue","log_price"]
	mat colnames coef = model`k'
	mat stat = e(N) \ e(r2_a)
	mat colnames stat = model`k'
	mat rownames stat = N r2a
	
	*proportion of donors
	summarize i_ext_giving
	local mu = r(mean)
	
	*implied elasticity
	lincom log_price*(1/`mu')
	mat elas = r(estimate) \ r(se) \ ttail(r(df), abs(r(estimate)/r(se)))*2
	mat colnames elas = model`k'
	mat rownames elas = e_b e_se e_pval
	
	*regression result
	mat_rapp model`k' : coef stat
	mat_rapp model`k' : model`k' elas
	mat model`k' = model`k''
	
	*combined with previous results
	mat_rapp tabular : tabular model`k'

	local k = `++k'
}

xsvmat tabular, saving(_assets/EstimateElasticityExtensive.dta, replace) rownames(xvar) names(col)
```

## Intensive Margin and Extensive Margin: Result

```{r shapeEstimateElasticityIntExt}
org.basereg <- list(
	intensive = read.dta13("_assets/EstimateElasticityIntensive.dta") %>% data.frame(),
	extensive = read.dta13("_assets/EstimateElasticityExtensive.dta") %>% data.frame()
)

coef.basereg <- org.basereg %>% 
	purrr::map(function(x)
		x %>% 
		mutate(
			b = case_when(
				pvalue <= 0.01 ~ sprintf("%1.3f***", b),
				pvalue <= 0.05 ~ sprintf("%1.3f**", b),
				pvalue <= 0.1 ~ sprintf("%1.3f*", b),
				TRUE ~ sprintf("%1.3f", b)
			),
			se = sprintf("(%1.3f)", se),
			N = sprintf("%1d", N)
		) %>% 
		select(xvar, b, se, N) %>% 
		pivot_longer(-xvar, values_to = "value", names_to = "stat") %>% 
		pivot_wider(values_from = "value", names_from = "xvar") %>% 
		select(-stat) %>% 
		cbind(xvar = c("ln(giving price)", "", ""), .)
	) %>% 
	reduce(rbind)
	

elas.basereg <- org.basereg$extensive %>% 
	mutate(
		e_b = case_when(
			e_pval <= 0.01 ~ sprintf("%1.3f***", e_b),
			e_pval <= 0.05 ~ sprintf("%1.3f**", e_b),
			e_pval <= 0.1 ~ sprintf("%1.3f*", e_b),
			TRUE ~ sprintf("%1.3f", e_b)
		),
		e_se = sprintf("(%1.3f)", e_se)
	) %>% 
	select(xvar, e_b, e_se) %>% 
	pivot_longer(-xvar, values_to = "value", names_to = "stat") %>% 
	pivot_wider(values_from = "value", names_from = "xvar") %>% 
	select(-stat) %>% 
	cbind(xvar = c("Elasticity", ""), .)

tab.basereg <- rbind(coef.basereg[-6,], elas.basereg) %>% rbind(coef.basereg[6,])
```

```{r kableEstimateElasticityIntExt, include = TRUE}
knitr::kable(
    tab.basereg,
    format = "latex",
    caption = "Intensive-margin and Extensive-Margin Price Elasticity",
    col.names = c("", "(1)", "(2)", "(3)", "(4)", "(5)"),
    row.names = FALSE,
    align = "lccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 8) %>% 
pack_rows("Intensive Margin", 1, 3) %>% 
pack_rows("Extensive Margin", 4, 6)
```

## Robustness Check

1. Income and donations are determined simultaneously
1. Effect of presidential transition on donation behavior
1. Last price elasticity
1. Self-selection of receiving tax benefit
1. Transitory and permanent elasticity

## Robustness Check 1

First potential concern: Income and donations are determined simultaneously
    
- This causes both a change of giving price and a change of an amount of donations
- Gruber and Saez (2002) provided that we should use $\log(\text{Price}_{ijt}/\text{Price}_{ij(t-k)})$ as an insturment.
- We estimated the model (5) in the previous slide, using the panel IV model for $k = 1, 2, 3$.
	- Note that Alumnia (2020) took a strategy of $k$-difference model.


```{stata PanelIVEstimateElasticity, results = "hide", eval = FALSE}
forvalues k = 1(1)3 {
    
	di "lag = `k'"
	
	* first stage 
    xtreg log_price diff`k'p log_pinc_all age i.living_area i.year##i.gender i.year##i.educ, ///
		fe vce(cluster pid)
	
	* result of first stage
	mat fstage = r(table)["b".."pvalue","diff`k'p"]
	mat fstage = fstage[1,1] \ fstage[3,1]^2
	mat colnames fstage = model`k'
	mat rownames fstage = ivcoef ivf
	
	* second stage
	xtivreg log_total_g log_pinc_all age i.living_area i.year##i.gender i.year##i.educ ///
		(log_price = diff`k'p), fe vce(cluster pid)
	
	* result of second stage
	mat coef = r(table)["b".."pvalue","log_price"]
	mat colnames coef = model`k'
	mat stat = e(N) \ e(r2_w)
	mat colnames stat = model`k'
	mat rownames stat = N r2w
	mat_rapp model`k' : coef stat
	
	* combined with first stage result
	mat_rapp model`k' : model`k' fstage
	mat model`k' = model`k''
}

mat_rapp tabular : model1 model2
mat_rapp tabular : tabular model3

xsvmat tabular, saving(_assets/PanelIVEstimateElasticity.dta, replace) rownames(xvar) names(col)
```

```{stata PanelIVEstimateElasticityExtensive, results = "hide", eval = FALSE}
forvalues k = 1(1)3 {
    
	di "lag = `k'"
	
	* first stage 
    xtreg log_price diff`k'p log_pinc_all age i.living_area i.year##i.gender i.year##i.educ, ///
		fe vce(cluster pid)
	
	* result of first stage
	mat fstage = r(table)["b".."pvalue","diff`k'p"]
	mat fstage = fstage[1,1] \ fstage[3,1]^2
	mat colnames fstage = model`k'
	mat rownames fstage = ivcoef ivf
	
	* second stage
	xtivreg i_ext_giving log_pinc_all age i.living_area i.year##i.gender i.year##i.educ ///
		(log_price = diff`k'p), fe vce(cluster pid)
	
	* result of second stage
	mat coef = r(table)["b".."pvalue","log_price"]
	mat colnames coef = model`k'
	mat stat = e(N) \ e(r2_w)
	mat colnames stat = model`k'
	mat rownames stat = N r2w
	
	*proportion of donors
	summarize i_ext_giving
	local mu = r(mean)
	
	*implied elasticity
	lincom log_price*(1/`mu')
	mat elas = r(estimate) \ r(se) \ (1 - normal(abs(r(estimate)/r(se))))*2
	mat colnames elas = model`k'
	mat rownames elas = e_b e_se e_pval
	
	* combined with results
	mat_rapp model`k' : coef stat
	mat_rapp model`k' : model`k' elas
	mat_rapp model`k' : model`k' fstage
	mat model`k' = model`k''

}

mat_rapp tabular : model1 model2
mat_rapp tabular : tabular model3

xsvmat tabular, saving(_assets/PanelIVEstimateElasticityExtensive.dta, replace) rownames(xvar) names(col)
```

```{stata PanelIVEstimateElasticityIntensive, results = "hide", eval = FALSE}
forvalues k = 1(1)3 {
    
	di "lag = `k'"
	
	* first stage 
    xtreg log_price diff`k'p log_pinc_all age i.living_area i.year##i.gender i.year##i.educ ///
		if i_ext_giving == 1, fe vce(cluster pid)
	
	* result of first stage
	mat fstage = r(table)["b".."pvalue","diff`k'p"]
	mat fstage = fstage[1,1] \ fstage[3,1]^2
	mat colnames fstage = model`k'
	mat rownames fstage = ivcoef ivf
	
	* second stage
	xtivreg log_total_g log_pinc_all age i.living_area i.year##i.gender i.year##i.educ ///
		(log_price = diff`k'p) if i_ext_giving == 1, fe vce(cluster pid)
	
	* result of second stage
	mat coef = r(table)["b".."pvalue","log_price"]
	mat colnames coef = model`k'
	mat stat = e(N) \ e(r2_w)
	mat colnames stat = model`k'
	mat rownames stat = N r2w
	mat_rapp model`k' : coef stat
	
	* combined with first stage result
	mat_rapp model`k' : model`k' fstage
	mat model`k' = model`k''
}

mat_rapp tabular : model1 model2
mat_rapp tabular : tabular model3

xsvmat tabular, saving(_assets/PanelIVEstimateElasticityIntensive.dta, replace) rownames(xvar) names(col)
```


## Robustness Check 1: Result

```{r shapePanelIVEstimateElasticity}
org.pivreg <- read.dta13("_assets/PanelIVEstimateElasticity.dta") %>% data.frame()

coef.pivreg <- org.pivreg %>% 
	select(xvar, b, se, pvalue) %>% 
	mutate(
		b = case_when(
			pvalue <= 0.01 ~ sprintf("%1.3f***", b),
			pvalue <= 0.05 ~ sprintf("%1.3f**", b),
			pvalue <= 0.1 ~ sprintf("%1.3f*", b),
			TRUE ~ sprintf("%1.3f", b)
		),
		se = sprintf("(%1.3f)", se)
	) %>% 
	select(xvar, b, se) %>% 
	pivot_longer(-xvar, values_to = "value", names_to = "stat") %>% 
	pivot_wider(values_from = "value", names_from = "xvar") %>% 
	select(-stat) %>% 
	cbind(xvar = c("ln(giving price)", ""), .)

stat.pivreg <- org.pivreg %>% 
	select(xvar, ivf, N) %>% 
	mutate(ivf = sprintf("%1.2f", ivf), N = sprintf("%1d", as.integer(N))) %>%
	pivot_longer(-xvar, values_to = "value", names_to = "stat") %>% 
	pivot_wider(values_from = "value", names_from = "xvar") %>% 
	select(-stat) %>% 
	cbind(xvar = c("F-stat of IV", "N"), .)

tab.pivreg <- rbind(coef.pivreg, stat.pivreg)
```

```{r kablePanelIVEstimateElasticity, include = TRUE}
knitr::kable(
    tab.pivreg,
    format = "latex",
    caption = "Panel IV Regressions",
    col.names = c("", "k = 1", "k = 2", "k = 3"),
    row.names = FALSE,
    align = "lccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling()
```

## Robustness Check 1: Intensive and Extensive Margin

```{r shapePanelIVEstimateElasticityIntExt}
org.pivreg <- list(
	intensive = read.dta13("_assets/PanelIVEstimateElasticityIntensive.dta") %>% data.frame(),
	extensive = read.dta13("_assets/PanelIVEstimateElasticityExtensive.dta") %>% data.frame()
)

coef.pivreg <- org.pivreg %>% 
	purrr::map(function(x)
		x %>% 
		select(xvar, b, se, pvalue, ivf, N) %>% 
		mutate(
			b = case_when(
				pvalue <= 0.01 ~ sprintf("%1.4f***", b),
				pvalue <= 0.05 ~ sprintf("%1.4f**", b),
				pvalue <= 0.1 ~ sprintf("%1.4f*", b),
				TRUE ~ sprintf("%1.4f", b)
			),
			se = sprintf("(%1.4f)", se),
			ivf = sprintf("%1.2f", ivf), N = sprintf("%1d", as.integer(N))
		) %>% 
		select(xvar, b, se, ivf, N) %>% 
		pivot_longer(-xvar, values_to = "value", names_to = "stat") %>% 
		pivot_wider(values_from = "value", names_from = "xvar") %>% 
		select(-stat) %>% 
		cbind(xvar = c("ln(giving price)", "", "F-stat of IV", "N"), .)
	) %>% 
	reduce(rbind)

elas.pivreg <- org.pivreg$extensive %>% 
	mutate(
		e_b = case_when(
			e_pval <= 0.01 ~ sprintf("%1.3f***", e_b),
			e_pval <= 0.05 ~ sprintf("%1.3f**", e_b),
			e_pval <= 0.1 ~ sprintf("%1.3f*", e_b),
			TRUE ~ sprintf("%1.3f", e_b)
		),
		e_se = sprintf("(%1.3f)", e_se)
	) %>% 
	select(xvar, e_b, e_se) %>% 
	pivot_longer(-xvar, values_to = "value", names_to = "stat") %>% 
	pivot_wider(values_from = "value", names_from = "xvar") %>% 
	select(-stat) %>% 
	cbind(xvar = c("Elasticity", ""), .)

tab.pivreg <- rbind(coef.pivreg[1:6,], elas.pivreg) %>% rbind(coef.pivreg[7:8,])
```

```{r kablePanelIVEstimateElasticityIntExt, include = TRUE}
knitr::kable(
    tab.pivreg,
    format = "latex",
    caption = "Intensive- and Extensive-Margin Price Elasticity: Panel IV",
    col.names = c("", "k = 1", "k = 2", "k = 3"),
    row.names = FALSE,
    align = "lccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 9) %>% 
pack_rows("Intensive Margin", 1, 4) %>% 
pack_rows("Extensive Margin", 5, 10)
```

## Robust Check 2

Second potential concern: The effect of presidential transition on donations 
    
- The presidential transition is one of our major ommited factor to charitable giving.
	- In May 2017, South Korea president changed from Park Geun-hye to Moon Jae-in. This presidential transition was due to the impeachment charge against Park Geun-hye. People became distrustful of her due to the shinking of MV Sewol (April 2014).
- To shed light on this concern, we used data in 2013 and 2014 (President was Park Geun-hye in both years), and estimated the model (5) in the previous slide, using the fixed effect model and the panel IV model for $k = 1, 2, 3$.


```{stata ShortEstimateElasticity, results = "hide", eval = FALSE}
xtreg log_total_g log_price log_pinc_all age i.living_area i.year##i.gender i.year##i.educ ///
	if year == 2013 | year == 2014, fe vce(cluster pid)

mat coef = r(table)["b".."pvalue","log_price"]
mat colnames coef = model0
mat stat = e(N) \ e(r2_w)
mat colnames stat = model0
mat rownames stat = N r2w
mat_rapp model : coef stat
mat tabular = model'

forvalues k = 1(1)3 {
    
	di "lag = `k'"
	
	* first stage 
    xtreg log_price diff`k'p log_pinc_all age i.living_area i.year##i.gender i.year##i.educ ///
		if year == 2013 | year == 2014, fe vce(cluster pid)
	
	* result of first stage
	mat fstage = r(table)["b".."pvalue","diff`k'p"]
	mat fstage = fstage[1,1] \ fstage[3,1]^2
	mat colnames fstage = model`k'
	mat rownames fstage = ivcoef ivf
	
	* second stage
	xtivreg log_total_g log_pinc_all age i.living_area i.year##i.gender i.year##i.educ ///
		(log_price = diff`k'p) if year == 2013 | year == 2014, fe vce(cluster pid)
	
	* result of second stage
	mat coef = r(table)["b".."pvalue","log_price"]
	mat colnames coef = model`k'
	mat stat = e(N) \ e(r2_w)
	mat colnames stat = model`k'
	mat rownames stat = N r2w
	mat_rapp model`k' : coef stat
	
	* combined with first stage result
	mat_rapp model`k' : model`k' fstage
	mat model`k' = model`k''
	mat_rapp tabular : tabular model`k', miss(.)
}


mat list tabular

xsvmat tabular, saving(_assets/ShortEstimateElasticity.dta, replace) rownames(xvar) names(col)
```

```{stata ShortEstimateElasticityExtensive, results = "hide", eval = FALSE}
* baseline
xtreg i_ext_giving log_price log_pinc_all age i.living_area i.year##i.gender i.year##i.educ ///
	if year == 2013 | year == 2014, fe vce(cluster pid)

mat coef = r(table)["b".."pvalue","log_price"]
mat colnames coef = model0
mat stat = e(N) \ e(r2_w)
mat colnames stat = model0
mat rownames stat = N r2w

* proportion of donors
summarize i_ext_giving
local mu = r(mean)

* implied elasticity
lincom log_price*(1/`mu')
mat elas = r(estimate) \ r(se) \ ttail(r(df), abs(r(estimate)/r(se)))*2
mat colnames elas = model0
mat rownames elas = e_b e_se e_pval

mat_rapp model : coef elas
mat_rapp model : model stat
mat tabular = model'

forvalues k = 1(1)3 {
    
	di "lag = `k'"
	
	* first stage 
    xtreg log_price diff`k'p log_pinc_all age i.living_area i.year##i.gender i.year##i.educ ///
		if year == 2013 | year == 2014, fe vce(cluster pid)
	
	* result of first stage
	mat fstage = r(table)["b".."pvalue","diff`k'p"]
	mat fstage = fstage[1,1] \ fstage[3,1]^2
	mat colnames fstage = model`k'
	mat rownames fstage = ivcoef ivf
	
	* second stage
	xtivreg i_ext_giving log_pinc_all age i.living_area i.year##i.gender i.year##i.educ ///
		(log_price = diff`k'p) if year == 2013 | year == 2014, fe vce(cluster pid)
	
	* result of second stage
	mat coef = r(table)["b".."pvalue","log_price"]
	mat colnames coef = model`k'
	mat stat = e(N) \ e(r2_w)
	mat colnames stat = model`k'
	mat rownames stat = N r2w
	
	*proportion of donors
	summarize i_ext_giving
	local mu = r(mean)
	
	*implied elasticity
	lincom log_price*(1/`mu')
	mat elas = r(estimate) \ r(se) \ (1 - normal(abs(r(estimate)/r(se))))*2
	mat colnames elas = model`k'
	mat rownames elas = e_b e_se e_pval
	
	* combined with first stage result
	mat_rapp model`k' : coef elas
	mat_rapp model`k' : model`k' stat
	mat_rapp model`k' : model`k' fstage
	mat model`k' = model`k''
	mat_rapp tabular : tabular model`k', miss(.)
}


mat list tabular

xsvmat tabular, saving(_assets/ShortEstimateElasticityExtensive.dta, replace) rownames(xvar) names(col)
```

```{stata ShortEstimateElasticityIntensive, results = "hide", eval = FALSE}
* baseline
xtreg log_total_g log_price log_pinc_all age i.living_area i.year##i.gender i.year##i.educ ///
	if (year == 2013 | year == 2014) & i_ext_giving == 1, fe vce(cluster pid)

mat coef = r(table)["b".."pvalue","log_price"]
mat colnames coef = model0
mat stat = e(N) \ e(r2_w)
mat colnames stat = model0
mat rownames stat = N r2w
mat_rapp model : coef stat
mat tabular = model'

forvalues k = 1(1)3 {
    
	di "lag = `k'"
	
	* first stage 
    xtreg log_price diff`k'p log_pinc_all age i.living_area i.year##i.gender i.year##i.educ ///
		if (year == 2013 | year == 2014) & i_ext_giving == 1, fe vce(cluster pid)
	
	* result of first stage
	mat fstage = r(table)["b".."pvalue","diff`k'p"]
	mat fstage = fstage[1,1] \ fstage[3,1]^2
	mat colnames fstage = model`k'
	mat rownames fstage = ivcoef ivf
	
	* second stage
	xtivreg log_total_g log_pinc_all age i.living_area i.year##i.gender i.year##i.educ ///
		(log_price = diff`k'p) if (year == 2013 | year == 2014) & i_ext_giving == 1, fe vce(cluster pid)
	
	* result of second stage
	mat coef = r(table)["b".."pvalue","log_price"]
	mat colnames coef = model`k'
	mat stat = e(N) \ e(r2_w)
	mat colnames stat = model`k'
	mat rownames stat = N r2w
	mat_rapp model`k' : coef stat
	
	* combined with first stage result
	mat_rapp model`k' : model`k' fstage
	mat model`k' = model`k''
	mat_rapp tabular : tabular model`k', miss(.)
}


mat list tabular


xsvmat tabular, saving(_assets/ShortEstimateElasticityIntensive.dta, replace) rownames(xvar) names(col)
```


## Robustness Check 2: Result

```{r shapeShortEstimateElasticity}
org.tab <- read.dta13("_assets/ShortEstimateElasticity.dta") %>% data.frame()

shape.tab <- org.tab %>% 
	select(xvar, b, se, pvalue, ivf, N) %>% 
	mutate(
		b = case_when(
			pvalue <= 0.01 ~ sprintf("%1.3f***", b),
			pvalue <= 0.05 ~ sprintf("%1.3f**", b),
			pvalue <= 0.1 ~ sprintf("%1.3f*", b),
			TRUE ~ sprintf("%1.3f", b)
		),
		se = sprintf("(%1.3f)", se),
		ivf = if_else(is.na(ivf), "", sprintf("%1.2f", ivf)), 
		N = sprintf("%1d", as.integer(N))
	) %>% 
	select(xvar, b, se, ivf, N) %>% 
	pivot_longer(-xvar, values_to = "value", names_to = "stat") %>% 
	pivot_wider(values_from = "value", names_from = "xvar") %>% 
	select(-stat) %>% 
	cbind(xvar = c("ln(giving price)", "", "F-stat of IV", "N"), .)
```

```{r kableShortEstimateElasticity, include=TRUE}
knitr::kable(
    shape.tab,
    format = "latex",
    caption = "Results with data in 2013 and 2014",
    col.names = c("", "", "k = 1", "k = 2", "k = 3"),
    row.names = FALSE,
    align = "lcccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 9) %>% 
add_header_above(c(" " = 1, "FE" = 1, "Panel IV with FE" = 3))
```

## Robustness Check 2: Intensive and Extensive Margin

```{r shapeShortEstimateElasticityIntExt}
org.tab <- list(
	intensive = read.dta13("_assets/ShortEstimateElasticityIntensive.dta") %>% data.frame(),
	extensive = read.dta13("_assets/ShortEstimateElasticityExtensive.dta") %>% data.frame()
)

coef.tab <- org.tab %>% 
	purrr::map(function(x)
		x %>% 
		select(xvar, b, se, pvalue, ivf, N) %>% 
		mutate(
			b = case_when(
				pvalue <= 0.01 ~ sprintf("%1.3f***", b),
				pvalue <= 0.05 ~ sprintf("%1.3f**", b),
				pvalue <= 0.1 ~ sprintf("%1.3f*", b),
				TRUE ~ sprintf("%1.3f", b)
			),
			se = sprintf("(%1.3f)", se),
			ivf = if_else(is.na(ivf), "", sprintf("%1.2f", ivf)), 
			N = sprintf("%1d", as.integer(N))
		) %>% 
		select(xvar, b, se, ivf, N) %>% 
		pivot_longer(-xvar, values_to = "value", names_to = "stat") %>% 
		pivot_wider(values_from = "value", names_from = "xvar") %>% 
		select(-stat) %>% 
		cbind(xvar = c("ln(giving price)", "", "F-stat of IV", "N"), .)
	) %>% 
	reduce(rbind)

elas.tab <- org.tab$extensive %>% 
	mutate(
		e_b = case_when(
			e_pval <= 0.01 ~ sprintf("%1.3f***", e_b),
			e_pval <= 0.05 ~ sprintf("%1.3f**", e_b),
			e_pval <= 0.1 ~ sprintf("%1.3f*", e_b),
			TRUE ~ sprintf("%1.3f", e_b)
		),
		e_se = sprintf("(%1.3f)", e_se)
	) %>% 
	select(xvar, e_b, e_se) %>% 
	pivot_longer(-xvar, values_to = "value", names_to = "stat") %>% 
	pivot_wider(values_from = "value", names_from = "xvar") %>% 
	select(-stat) %>% 
	cbind(xvar = c("Elasticity", ""), .)

tab <- rbind(coef.tab[1:6,], elas.tab) %>% rbind(coef.tab[7:8,])
```

```{r kableShortEstimateElasticityIntExt, include=TRUE}
knitr::kable(
    tab,
    format = "latex",
    caption = "Intensive- and Extensive-Margin Price Elasticity with Data in 2013 and 2014",
    col.names = c("", "", "k = 1", "k = 2", "k = 3"),
    row.names = FALSE,
    align = "lcccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 9) %>% 
add_header_above(c(" " = 1, "FE" = 1, "Panel IV with FE" = 3)) %>% 
pack_rows("Intensive Margin", 1, 4) %>% 
pack_rows("Extensive Margin", 5, 10)
```

