
```{r setup, include = FALSE, echo = FALSE}
library(here)
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  echo = FALSE, 
  cache = FALSE,
  include = FALSE,
  fig.width = 10, fig.height = 6,
  fig.align = "center"
)
knitr::opts_knit$set(root.dir = here())

library(tidyverse)
library(readstata13)
library(kableExtra)
options(knitr.kable.NA = "")
```


# Main Results

```{stata Elasticity, results = "hide", eval = FALSE}
xtreg log_total_g log_price log_pinc_all i.year, fe vce(cluster pid)

mat coeftab = r(table)["b".."pvalue", "log_price".."log_pinc_all"]
mat colnames coeftab = Logprice_M0 Loginc_M0

mat stattab = e(N) \ e(r2)
mat colnames stattab = M0
mat rownames stattab = N r2

predict resid, e

* with covariates
local cov sqage i.year##i.educ i.year##i.gender i.year##i.living_area
local xvars 
local k = 1
foreach v of local cov {
	di "model `k'"
    
	*make set of covariates
	local xvars `xvars' `v'
	
	*estimate fixed effect model
	xtreg log_total_g log_price log_pinc_all i.year age `xvars', fe vce(cluster pid)
	
	*matrix of regression result
	mat coef = r(table)["b".."pvalue","log_price".."log_pinc_all"]
	mat colnames coef = Logprice_M`k' Loginc_M`k'
	
	mat stat = e(N) \ e(r2)
	mat colnames stat = M`k'
	mat rownames stat = N r2
	
	*combined with previous results
	mat_capp coeftab : coeftab coef
	mat_capp stattab : stattab stat

	local k = `++k'
}

mat list coeftab
mat list stattab

xsvmat coeftab, saving(_assets/ElasticityCoef.dta, replace) rownames(xvar) names(col)
xsvmat stattab, saving(_assets/ElasticityStat.dta, replace) rownames(xvar) names(col)

* residuals plot
frame copy default plotdt
frame plotdt {
	by year benefit_group, sort: egen meang = mean(resid)
	
	keep meang year benefit_group
	duplicates drop
	keep if !missing(benefit_group)
	
	gen meang_norm = meang if year == 2013
	by benefit_group, sort: egen meang13 = mean(meang_norm) 
	gen meang_n = meang - meang13
}

frame plotdt {
	twoway ///
	(connected meang_n year if benefit_group == 1, sort msymbol(O) color(black))  ///
	(connected meang_n year if benefit_group == 2, sort msymbol(T) color(black))  ///
	(connected meang_n year if benefit_group == 3, sort msymbol(S) color(black)),  ///
	xline(2013.5, lcolor(red) lpattern(-)) ///
	xlabel(2012(1)2018) xtitle("Year")  ///
	ytitle("Average Residuals (Normalized)")  ///
	legend(label(1 "Income {&lt} 1200") label(2 " Income in [1200, 4600)") label(3 "Income {&ge} 4600"))  ///
	graphregion(fcolor(white))

	graph export "_assets/ElasticityResid.pdf", replace
}

frame drop plotdt
```

```{stata ExtElasticity, results = "hide", eval = FALSE}
* baseline
xtreg i_ext_giving log_price log_pinc_all i.year, fe vce(cluster pid)

mat coeftab = r(table)["b".."pvalue", "log_price".."log_pinc_all"]
mat colnames coeftab = Logprice_M0 Loginc_M0

mat stattab = e(N) \ e(r2)
mat colnames stattab = M0
mat rownames stattab = N r

predict residext, e

* price elasticity evaluated at mean
summarize i_ext_giving
local mu = r(mean)
lincom log_price*(1/`mu')

mat elas1 = r(estimate) \ r(se) \ ttail(r(df), abs(r(estimate)/r(se)))*2
mat colnames elas1 = Logprice_M0
mat rownames elas1 = e_b e_se e_pval

* price elasticity evaluated at mean
summarize i_ext_giving
local mu = r(mean)
lincom log_pinc_all*(1/`mu')

mat elas2 = r(estimate) \ r(se) \ ttail(r(df), abs(r(estimate)/r(se)))*2
mat colnames elas2 = Loginc_M0
mat rownames elas2 = e_b e_se e_pval

* baseline result
mat_capp elas : elas1 elas2
mat_rapp coeftab : coeftab elas


* with covariates
local cov sqage i.year##i.educ i.year##i.gender i.year##i.living_area
local xvars 
local k = 1
foreach v of local cov {
	di "model `k'"
    
	*make set of covariates
	local xvars `xvars' `v'
	
	*estimate fixed effect model
	xtreg i_ext_giving log_price log_pinc_all i.year age `xvars', fe vce(cluster pid)
	
	*matrix of regression result
	mat coef = r(table)["b".."pvalue", "log_price".."log_pinc_all"]
	mat colnames coef = Logprice_M`k' Loginc_M`k'

	mat stat = e(N) \ e(r2)
	mat colnames stat = M`k'
	mat rownames stat = N r
	
	*proportion of donors
	summarize i_ext_giving
	local mu = r(mean)
	
	* price elasticity evaluated at mean
	summarize i_ext_giving
	local mu = r(mean)
	lincom log_price*(1/`mu')

	mat elas1 = r(estimate) \ r(se) \ ttail(r(df), abs(r(estimate)/r(se)))*2
	mat colnames elas1 = Logprice_M`k'
	mat rownames elas1 = e_b e_se e_pval

	* price elasticity evaluated at mean
	summarize i_ext_giving
	local mu = r(mean)
	lincom log_pinc_all*(1/`mu')

	mat elas2 = r(estimate) \ r(se) \ ttail(r(df), abs(r(estimate)/r(se)))*2
	mat colnames elas2 = Loginc_M`k'
	mat rownames elas2 = e_b e_se e_pval
	
	*combined with previous results
	mat_capp elas : elas1 elas2
	mat_rapp coef : coef elas
	mat_capp coeftab : coeftab coef
	
	mat_capp stattab : stattab stat

	local k = `++k'
}

mat list coeftab
mat list stattab

xsvmat coeftab, saving(_assets/ExtElasticityCoef.dta, replace) rownames(xvar) names(col)
xsvmat stattab, saving(_assets/ExtElasticityStat.dta, replace) rownames(xvar) names(col)

* residuals plot
frame copy default plotdt
frame plotdt {
	by year benefit_group, sort: egen meang = mean(residext)
	
	keep meang year benefit_group
	duplicates drop
	keep if !missing(benefit_group)
	
	gen meang_norm = meang if year == 2013
	by benefit_group, sort: egen meang13 = mean(meang_norm) 
	gen meang_n = meang - meang13
}

frame plotdt {
	twoway ///
	(connected meang_n year if benefit_group == 1, sort msymbol(O) color(black))  ///
	(connected meang_n year if benefit_group == 2, sort msymbol(T) color(black))  ///
	(connected meang_n year if benefit_group == 3, sort msymbol(S) color(black)),  ///
	xline(2013.5, lcolor(red) lpattern(-)) ///
	xlabel(2012(1)2018) xtitle("Year")  ///
	ytitle("Average Residuals (Normalized)")  ///
	legend(label(1 "Income {&lt} 1200") label(2 " Income in [1200, 4600)") label(3 "Income {&ge} 4600"))  ///
	graphregion(fcolor(white))

	graph export "_assets/ExtElasticityResid.pdf", replace
}

frame drop plotdt
```

```{stata IntElasticity, results = "hide", eval = FALSE}
* baseline
xtreg log_total_g log_price log_pinc_all i.year if i_ext_giving == 1, fe vce(cluster pid)

mat coeftab = r(table)["b".."pvalue", "log_price".."log_pinc_all"]
mat colnames coeftab = Logprice_M0 Loginc_M0

mat stattab = e(N) \ e(r2)
mat colnames stattab = M0
mat rownames stattab = N r2

predict residint, e

* with covariates
local cov sqage i.year##i.educ i.year##i.gender i.year##i.living_area
local xvars 
local k = 1
foreach v of local cov {
	di "model `k'"
    
	*make set of covariates
	local xvars `xvars' `v'
	
	*estimate fixed effect model
	xtreg log_total_g log_price log_pinc_all i.year age `xvars' if i_ext_giving == 1, fe vce(cluster pid)
	
	*matrix of regression result
	mat coef = r(table)["b".."pvalue","log_price".."log_pinc_all"]
	mat colnames coef = Logprice_M`k' Loginc_M`k'
	
	mat stat = e(N) \ e(r2)
	mat colnames stat = M`k'
	mat rownames stat = N r2
	
	*combined with previous results
	mat_capp coeftab : coeftab coef
	mat_capp stattab : stattab stat

	local k = `++k'
}

mat list coeftab
mat list stattab

xsvmat coeftab, saving(_assets/IntElasticityCoef.dta, replace) rownames(xvar) names(col)
xsvmat stattab, saving(_assets/IntElasticityStat.dta, replace) rownames(xvar) names(col)

* residuals plot
frame copy default plotdt
frame plotdt {
	by year benefit_group, sort: egen meang = mean(residint)
	
	keep meang year benefit_group
	duplicates drop
	keep if !missing(benefit_group)
	
	gen meang_norm = meang if year == 2013
	by benefit_group, sort: egen meang13 = mean(meang_norm) 
	gen meang_n = meang - meang13
}

frame plotdt {
	twoway ///
	(connected meang_n year if benefit_group == 1, sort msymbol(O) color(black))  ///
	(connected meang_n year if benefit_group == 2, sort msymbol(T) color(black))  ///
	(connected meang_n year if benefit_group == 3, sort msymbol(S) color(black)),  ///
	xline(2013.5, lcolor(red) lpattern(-)) ///
	xlabel(2012(1)2018) xtitle("Year")  ///
	ytitle("Average Residuals (Normalized)")  ///
	legend(label(1 "Income {&lt} 1200") label(2 " Income in [1200, 4600)") label(3 "Income {&ge} 4600"))  ///
	graphregion(fcolor(white))

	graph export "_assets/IntElasticityResid.pdf", replace
}

frame drop plotdt
```


## Price and Income Elasticity

- To show our baseline results graphically, Figure \@ref(fig:showElasticityResid) shows average residuals grouped by year and benefit of the 2014 tax reform.
    - Residuals are obtained from the regression of logged donations on logged annual taxable income, individual and time fixed year.

## Price and Income Elasticity: Residuals Plot

Those who incurring loss owing to the 2014 tax reform drastically decreases thier amount of donations.

```{r showElasticityResid, include = TRUE, out.width="80%", fig.cap="Average Residuals Grouped by Year and Tax-Reform Benefit Group"}
knitr::include_graphics(paste(here(), "_assets/ElasticityResid.pdf", sep= "/"))
```


## Price and Income Elasticity: Estimation Results

We found the **price effect** of giving (1\% price increase leads to about 1.1\% giving decrease),
and the **income effect** of giving(1\% income increase leads to about 5\% giving increase).

```{r shapeElasticity}
coeftab <- list(
	overall = read.dta13("_assets/ElasticityCoef.dta") %>% data.frame(),
	intensive = read.dta13("_assets/IntElasticityCoef.dta") %>% data.frame(),
	extensive = read.dta13("_assets/ExtElasticityCoef.dta") %>% data.frame()
)

shape_coeftab <- coeftab %>% 
	purrr::map(function(x)
		x %>% 
			filter(!str_detect(xvar, "e_")) %>%
			pivot_longer(-xvar, values_to = "value", names_to = c("vars", "model"), names_sep = "_") %>% 
			pivot_wider(values_from = "value", names_from = "xvar") %>% 
			mutate(
				b = case_when(
					pvalue <= 0.01 ~ sprintf("%1.3f***", b),
					pvalue <= 0.05 ~ sprintf("%1.3f**", b),
					pvalue <= 0.1 ~ sprintf("%1.3f*", b),
					TRUE ~ sprintf("%1.3f", b)
				),
				se = sprintf("(%1.3f)", se)
			) %>% 
			select(-t, -pvalue) %>% 
			pivot_longer(cols = b:se, values_to = "value", names_to = "stat") %>% 
			pivot_wider(values_from = "value", names_from = "model") %>%
			mutate(
				vars = case_when(
					stat == "se" ~ "",
					vars == "Logprice" ~ "ln(giving price)",
					vars == "Loginc" ~ "ln(auunaul taxable income)"
				)
			) %>% 
			select(-stat)
	)

elastab <- coeftab$extensive %>% 
	filter(str_detect(xvar, "e_")) %>%
	pivot_longer(-xvar, values_to = "value", names_to = c("vars", "model"), names_sep = "_") %>% 
	pivot_wider(values_from = "value", names_from = "xvar") %>% 
	mutate(
		e_b = case_when(
			e_pval <= 0.01 ~ sprintf("%1.3f***", e_b),
			e_pval <= 0.05 ~ sprintf("%1.3f**", e_b),
			e_pval <= 0.1 ~ sprintf("%1.3f*", e_b),
			TRUE ~ sprintf("%1.3f", e_b)
		),
		e_se = sprintf("(%1.3f)", e_se)
	) %>% 
	select(-e_pval) %>% 
	pivot_longer(cols = e_b:e_se, values_to = "value", names_to = "stat") %>% 
	pivot_wider(values_from = "value", names_from = "model") %>%
	mutate(
		vars = case_when(
			stat == "e_se" ~ "",
			vars == "Logprice" ~ "Implied price elasiticity",
			vars == "Loginc" ~ "Implied income elasticity"
		)
	) %>% 
	select(-stat)

shape_coeftab$extensive <- rbind(shape_coeftab$extensive, elastab)

stattab <- list(
	overall = read.dta13("_assets/ElasticityStat.dta") %>% data.frame(),
	intensive = read.dta13("_assets/IntElasticityStat.dta") %>% data.frame(),
	extensive = read.dta13("_assets/ExtElasticityStat.dta") %>% data.frame()
) %>% 
purrr::map(function(x) 
	x %>% mutate_at(
		vars(-xvar),
		list(~case_when(xvar == "N" ~ sprintf("%1.0f", .), TRUE ~ sprintf("%1.3f", .)))
	) %>% 
	mutate(xvar = recode(xvar, "r" = "R-sq", "r2" = "R-sq", .default = xvar)) %>% 
	rename(vars = xvar)
)

addline <- cbind(
	vars = c("Individual FE", "Time FE", "Age", "Year X Education", "Year X Gender", "Year X Resident Area"),
	M0 = c(rep("Y", 2), rep("N", 4)),
	M1 = c(rep("Y", 3), rep("N", 3)),
	M2 = c(rep("Y", 4), rep("N", 2)),
	M3 = c(rep("Y", 5), rep("N", 1)),
	M4 = rep("Y", 6)
)

tabular <- c("overall", "intensive", "extensive") %>% 
	purrr::map(function(x) rbind(shape_coeftab[[x]], addline) %>% rbind(stattab[[x]]))

alltab <- tabular[[1]]
intexttab <- rbind(tabular[[2]][-(5:10),], tabular[[3]])
```

```{r kableEstimateElasticityPart1, include = TRUE}
knitr::kable(
    alltab[-c(5:6, 12),],
    format = "latex",
    caption = "Main Results",
    col.names = c("", "(1)", "(2)", "(3)", "(4)", "(5)"),
    row.names = FALSE,
    align = "lccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 7) #%>% 
#footnote(general_title = "", general = "Notes: $^{*}$ $p < 0.1$, $^{**}$ $p < 0.05$, $^{***}$ $p < 0.01$. Standard errors are clustered at individual level. When controlling age, we alson include its squared term.", threeparttable = TRUE, escape = FALSE)
```


## Intensive and Extensive Margin

- To obtain intensive- and extensive-margin elasticity, we repeat the same excercise.
- \@ref(fig:showIntElasticityResid) shows average residuals grouped by year and benefit of the 2014 tax reform 
    - We used those who donated and estimated residuals obtained from the regression logged donations on logged annual taxable income, individual and time fixed year.
- \@ref(fig:showExtElasticityResid) shows average residuals grouped by year and benefir of the 2014 tax reform.
    - We estimated residuals obtained from the regression the donation dummy on logged annual taxable income, individual and time fixed year.

## Intensive Margin: Residuals Plot

Donors who receive benefit owing to the 2014 tax reform decrease their donations in 2014 and 2015.

```{r showIntElasticityResid, include = TRUE, out.width="80%", fig.cap="Average Residuals Grouped by Year and Tax-Reform Benefit Group (Intensive Margin)"}
knitr::include_graphics(paste(here(), "_assets/IntElasticityResid.pdf", sep= "/"))
```

## Extensive Margin: Residuals Plot

Those who incurring loss owing to the 2014 tax reform drastically were less likely to donate.

```{r showExtElasticityResid, include = TRUE, out.width="80%", fig.cap="Average Residuals Grouped by Year and Tax-Reform Benefit Group (Extensive Margin)"}
knitr::include_graphics(paste(here(), "_assets/ExtElasticityResid.pdf", sep= "/"))
```

## Intensive and Extensive Margin: Estimation Results

The intensive-margin price elasticity is -0.5 ~ -1\%. 

```{r kableEstimateElasticityPart2Slide1, include = TRUE}
knitr::kable(
    rbind(intexttab[1:4,], intexttab[17:20,]) %>% rbind(intexttab[5,]),
    format = "latex",
    caption = "Main Results: Intensive-Margin Elasticity",
    col.names = c("", "(1)", "(2)", "(3)", "(4)", "(5)"),
    row.names = FALSE,
    align = "lccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 7)
```

## Intensive and Extensive Margin: Estimation Results

The extensive-margin price elasticity is -1.2 ~ -1.4\%. 

```{r kableEstimateElasticityPart2Slide2, include = TRUE}
knitr::kable(
    rbind(intexttab[11:14,], intexttab[17:21,]),
    format = "latex",
    caption = "Main Results: Extensive-Margin Elasticity",
    col.names = c("", "(1)", "(2)", "(3)", "(4)", "(5)"),
    row.names = FALSE,
    align = "lccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 7)
```

<!--- For Paper
```{r kableEstimateElasticityPart2, include = TRUE, eval = FALSE}
knitr::kable(
    intexttab,
    format = "latex",
    caption = "Main Results: Intensive- and Extensive-Margin Elasticity",
    col.names = c("", "(1)", "(2)", "(3)", "(4)", "(5)"),
    row.names = FALSE,
    align = "lccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 8) %>% 
pack_rows("Intensive-Margin Elasticity", 1, 6) %>% 
pack_rows("Extensive-Margin Elasticity", 7, 22) %>% 
footnote(general_title = "", general = "Notes: $^{*}$ $p < 0.1$, $^{**}$ $p < 0.05$, $^{***}$ $p < 0.01$. Standard errors are clustered at individual level. When controlling age, we alson include its squared term. The implied extensive-marign price elasticity is evaluated at the sample mean of $D_{ijt}$.", threeparttable = TRUE, escape = FALSE)
```
--->

## Robustness Check 1

First potential concern: last price elasticity

- Our baseline results show the **first** price elasticity to avoid the endogeneity of giving price.
- We estimated the **last** price elasticity, using the Panel IV method.
    - The instrument is the first giving price.
    - Note that the last giving price is equal to the first giving price under the tax credit system.

```{stata LastElasticity, results = "hide", eval = FALSE}
* first stage
xtreg log_lprice log_price log_pinc_all i.year, fe vce(cluster pid)

mat fstage = r(table)["b".."pvalue","log_price"]
mat fstage = fstage[1,1] \ fstage[3,1]^2
mat colnames fstage = M0
mat rownames fstage = ivcoef ivf

* second stage
xtivreg log_total_g log_pinc_all i.year (log_lprice = log_price), fe vce(cluster pid)

mat coeftab = r(table)["b".."pvalue", "log_lprice".."log_pinc_all"]
mat colnames coeftab = Loglprice_M0 Loginc_M0

mat stattab = e(N) \ e(r2)
mat colnames stattab = M0
mat rownames stattab = N r2

mat_rapp stattab : stattab fstage

* with covariates
local cov sqage i.year##i.educ i.year##i.gender i.year##i.living_area
local xvars 
local k = 1
foreach v of local cov {
	di "model `k'"
    
	*make set of covariates
	local xvars `xvars' `v'
	
	*first stage
	xtreg log_lprice log_price log_pinc_all i.year age `xvars', fe vce(cluster pid)
	
	mat fstage = r(table)["b".."pvalue","log_price"]
	mat fstage = fstage[1,1] \ fstage[3,1]^2
	mat colnames fstage = M`k'
	mat rownames fstage = ivcoef ivf
	
	*second stage
	xtivreg log_total_g log_pinc_all i.year age `xvars' (log_lprice = log_price), fe vce(cluster pid)
	
	mat coef = r(table)["b".."pvalue", "log_lprice".."log_pinc_all"]
	mat colnames coef = Loglprice_M`k' Loginc_M`k'

	mat stat = e(N) \ e(r2)
	mat colnames stat = M`k'
	mat rownames stat = N r2
	
	mat_rapp stat : stat fstage
	
	*combined with previous results
	mat_capp coeftab : coeftab coef
	mat_capp stattab : stattab stat

	local k = `++k'
}

mat list coeftab
mat list stattab

xsvmat coeftab, saving(_assets/LastElasticityCoef.dta, replace) rownames(xvar) names(col)
xsvmat stattab, saving(_assets/LastElasticityStat.dta, replace) rownames(xvar) names(col)
```

```{stata LastExtElasticity, results = "hide", eval = FALSE}
* first stage
xtreg log_lprice log_price log_pinc_all i.year, fe vce(cluster pid)

mat fstage = r(table)["b".."pvalue","log_price"]
mat fstage = fstage[1,1] \ fstage[3,1]^2
mat colnames fstage = M0
mat rownames fstage = ivcoef ivf

* second stage
xtivreg i_ext_giving log_pinc_all i.year (log_lprice = log_price), fe vce(cluster pid)

mat coeftab = r(table)["b".."pvalue", "log_lprice".."log_pinc_all"]
mat colnames coeftab = Loglprice_M0 Loginc_M0

mat stattab = e(N) \ e(r2)
mat colnames stattab = M0
mat rownames stattab = N r2

* price elasticity evaluated at mean
summarize i_ext_giving
local mu = r(mean)
lincom log_lprice*(1/`mu')

mat elas1 = r(estimate) \ r(se) \ (1 - normal(abs(r(estimate)/r(se))))*2
mat colnames elas1 = Loglprice_M0
mat rownames elas1 = e_b e_se e_pval

* price elasticity evaluated at mean
summarize i_ext_giving
local mu = r(mean)
lincom log_pinc_all*(1/`mu')

mat elas2 = r(estimate) \ r(se) \ (1 - normal(abs(r(estimate)/r(se))))*2
mat colnames elas2 = Loginc_M0
mat rownames elas2 = e_b e_se e_pval

mat_capp elas : elas1 elas2
mat_rapp coeftab : coeftab elas
mat_rapp stattab : stattab fstage

* with covariates
local cov sqage i.year##i.educ i.year##i.gender i.year##i.living_area
local xvars 
local k = 1
foreach v of local cov {
	di "model `k'"
    
	*make set of covariates
	local xvars `xvars' `v'
	
	*first stage
	xtreg log_lprice log_price log_pinc_all i.year age `xvars', fe vce(cluster pid)
	
	mat fstage = r(table)["b".."pvalue","log_price"]
	mat fstage = fstage[1,1] \ fstage[3,1]^2
	mat colnames fstage = M`k'
	mat rownames fstage = ivcoef ivf
	
	*second stage
	xtivreg i_ext_giving log_pinc_all i.year age `xvars' (log_lprice = log_price), fe vce(cluster pid)
	
	mat coef = r(table)["b".."pvalue", "log_lprice".."log_pinc_all"]
	mat colnames coef = Loglprice_M`k' Loginc_M`k'

	mat stat = e(N) \ e(r2)
	mat colnames stat = M`k'
	mat rownames stat = N r2
	
	* price elasticity evaluated at mean
	summarize i_ext_giving
	local mu = r(mean)
	lincom log_lprice*(1/`mu')

	mat elas1 = r(estimate) \ r(se) \ (1 - normal(abs(r(estimate)/r(se))))*2
	mat colnames elas1 = Loglprice_M`k'
	mat rownames elas1 = e_b e_se e_pval

	* price elasticity evaluated at mean
	summarize i_ext_giving
	local mu = r(mean)
	lincom log_pinc_all*(1/`mu')

	mat elas2 = r(estimate) \ r(se) \ (1 - normal(abs(r(estimate)/r(se))))*2
	mat colnames elas2 = Loginc_M`k'
	mat rownames elas2 = e_b e_se e_pval

	mat_capp elas : elas1 elas2
	mat_rapp coef : coef elas
	mat_rapp stat : stat fstage
	
	*combined with previous results
	mat_capp coeftab : coeftab coef
	mat_capp stattab : stattab stat

	local k = `++k'
}

mat list coeftab
mat list stattab

xsvmat coeftab, saving(_assets/LastExtElasticityCoef.dta, replace) rownames(xvar) names(col)
xsvmat stattab, saving(_assets/LastExtElasticityStat.dta, replace) rownames(xvar) names(col)
```

```{stata LastIntElasticity, results = "hide", eval = FALSE}
* first stage
xtreg log_lprice log_price log_pinc_all i.year if i_ext_giving == 1, fe vce(cluster pid)

mat fstage = r(table)["b".."pvalue","log_price"]
mat fstage = fstage[1,1] \ fstage[3,1]^2
mat colnames fstage = M0
mat rownames fstage = ivcoef ivf

* second stage
xtivreg log_total_g log_pinc_all i.year (log_lprice = log_price) if i_ext_giving == 1, fe vce(cluster pid)

mat coeftab = r(table)["b".."pvalue", "log_lprice".."log_pinc_all"]
mat colnames coeftab = Loglprice_M0 Loginc_M0

mat stattab = e(N) \ e(r2)
mat colnames stattab = M0
mat rownames stattab = N r2

mat_rapp stattab : stattab fstage

* with covariates
local cov sqage i.year##i.educ i.year##i.gender i.year##i.living_area
local xvars 
local k = 1
foreach v of local cov {
	di "model `k'"
    
	*make set of covariates
	local xvars `xvars' `v'
	
	*first stage
	xtreg log_lprice log_price log_pinc_all i.year age `xvars' if i_ext_giving == 1, fe vce(cluster pid)
	
	mat fstage = r(table)["b".."pvalue","log_price"]
	mat fstage = fstage[1,1] \ fstage[3,1]^2
	mat colnames fstage = M`k'
	mat rownames fstage = ivcoef ivf
	
	*second stage
	xtivreg log_total_g log_pinc_all i.year age `xvars' (log_lprice = log_price) if i_ext_giving == 1, fe vce(cluster pid)
	
	mat coef = r(table)["b".."pvalue", "log_lprice".."log_pinc_all"]
	mat colnames coef = Loglprice_M`k' Loginc_M`k'

	mat stat = e(N) \ e(r2)
	mat colnames stat = M`k'
	mat rownames stat = N r2
	
	mat_rapp stat : stat fstage
	
	*combined with previous results
	mat_capp coeftab : coeftab coef
	mat_capp stattab : stattab stat

	local k = `++k'
}

mat list coeftab
mat list stattab

xsvmat coeftab, saving(_assets/LastIntElasticityCoef.dta, replace) rownames(xvar) names(col)
xsvmat stattab, saving(_assets/LastIntElasticityStat.dta, replace) rownames(xvar) names(col)
```


## Robustness Check 1: Result

Overall last price elasticity increases twofold.

```{r shapeLastElasticity}
coeftab <- list(
	overall = read.dta13("_assets/LastElasticityCoef.dta") %>% data.frame(),
	intensive = read.dta13("_assets/LastIntElasticityCoef.dta") %>% data.frame(),
	extensive = read.dta13("_assets/LastExtElasticityCoef.dta") %>% data.frame()
)

shape_coeftab <- coeftab %>% 
	purrr::map(function(x)
		x %>% 
			filter(!str_detect(xvar, "e_")) %>%
			pivot_longer(-xvar, values_to = "value", names_to = c("vars", "model"), names_sep = "_") %>% 
			pivot_wider(values_from = "value", names_from = "xvar") %>% 
			mutate(
				b = case_when(
					pvalue <= 0.01 ~ sprintf("%1.3f***", b),
					pvalue <= 0.05 ~ sprintf("%1.3f**", b),
					pvalue <= 0.1 ~ sprintf("%1.3f*", b),
					TRUE ~ sprintf("%1.3f", b)
				),
				se = sprintf("(%1.3f)", se)
			) %>% 
			select(-z, -pvalue) %>% 
			pivot_longer(cols = b:se, values_to = "value", names_to = "stat") %>% 
			pivot_wider(values_from = "value", names_from = "model") %>%
			mutate(
				vars = case_when(
					stat == "se" ~ "",
					vars == "Loglprice" ~ "ln(last giving price)",
					vars == "Loginc" ~ "ln(auunaul taxable income)"
				)
			) %>% 
			select(-stat)
	)

elastab <- coeftab$extensive %>% 
	filter(str_detect(xvar, "e_")) %>%
	pivot_longer(-xvar, values_to = "value", names_to = c("vars", "model"), names_sep = "_") %>% 
	pivot_wider(values_from = "value", names_from = "xvar") %>% 
	mutate(
		e_b = case_when(
			e_pval <= 0.01 ~ sprintf("%1.3f***", e_b),
			e_pval <= 0.05 ~ sprintf("%1.3f**", e_b),
			e_pval <= 0.1 ~ sprintf("%1.3f*", e_b),
			TRUE ~ sprintf("%1.3f", e_b)
		),
		e_se = sprintf("(%1.3f)", e_se)
	) %>% 
	select(-e_pval) %>% 
	pivot_longer(cols = e_b:e_se, values_to = "value", names_to = "stat") %>% 
	pivot_wider(values_from = "value", names_from = "model") %>%
	mutate(
		vars = case_when(
			stat == "e_se" ~ "",
			vars == "Loglprice" ~ "Implied last price elasiticity",
			vars == "Loginc" ~ "Implied income elasticity"
		)
	) %>% 
	select(-stat)

shape_coeftab$extensive <- rbind(shape_coeftab$extensive, elastab)

stattab <- list(
	overall = read.dta13("_assets/LastElasticityStat.dta") %>% data.frame(),
	intensive = read.dta13("_assets/LastIntElasticityStat.dta") %>% data.frame(),
	extensive = read.dta13("_assets/LastExtElasticityStat.dta") %>% data.frame()
) %>% 
purrr::map(function(x) 
	x %>% mutate_at(
		vars(-xvar),
		list(~case_when(xvar == "N" ~ sprintf("%1.0f", .), TRUE ~ sprintf("%1.2f", .)))
	) %>% 
	mutate(xvar = recode(xvar, "r2" = "R-sq", "ivf" = "F-statistics of IV", .default = xvar)) %>% 
	rename(vars = xvar) %>% 
	filter(vars != "R-sq" & vars != "ivcoef") %>% 
	.[c(2,1),]
)

addline <- cbind(
	vars = c("Individual FE", "Time FE", "Age", "Year X Education", "Year X Gender", "Year X Resident Area"),
	M0 = c(rep("Y", 2), rep("N", 4)),
	M1 = c(rep("Y", 3), rep("N", 3)),
	M2 = c(rep("Y", 4), rep("N", 2)),
	M3 = c(rep("Y", 5), rep("N", 1)),
	M4 = rep("Y", 6)
)

tabular <- c("overall", "intensive", "extensive") %>% 
	purrr::map(function(x) rbind(shape_coeftab[[x]], addline) %>% rbind(stattab[[x]]))

alltab <- tabular[[1]]
intexttab <- rbind(tabular[[2]][-(5:10),], tabular[[3]])
```

```{r kableLastElasticity1, include = TRUE}
knitr::kable(
    alltab[-c(5:6, 11),],
    format = "latex",
    caption = "Last Price Elasticity: Panel IV",
    col.names = c("", "(1)", "(2)", "(3)", "(4)", "(5)"),
    row.names = FALSE,
    align = "lccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 7) #%>% 
#footnote(general_title = "", general = "Notes: $^{*}$ $p < 0.1$, $^{**}$ $p < 0.05$, $^{***}$ $p < 0.01$. Standard errors are clustered at individual level. The instumental variable is the first giving price in year $t$. When controlling age, we alson include its squared term.", threeparttable = TRUE, escape = FALSE)
```


## Robustness Check 1: Intensive Margin

The intensive-margin last price elasticity lies within the range of the first price elasticity.

```{r kableLastElasticity2Slide1, include = TRUE}
knitr::kable(
    rbind(intexttab[1:4,], intexttab[17:20,]) %>% rbind(intexttab[6,]),
    format = "latex",
    caption = "Intensive-Margin Last Price Elasticity: Panel IV",
    col.names = c("", "(1)", "(2)", "(3)", "(4)", "(5)"),
    row.names = FALSE,
    align = "lccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 7)
```

## Robustness Check 1: Extensive Margin

The extensive-margin last price elasticity at sample mean is roughly -3\%.

```{r kableLastElasticity2Slide2, include = TRUE}
knitr::kable(
    rbind(intexttab[11:14,], intexttab[17:20,]) %>% rbind(intexttab[22,]),
    format = "latex",
    caption = "Extensive-Margin Last Price Elasticity: Panel IV",
    col.names = c("", "(1)", "(2)", "(3)", "(4)", "(5)"),
    row.names = FALSE,
    align = "lccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 7)
```

<!--- Paper
```{r kableLastElasticity2, include = TRUE, eval = FALSE}
knitr::kable(
    intexttab,
    format = "latex",
    caption = "Intensive- and Extensive-Margin Last Price Elasticity: Panel IV",
    col.names = c("", "(1)", "(2)", "(3)", "(4)", "(5)"),
    row.names = FALSE,
    align = "lccccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 8) %>% 
pack_rows("Intensive-Margin Elasticity", 1, 6) %>% 
pack_rows("Extensive-Margin Elasticity", 7, 22) %>% 
footnote(general_title = "", general = "Notes: $^{*}$ $p < 0.1$, $^{**}$ $p < 0.05$, $^{***}$ $p < 0.01$. Standard errors are clustered at individual level. The instumental variable is the first giving price in year $t$. When controlling age, we alson include its squared term. The implied extensive-marign price elasticity is evaluated at the sample mean of $D_{ijt}$.", threeparttable = TRUE, escape = FALSE)
```
--->


## Robust Check 2

Second potential concern: Price change due to the change of income
    
- Since the giving price under the tax deduction depends on the change of income, the *within* variation of giving price may be endogenous.
- To resolve this concern, we used the data (i) from 2013 to 2018 or (ii) from 2013 to 2014, and estimated the fixed effect model.
    - By this restriction, the *within* price variation of giving price is completely exgonenous.


```{stata ShortElasticity, results = "hide", eval = FALSE}
* M0: year >= 2013 without cov
xtreg log_total_g log_price log_pinc_all i.year if year >= 2013, fe vce(cluster pid)

mat coeftab0 = r(table)["b".."pvalue", "log_price".."log_pinc_all"]
mat colnames coeftab0 = Logprice_M0 Loginc_M0

mat stattab0 = e(N) \ e(r2)
mat colnames stattab0 = M0
mat rownames stattab0 = N r2

* M1: year >= 2013 with cov
xtreg log_total_g log_price log_pinc_all i.year age sqage i.year##i.educ i.year##i.gender i.year##i.living_area ///
	if year >= 2013, fe vce(cluster pid)

mat coeftab1 = r(table)["b".."pvalue", "log_price".."log_pinc_all"]
mat colnames coeftab1 = Logprice_M1 Loginc_M1

mat stattab1 = e(N) \ e(r2)
mat colnames stattab1 = M1
mat rownames stattab1 = N r2

* M2: year == 2013 | 2014 without cov
xtreg log_total_g log_price log_pinc_all i.year if year == 2013 | year == 2014, fe vce(cluster pid)

mat coeftab2 = r(table)["b".."pvalue", "log_price".."log_pinc_all"]
mat colnames coeftab2 = Logprice_M2 Loginc_M2

mat stattab2 = e(N) \ e(r2)
mat colnames stattab2 = M2
mat rownames stattab2 = N r2

* M3: year == 2013 | 2014 with cov
xtreg log_total_g log_price log_pinc_all i.year age sqage i.year##i.educ i.year##i.gender i.year##i.living_area ///
	if year == 2013 | year == 2014, fe vce(cluster pid)

mat coeftab3 = r(table)["b".."pvalue", "log_price".."log_pinc_all"]
mat colnames coeftab3 = Logprice_M3 Loginc_M3

mat stattab3 = e(N) \ e(r2)
mat colnames stattab3 = M3
mat rownames stattab3 = N r2

mat_capp coeftab : coeftab0 coeftab1
mat_capp coeftab : coeftab coeftab2
mat_capp coeftab : coeftab coeftab3

mat_capp stattab : stattab0 stattab1
mat_capp stattab : stattab stattab2
mat_capp stattab : stattab stattab3

mat list coeftab
mat list stattab

xsvmat coeftab, saving(_assets/ShortElasticityCoef.dta, replace) rownames(xvar) names(col)
xsvmat stattab, saving(_assets/ShortElasticityStat.dta, replace) rownames(xvar) names(col)
```

```{stata ShortIntElasticity, results = "hide", eval = FALSE}
* M0: year >= 2013 without cov
xtreg log_total_g log_price log_pinc_all i.year if year >= 2013 & i_ext_giving == 1, fe vce(cluster pid)

mat coeftab0 = r(table)["b".."pvalue", "log_price".."log_pinc_all"]
mat colnames coeftab0 = Logprice_M0 Loginc_M0

mat stattab0 = e(N) \ e(r2)
mat colnames stattab0 = M0
mat rownames stattab0 = N r2

* M1: year >= 2013 with cov
xtreg log_total_g log_price log_pinc_all i.year age sqage i.year##i.educ i.year##i.gender i.year##i.living_area ///
	if year >= 2013 & i_ext_giving == 1, fe vce(cluster pid)

mat coeftab1 = r(table)["b".."pvalue", "log_price".."log_pinc_all"]
mat colnames coeftab1 = Logprice_M1 Loginc_M1

mat stattab1 = e(N) \ e(r2)
mat colnames stattab1 = M1
mat rownames stattab1 = N r2

* M2: year == 2013 | 2014 without cov
xtreg log_total_g log_price log_pinc_all i.year if (year == 2013 | year == 2014) & i_ext_giving == 1, fe vce(cluster pid)

mat coeftab2 = r(table)["b".."pvalue", "log_price".."log_pinc_all"]
mat colnames coeftab2 = Logprice_M2 Loginc_M2

mat stattab2 = e(N) \ e(r2)
mat colnames stattab2 = M2
mat rownames stattab2 = N r2

* M3: year == 2013 | 2014 with cov
xtreg log_total_g log_price log_pinc_all i.year age sqage i.year##i.educ i.year##i.gender i.year##i.living_area ///
	if (year == 2013 | year == 2014) & i_ext_giving == 1, fe vce(cluster pid)

mat coeftab3 = r(table)["b".."pvalue", "log_price".."log_pinc_all"]
mat colnames coeftab3 = Logprice_M3 Loginc_M3

mat stattab3 = e(N) \ e(r2)
mat colnames stattab3 = M3
mat rownames stattab3 = N r2

mat_capp coeftab : coeftab0 coeftab1
mat_capp coeftab : coeftab coeftab2
mat_capp coeftab : coeftab coeftab3

mat_capp stattab : stattab0 stattab1
mat_capp stattab : stattab stattab2
mat_capp stattab : stattab stattab3

mat list coeftab
mat list stattab

xsvmat coeftab, saving(_assets/ShortIntElasticityCoef.dta, replace) rownames(xvar) names(col)
xsvmat stattab, saving(_assets/ShortIntElasticityStat.dta, replace) rownames(xvar) names(col)
```

```{stata ShortExtElasticity, results = "hide", eval = FALSE}
** M0: year >= 2013 without cov
xtreg i_ext_giving log_price log_pinc_all i.year if year >= 2013, fe vce(cluster pid)

mat coeftab0 = r(table)["b".."pvalue", "log_price".."log_pinc_all"]
mat colnames coeftab0 = Logprice_M0 Loginc_M0

mat stattab0 = e(N) \ e(r2)
mat colnames stattab0 = M0
mat rownames stattab0 = N r2

* price elasticity evaluated at mean
summarize i_ext_giving if year >= 2013
local mu = r(mean)
lincom log_price*(1/`mu')

mat elas1 = r(estimate) \ r(se) \ ttail(r(df), abs(r(estimate)/r(se)))*2
mat colnames elas1 = Logprice_M0
mat rownames elas1 = e_b e_se e_pval

* price elasticity evaluated at mean
summarize i_ext_giving if year >= 2013
local mu = r(mean)
lincom log_pinc_all*(1/`mu')

mat elas2 = r(estimate) \ r(se) \ ttail(r(df), abs(r(estimate)/r(se)))*2
mat colnames elas2 = Loginc_M0
mat rownames elas2 = e_b e_se e_pval

mat_capp elas : elas1 elas2
mat_rapp coeftab0 : coeftab0 elas

** M1: year >= 2013 with cov
xtreg i_ext_giving log_price log_pinc_all i.year age sqage i.year##i.educ i.year##i.gender i.year##i.living_area ///
	if year >= 2013, fe vce(cluster pid)

mat coeftab1 = r(table)["b".."pvalue", "log_price".."log_pinc_all"]
mat colnames coeftab1 = Logprice_M1 Loginc_M1

mat stattab1 = e(N) \ e(r2)
mat colnames stattab1 = M1
mat rownames stattab1 = N r2

* price elasticity evaluated at mean
summarize i_ext_giving if year >= 2013
local mu = r(mean)
lincom log_price*(1/`mu')

mat elas1 = r(estimate) \ r(se) \ ttail(r(df), abs(r(estimate)/r(se)))*2
mat colnames elas1 = Logprice_M1
mat rownames elas1 = e_b e_se e_pval

* price elasticity evaluated at mean
summarize i_ext_giving if year >= 2013
local mu = r(mean)
lincom log_pinc_all*(1/`mu')

mat elas2 = r(estimate) \ r(se) \ ttail(r(df), abs(r(estimate)/r(se)))*2
mat colnames elas2 = Loginc_M1
mat rownames elas2 = e_b e_se e_pval

mat_capp elas : elas1 elas2
mat_rapp coeftab1 : coeftab1 elas

** M2: year == 2013 | 2014 without cov
xtreg i_ext_giving log_price log_pinc_all i.year if year == 2013 | year == 2014, fe vce(cluster pid)

mat coeftab2 = r(table)["b".."pvalue", "log_price".."log_pinc_all"]
mat colnames coeftab2 = Logprice_M2 Loginc_M2

mat stattab2 = e(N) \ e(r2)
mat colnames stattab2 = M2
mat rownames stattab2 = N r2

* price elasticity evaluated at mean
summarize i_ext_giving if year == 2013 | year == 2014
local mu = r(mean)
lincom log_price*(1/`mu')

mat elas1 = r(estimate) \ r(se) \ ttail(r(df), abs(r(estimate)/r(se)))*2
mat colnames elas1 = Logprice_M2
mat rownames elas1 = e_b e_se e_pval

* price elasticity evaluated at mean
summarize i_ext_giving if year == 2013 | year == 2014
local mu = r(mean)
lincom log_pinc_all*(1/`mu')

mat elas2 = r(estimate) \ r(se) \ ttail(r(df), abs(r(estimate)/r(se)))*2
mat colnames elas2 = Loginc_M2
mat rownames elas2 = e_b e_se e_pval

mat_capp elas : elas1 elas2
mat_rapp coeftab2 : coeftab2 elas

** M3: year == 2013 | 2014 with cov
xtreg i_ext_giving log_price log_pinc_all i.year age sqage i.year##i.educ i.year##i.gender i.year##i.living_area ///
	if year == 2013 | year == 2014, fe vce(cluster pid)

mat coeftab3 = r(table)["b".."pvalue", "log_price".."log_pinc_all"]
mat colnames coeftab3 = Logprice_M3 Loginc_M3

mat stattab3 = e(N) \ e(r2)
mat colnames stattab3 = M3
mat rownames stattab3 = N r2

* price elasticity evaluated at mean
summarize i_ext_giving if year == 2013 | year == 2014
local mu = r(mean)
lincom log_price*(1/`mu')

mat elas1 = r(estimate) \ r(se) \ ttail(r(df), abs(r(estimate)/r(se)))*2
mat colnames elas1 = Logprice_M3
mat rownames elas1 = e_b e_se e_pval

* price elasticity evaluated at mean
summarize i_ext_giving if year == 2013 | year == 2014
local mu = r(mean)
lincom log_pinc_all*(1/`mu')

mat elas2 = r(estimate) \ r(se) \ ttail(r(df), abs(r(estimate)/r(se)))*2
mat colnames elas2 = Loginc_M3
mat rownames elas2 = e_b e_se e_pval

mat_capp elas : elas1 elas2
mat_rapp coeftab3 : coeftab3 elas

mat_capp coeftab : coeftab0 coeftab1
mat_capp coeftab : coeftab coeftab2
mat_capp coeftab : coeftab coeftab3

mat_capp stattab : stattab0 stattab1
mat_capp stattab : stattab stattab2
mat_capp stattab : stattab stattab3

mat list coeftab
mat list stattab

xsvmat coeftab, saving(_assets/ShortExtElasticityCoef.dta, replace) rownames(xvar) names(col)
xsvmat stattab, saving(_assets/ShortExtElasticityStat.dta, replace) rownames(xvar) names(col)
```

```{r shapeShortElasticity}
coeftab <- list(
	overall = read.dta13("_assets/ShortElasticityCoef.dta") %>% data.frame(),
	intensive = read.dta13("_assets/ShortIntElasticityCoef.dta") %>% data.frame(),
	extensive = read.dta13("_assets/ShortExtElasticityCoef.dta") %>% data.frame()
)

shape_coeftab <- coeftab %>% 
	purrr::map(function(x)
		x %>% 
			filter(!str_detect(xvar, "e_")) %>%
			pivot_longer(-xvar, values_to = "value", names_to = c("vars", "model"), names_sep = "_") %>% 
			pivot_wider(values_from = "value", names_from = "xvar") %>% 
			mutate(
				b = case_when(
					pvalue <= 0.01 ~ sprintf("%1.3f***", b),
					pvalue <= 0.05 ~ sprintf("%1.3f**", b),
					pvalue <= 0.1 ~ sprintf("%1.3f*", b),
					TRUE ~ sprintf("%1.3f", b)
				),
				se = sprintf("(%1.3f)", se)
			) %>% 
			select(-t, -pvalue) %>% 
			pivot_longer(cols = b:se, values_to = "value", names_to = "stat") %>% 
			pivot_wider(values_from = "value", names_from = "model") %>%
			mutate(
				vars = case_when(
					stat == "se" ~ "",
					vars == "Logprice" ~ "ln(giving price)",
					vars == "Loginc" ~ "ln(auunaul taxable income)"
				)
			) %>% 
			select(-stat)
	)

elastab <- coeftab$extensive %>% 
	filter(str_detect(xvar, "e_")) %>%
	pivot_longer(-xvar, values_to = "value", names_to = c("vars", "model"), names_sep = "_") %>% 
	pivot_wider(values_from = "value", names_from = "xvar") %>% 
	mutate(
		e_b = case_when(
			e_pval <= 0.01 ~ sprintf("%1.3f***", e_b),
			e_pval <= 0.05 ~ sprintf("%1.3f**", e_b),
			e_pval <= 0.1 ~ sprintf("%1.3f*", e_b),
			TRUE ~ sprintf("%1.3f", e_b)
		),
		e_se = sprintf("(%1.3f)", e_se)
	) %>% 
	select(-e_pval) %>% 
	pivot_longer(cols = e_b:e_se, values_to = "value", names_to = "stat") %>% 
	pivot_wider(values_from = "value", names_from = "model") %>%
	mutate(
		vars = case_when(
			stat == "e_se" ~ "",
			vars == "Logprice" ~ "Implied price elasiticity",
			vars == "Loginc" ~ "Implied income elasticity"
		)
	) %>% 
	select(-stat)

shape_coeftab$extensive <- rbind(shape_coeftab$extensive, elastab)

stattab <- list(
	overall = read.dta13("_assets/ShortElasticityStat.dta") %>% data.frame(),
	intensive = read.dta13("_assets/ShortIntElasticityStat.dta") %>% data.frame(),
	extensive = read.dta13("_assets/ShortExtElasticityStat.dta") %>% data.frame()
) %>% 
purrr::map(function(x) 
	x %>% mutate_at(
		vars(-xvar),
		list(~case_when(xvar == "N" ~ sprintf("%1.0f", .), TRUE ~ sprintf("%1.3f", .)))
	) %>% 
	mutate(xvar = recode(xvar, "r" = "R-sq", "r2" = "R-sq", .default = xvar)) %>% 
	rename(vars = xvar)
)

addline <- cbind(
	vars = c("Individual FE", "Time FE", "Other Controls"),
	M0 = c(rep("Y", 2), "N"),
	M1 = rep("Y", 3),
	M2 = c(rep("Y", 2), "N"),
	M3 = rep("Y", 3)
)

tabular <- c("overall", "intensive", "extensive") %>% 
	purrr::map(function(x) rbind(shape_coeftab[[x]], addline) %>% rbind(stattab[[x]]))

alltab <- tabular[[1]]
intexttab <- rbind(tabular[[2]][-(5:7),], tabular[[3]])
```


## Robustness Check 2: Result

Overall price elasticity is -1 ~ -1.7\%.

```{r kableShortElasticity1, include=TRUE}
knitr::kable(
    alltab[-c(5, 6, 9),],
    format = "latex",
    caption = "Elasticity with Short-Period Data",
    col.names = c("", "(1)", "(2)", "(3)", "(4)"),
    row.names = FALSE,
    align = "lcccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 8) %>% 
add_header_above(c(" " = 1, "After 2012" = 2, "2013 and 2014" = 2), escape = FALSE) #%>%
#footnote(general_title = "", general = "Notes: $^{*}$ $p < 0.1$, $^{**}$ $p < 0.05$, $^{***}$ $p < 0.01$. Standard errors are clustered at individual level. Other controls are age (its squared value), the interaction between year dummies and education dummies, the interaction between year dummies and gender dummies, and the interaction between year dummies and resident area.", threeparttable = TRUE, escape = FALSE)
```


## Robustness Check 2: Intensive Marign

The intensive-margin price elasticity is -0.6 ~ -1\%.
In column (3), the price elasticity is statistically insignificant.

```{r kableShortElasticity2Slide1, include=TRUE}
knitr::kable(
    rbind(intexttab[1:4,], intexttab[17,]) %>% rbind(intexttab[5,]),
    format = "latex",
    caption = "Intensive-Margin Elasticity with Short-Period Data",
    col.names = c("", "(1)", "(2)", "(3)", "(4)"),
    row.names = FALSE,
    align = "lcccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 8) %>% 
add_header_above(c(" " = 1, "After 2012" = 2, "2013 and 2014" = 2), escape = FALSE) 
```

## Robustness Check 2: Extensive Marign

The extensive-margin price elasticity at sample mean is -1 ~ -2\%.

```{r kableShortElasticity2Slide2, include=TRUE}
knitr::kable(
    rbind(intexttab[11:14,], intexttab[17:18,]),
    format = "latex",
    caption = "Extensive-Margin Elasticity with Short-Period Data",
    col.names = c("", "(1)", "(2)", "(3)", "(4)"),
    row.names = FALSE,
    align = "lcccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 8) %>% 
add_header_above(c(" " = 1, "After 2012" = 2, "2013 and 2014" = 2), escape = FALSE) 
```


<!--- Paper
```{r kableShortElasticity2, include=TRUE, eval = FALSE}
knitr::kable(
    intexttab,
    format = "latex",
    caption = "Intensive- and Extensive-Margin Elasticity with Short-Period Data",
    col.names = c("", "(1)", "(2)", "(3)", "(4)"),
    row.names = FALSE,
    align = "lcccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 8) %>% 
pack_rows("Intensive-Margin Elasticity", 1, 6) %>% 
pack_rows("Extensive-Margin Elasticity", 7, 19) %>% 
add_header_above(c(" " = 1, "After 2012" = 2, "2013 and 2014" = 2), escape = FALSE) %>%
footnote(general_title = "", general = "Notes: $^{*}$ $p < 0.1$, $^{**}$ $p < 0.05$, $^{***}$ $p < 0.01$. Standard errors are clustered at individual level. Other controls are age (its squared value), the interaction between year dummies and education dummies, the interaction between year dummies and gender dummies, and the interaction between year dummies and resident area. The implied extensive-marign price elasticity is evaluated at the sample mean of $D_{ijt}$.", threeparttable = TRUE, escape = FALSE)
```
--->

## Robustness Check 3

Second potential concerns: the change of price due to the change of income

- To exclude this potential concerns, previous identification strategy uses the 2014 tax reform.
- We can also rule out this problem, using the change in the first giving price.
    - The change in the first giving price is $\ln(p_{it}(y_{it-k} - g_{it-k})/p_{it-k}(y_{it-k} - g_{it-k}))$ where $g_{it-k} = 0$.
    - Since we fix the income $y_{it-k}$, this variation comes from the tax reform.

## Robustness Check 3 (Cont'd)

Our estimation equation is 
$$\Delta^k \ln g_{it} = \delta \Delta^k \ln p_{it} + \gamma \Delta^k \ln y_{it} + \Delta^k X_{it} \beta + \mu_i + \iota_t + v_{it},$$
where $\Delta^k Y_{it} = Y_{it} - Y_{it-k}$.

- Note that we cannot estimation the extensive-margin elasticity since it is hard to interapt this estimation equation when we use $\Delta^k D_{it}$ as an outcome.
- We estimate this model for $k = 1, 2, 3$.


```{stata kDiffElasticity, results = "hide", eval = FALSE}
forvalues k = 1(1)3 {
    
	di "lag = `k'"
	
	* panel regression
	xtreg log_diff`k'g log_iv`k'price log_diff`k'I diff`k'_age diff`k'_sqage i.year##i.educ i.year##i.gender i.year##i.living_area, ///
		fe vce(cluster pid)
	
	* result of panel regression
	mat coef = r(table)["b".."pvalue","log_iv`k'price".."log_diff`k'I"]
	mat colnames coef = Logdiffprice_M`k' Logdiffinc_M`k'
	
	mat stat = e(N) \ e(r2)
	mat colnames stat = M`k'
	mat rownames stat = N r2
	
	if `k' == 1 {
	    mat coeftab = coef
		mat stattab = stat
	}
	else {
	    mat_capp coeftab : coeftab coef
		mat_capp stattab : stattab stat
	}
}

mat list coeftab
mat list stattab

xsvmat coeftab, saving(_assets/kDiffElasticityCoef.dta, replace) rownames(xvar) names(col)
xsvmat stattab, saving(_assets/kDiffElasticityStat.dta, replace) rownames(xvar) names(col)
```

```{stata kDiffIntElasticity, results = "hide", eval = FALSE}
forvalues k = 1(1)3 {
    
	di "lag = `k'"
	
	* panel regression
	xtreg log_diff`k'g log_iv`k'price log_diff`k'I diff`k'_age diff`k'_sqage i.year##i.educ i.year##i.gender i.year##i.living_area ///
		if i_ext_giving == 1, fe vce(cluster pid)
	
	* result of panel regression
	mat coef = r(table)["b".."pvalue","log_iv`k'price".."log_diff`k'I"]
	mat colnames coef = Logdiffprice_M`k' Logdiffinc_M`k'
	
	mat stat = e(N) \ e(r2)
	mat colnames stat = M`k'
	mat rownames stat = N r2
	
	if `k' == 1 {
	    mat coeftab = coef
		mat stattab = stat
	}
	else {
	    mat_capp coeftab : coeftab coef
		mat_capp stattab : stattab stat
	}
}

mat list coeftab
mat list stattab

xsvmat coeftab, saving(_assets/kDiffIntElasticityCoef.dta, replace) rownames(xvar) names(col)
xsvmat stattab, saving(_assets/kDiffIntElasticityStat.dta, replace) rownames(xvar) names(col)
```

```{r shapekDiffElasticity}
coeftab <- list(
	overall = read.dta13("_assets/kDiffElasticityCoef.dta") %>% data.frame(),
	intensive = read.dta13("_assets/kDiffIntElasticityCoef.dta") %>% data.frame()
)

shape_coeftab <- coeftab %>% 
	purrr::map(function(x)
		x %>% 
			filter(!str_detect(xvar, "e_")) %>%
			pivot_longer(-xvar, values_to = "value", names_to = c("vars", "model"), names_sep = "_") %>% 
			pivot_wider(values_from = "value", names_from = "xvar") %>% 
			mutate(
				b = case_when(
					pvalue <= 0.01 ~ sprintf("%1.3f***", b),
					pvalue <= 0.05 ~ sprintf("%1.3f**", b),
					pvalue <= 0.1 ~ sprintf("%1.3f*", b),
					TRUE ~ sprintf("%1.3f", b)
				),
				se = sprintf("(%1.3f)", se)
			) %>% 
			select(-t, -pvalue) %>% 
			pivot_longer(cols = b:se, values_to = "value", names_to = "stat") %>% 
			pivot_wider(values_from = "value", names_from = "model") %>%
			mutate(
				vars = case_when(
					stat == "se" ~ "",
					vars == "Logdiffprice" ~ "Lagged difference of first price (log)",
					vars == "Logdiffinc" ~ "Lagged difference of annual income (log)"
				)
			) %>% 
			select(-stat)
	)

stattab <- list(
	overall = read.dta13("_assets/kDiffElasticityStat.dta") %>% data.frame(),
	intensive = read.dta13("_assets/kDiffIntElasticityStat.dta") %>% data.frame()
) %>% 
purrr::map(function(x) 
	x %>% mutate_at(
		vars(-xvar),
		list(~case_when(xvar == "N" ~ sprintf("%1.0f", .), TRUE ~ sprintf("%1.3f", .)))
	) %>% 
	mutate(xvar = recode(xvar, "r" = "R-sq", "r2" = "R-sq", .default = xvar)) %>% 
	rename(vars = xvar)
)

addline <- cbind(
	vars = c("Individual FE", "Time FE", "Other Controls"),
	M1 = rep("Y", 3),
	M2 = rep("Y", 3),
	M3 = rep("Y", 3)
)

tabular <- c("overall", "intensive") %>% 
	purrr::map(function(x) rbind(shape_coeftab[[x]], addline) %>% rbind(stattab[[x]]))

alltab <- rbind(tabular[[1]][-(5:7),], tabular[[2]])
```


## Robustness Check 3: Overall Elasticity

Overall price elasticity is rougnly -2\%.

```{r kablekDiffElasticitySlide1, include=TRUE}
knitr::kable(
    alltab[1:5,],
    format = "latex",
    caption = "Overall Elasticity: $k$-difference model",
    col.names = c("", "(1)", "(2)", "(3)"),
    row.names = FALSE,
    align = "lccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 8) %>% 
add_header_above(c("lag $k$" = 1, "$k = 1$" = 1, "$k = 2$" = 1, "$k = 3$" = 1), escape = FALSE) 
```

## Robustness Check 3: Intensive-Margin Elasticity

The intensive-margin price elasticity is rougnly -2\%.

```{r kablekDiffElasticitySlide2, include=TRUE}
knitr::kable(
    rbind(alltab[7:10,], alltab[14,]),
    format = "latex",
    caption = "Intensive-Margin Elasticity: $k$-difference model",
    col.names = c("", "(1)", "(2)", "(3)"),
    row.names = FALSE,
    align = "lccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 8) %>% 
add_header_above(c("lag $k$" = 1, "$k = 1$" = 1, "$k = 2$" = 1, "$k = 3$" = 1), escape = FALSE) 
```

<!--- Paper
```{r kablekDiffElasticity, include=TRUE, eval = FALSE}
knitr::kable(
    alltab,
    format = "latex",
    caption = "Estimation of Elasticity: $k$-difference model",
    col.names = c("", "(1)", "(2)", "(3)"),
    row.names = FALSE,
    align = "lccc", 
    booktabs = TRUE, escape = TRUE, linesep = ""
) %>% 
kable_styling(font_size = 8) %>% 
pack_rows("Overall Elasticity", 1, 6) %>% 
pack_rows("Intensive-Margin Elasticity", 7, 15) %>% 
add_header_above(c("lag $k$" = 1, "$k = 1$" = 1, "$k = 2$" = 1, "$k = 3$" = 1), escape = FALSE) %>%
footnote(general_title = "", general = "Notes: $^{*}$ $p < 0.1$, $^{**}$ $p < 0.05$, $^{***}$ $p < 0.01$. Standard errors are clustered at individual level. The lagged difference of first price (log) is $\\\\ln(\\\\text{Price}^k_{ijt}) - \\\\ln(\\\\text{Price}_{ij(t-k)})$, where $\\\\text{Price}^k_{ijt}$ calculates the giving price under the tax system in year $t$, using annual taxable income in year $t-k$, $\\\\text{Income}_{ij(t-k)}$. The lagged of annual income (log) is $\\\\ln(\\\\text{Income}_{ijt}) - \\\\ln(\\\\text{Income}_{ij(t-k)})$. Other controls are lagged difference of age, lagged difference of squared age, the interaction between year dummies and education dummies, the interaction between year dummies and gender dummies, and the interaction between year dummies and resident area.", threeparttable = TRUE, escape = FALSE)
```
--->