---
title: |
  Should Application Cost for Tax Relief Be Reduced to Increase Donations?
  Or Should Giving Price be Lowered?
subtitle: Not intended for publication
author: Hiroki Kato
bibliography: ref_appx.bib
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    number_sections: false
params:
  preview: true
---

```{r knit_command, eval = FALSE, include = FALSE, echo = FALSE}
# If you want to knit draft, please run following command manually!!
rmarkdown::render(
  "Rmarkdown/note-identification.Rmd",
  output_file = "note-identification.html",
  output_dir = "report/view"
)
```

```{r include = FALSE, eval = params$preview}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  cache = FALSE,
  include = TRUE,
  fig.width = 10
)

library(here)
knitr::opts_knit$set(
  root.dir = here::here()
)

options(
  knitr.kable.NA = " ",
  knitr.table.format = "html",
  modelsummary_stars_note = FALSE
)
```



```{r include = FALSE, eval = params$preview}
library(xfun)
xfun::pkg_attach2(c(
  "tidyverse", "rlist", "modelsummary", "kableExtra",
  "estimatr", "fixest"
))

lapply(Sys.glob(file.path("script/R/functions", "*.r")), source)
```



```{r include = FALSE, eval = params$preview}
df <- readr::read_csv(
  "data/shaped2.csv",
  col_types = cols(
    ext_credit_giving = col_double(),
    krw_credit_giving = col_double(),
    trust_politician = col_double(),
    political_pref = col_double(),
    addtax = col_double(),
    avg_welfare_tax = col_double(),
    opt_welfare_tax = col_double(),
    now_balance = col_double(),
    ideal_balance = col_double()
  )
) %>%
dplyr::filter(
  ext_benefit_tl == 0 | (ext_benefit_tl == 1 & i_ext_giving == 1)
)
```


# Conceptual Framework
## Optimization Problem

Following @Almunia2020, we formulate the optimaization problem as follows:

\begin{align*}
  \max_{x_{it}, g_{it}, R_{it}} &U(x_{it}, g_{it}, G_t)
  = x_{it} - R_{it}K_{it} + \theta_i u(g_{it}) + V(G_t), \\
  \text{s.t.}\:\:
  &x_{it} + g_{it} = y_{it} - T_{it}(y_{it}, R_{it} g_{it}), \\
  &G_t = g_{it} + G_{-it}, \\
  &T_{it} = \begin{cases}
    \tau_t(y_{it} - R_{it} g_{it}) (y_{it} - R_{it} g_{it}) &t < 2014 \\
    \tau_t(y_{it}) y_{it} - m R_{it} g_{it} &t \ge 2014
  \end{cases}
\end{align*}

This model implicitly assume no income effect and no saving.
By this assumption,
a dynamic optimization reduces to a repeated static optimaization problem.
We further assume that
(i) decision-making before 2014 is based on $\tau(y_{it})$ (first-price);
and (ii) $G_{-it}$ is large enough to $V'(G_t) \approx 0$.
Especially, by the second assumption,
we do not need to take $\partial V(G_t) / \partial g_{it}$ into accuount
when we derive the optimal donation levels.

Under these assumptions,
we can reformulate the optimization problem as follows:

\begin{align*}
  \max_{g_{it}, R_{it}} &U(g_{it}) =
  - (1 - R_{it}s_{it}) g_{it} + \theta_i u(g_{it}), \\
  \text{s.t.}\:\:
  &s_{it} = \begin{cases}
    \tau(y_{it}) &t < 2014 \\
    m &t \ge 2014
  \end{cases},
\end{align*}

where $s_{it}$ is tax incentive of monetary donations
for individual $i$ in year $t$.

Let $g(1-s_{it};\theta_i)$ and $g(1;\theta_i)$
be the optimal donation levels when $R_{it} = 1$ and $R_{it} = 0$,
respectively.
Each indirect utility function is

\begin{align*}
  v(1 - s_{it}; \theta_i)
  &= -(1 - s_{it})g(1 - s_{it}; \theta_i)
  + \theta_i u(g(1 - s_{it}; \theta_i)), \\
  v(1; \theta_i)
  &= -g(1;\theta_i) + \theta_i u(g(1;\theta_i)).
\end{align*}

Note that the price effect on the indirect utility is

\begin{align*}
  \frac{\partial v(1 - s_{it};\theta_i)}{\partial (1 - s_{it})}
  &= -g(1 - s_{it};\theta_i)
  - (1 - s_{it}) \frac{\partial g(1-s_{it};\theta_i)}{\partial (1 - s_{it})}
  + \theta_i \frac{\partial u}{\partial g}
  \frac{\partial g(1-s_{it};\theta_i)}{\partial (1 - s_{it})} \\
  &= -g(1 - s_{it};\theta_i)
  + \left(\theta_i \frac{\partial u}{\partial g} - (1 - s_{it}) \right)
  \frac{\partial g(1-s_{it};\theta_i)}{\partial (1 - s_{it})} \\
  &= -g(1 - s_{it}; \theta_i).
\end{align*}

This implies that the effect of tax incentive $s_{it}$ on the indirect utility is
$\partial v(1 - s_{it};\theta_i) / \partial s_{it}
= (\partial v(1 - s_{it};\theta_i) / \partial (1 - s_{it}))(d (1 - s_{it})/d s_{it}) = g(1 - s_{it};\theta_i)$.

In the same way, the effect of warm-glow preference $\theta_i$ on indirect utility is

\begin{align*}
  \frac{\partial v(1 - s_{it};\theta_i)}{\partial \theta_i}
  &= -(1 - s_{it})\frac{\partial g(1-s_{it};\theta_i)}{\partial \theta_i}
  + \theta_i \frac{\partial u}{\partial g}
  \frac{\partial g(1-s_{it};\theta_i)}{\partial \theta_i}
  + u(g(1 - s_{it};\theta_i)) \\
  &= u(g(1 - s_{it};\theta_i))
  + \left(\theta_i \frac{\partial u}{\partial g} - (1 - s_{it}) \right)
  \frac{\partial g(1-s_{it};\theta_i)}{\partial \theta_i} \\
  &= u(g(1 - s_{it};\theta_i)),
\end{align*}

and,

\begin{align*}
  \frac{\partial v(1;\theta_i)}{\partial \theta_i}
  &= -\frac{\partial g(1;\theta_i)}{\partial \theta_i}
  + \theta_i \frac{\partial u}{\partial g}
  \frac{\partial g(1;\theta_i)}{\partial \theta_i}
  + u(g(1;\theta_i)) \\
  &= u(g(1;\theta_i))
  + \left(\theta_i \frac{\partial u}{\partial g} - 1 \right)
  \frac{\partial g(1;\theta_i)}{\partial \theta_i} \\
  &= u(g(1;\theta_i)).
\end{align*}

Finally, individual $i$ applies for tax relief in year $t$ if and only if

\begin{align*}
  \Delta v \equiv v(1 - s_{it};\theta_i) - v(1;\theta_i) > K_{it}.
\end{align*}

Note that $\partial \Delta v/\partial \theta_i = u(g(1 - s_{it};\theta_i)) - u(g(1;\theta_i)) \ge 0$
because $g(1 - s_{it};\theta_i) \ge g(1;\theta_i)$.

## Specification of Warm-Glow Utility

When performing the structual estimation,
@Almunia2020 specify the warm-glow utility $u$ as follows:

\begin{align*}
  u(g) = \frac{g^{1 - 1/\gamma_i}}{1 - \frac{1}{\gamma_i}}.
\end{align*}

where $\gamma_i > 0$.

If we follow this specification,
we can derive the optimal donation level as follows:

\begin{align*}
  g(1 - s_{it};\theta_i)
  &= \left( \theta_i/(1 - s_{it}) \right)^{\gamma_i}, \\
  g(1;\theta_i)
  &= \left( \theta_i \right)^{\gamma_i}.
\end{align*}

Moreover, these logarithm values are

\begin{align*}
  \ln g(1 - s_{it};\theta_i)
  &= \gamma_i \ln \theta_i - \gamma_i \ln (1 - s_{it}), \\
  \ln g(1;\theta_i)
  &= \gamma_i \ln \theta_i.
\end{align*}

Thus, individual $i$ applies for tax relief in year $t$ if and only if

\begin{align*}
  -(1 - s_{it}) (\theta_i / (1 - s_{it}))^{\gamma_i}
  + \theta_i^{\gamma_i}
  + \theta_i \frac{(\theta_i / (1 - s_{it}))^{\gamma_i(1 - 1/\gamma_i)}
  - \theta_i^{\gamma_i(1 - 1/\gamma_i)}}{1 - 1 / \gamma_i}
  &\ge K_{it}  \\
  \theta_i \frac{\theta_i^{\gamma_i - 1}((1 - s_{it})^{1 - \gamma_i} - 1)}
  {1 - 1 / \gamma_i} - \theta_i^{\gamma_i}((1 - s_{it})^{1 - \gamma_i} - 1)
  &\ge K_{it}  \\
  \theta_i^{\gamma_i}
  \frac{(1 - s_{it})^{1 - \gamma_i} - 1}{1 - 1 / \gamma_i} -
  \theta_i^{\gamma_i}((1 - s_{it})^{1 - \gamma_i} - 1)
  &\ge K_{it} \\
  \frac{\theta_i^{\gamma_i}}{\gamma_i - 1}((1 - s_{it})^{1 - \gamma_i} - 1)
  &\ge K_{it}
\end{align*}

## Parameter of Interest

We assume $\partial \Delta v/\partial \theta_i > 0$.

Assume that $\theta_i$ is distributed over
$[\underline{\theta}, \bar{\theta}]$,
and its density function is $f(\cdot)$.
Then, we can devide population into three types:

1. $\theta_i \le \theta_0$: individuals do not donate anything
    - $g(1;\theta_i) = 0$ if $\theta_i$ is too low
1. $\theta_i \in (\theta_0, \theta(s)]$: individuals donate but do not apply for tax relief
1. $\theta_i > \theta(s)$: individuals donate and apply for tax relief

where $\theta(s)$ holds $v(1 - s_{it};\theta(s)) - v(1;\theta(s)) = K_{it}$.
$\theta(s)$ is decreasing in $s_{it}$ because
$\partial v(1 - s_{it};\theta_i)/\partial (1 - s_{it}) \le 0$.

Social total amount of giving $G$ is defined by

\begin{align*}
  &G = g^0(s_{it}) + g^1(s_{it}) + G_g \\
  &g^0(s_{it}) = \int_{\theta_0}^{\theta(s)} g(1;\theta) f(\theta) d\theta \\
  &g^1(s_{it}) = \int_{\theta(s)}^{\bar{\theta}} g(1 - s_{it};\theta) f(\theta) d\theta \\
\end{align*}

where $G_g$ is public goods supplied by government.

# Identification

## Statistical Model

We assume that expectation of
$\ln g(1-s_{it};\theta_i)$ and $\ln g(1;/\theta_i)$
conditional on $s_{it}$ and $\theta_i$ has the following functional forms:

\begin{align*}
  &E[\ln g(1-s_{it};\theta_i)|s_{it}, \theta_i]
  = \theta_i + \gamma_i \ln (1 - s_{it}), \\
  &E[\ln g(1;\theta_i) | \theta_i] = \theta_i. \\
\end{align*}

Thus, realized value of
$\ln g(1-s_{it};\theta_i)$ and $\ln g(1;/\theta_i)$ are

\begin{align*}
  &\ln g(1-s_{it};\theta_i) =
  \theta_i + \gamma_i \ln (1 - s_{it}) + \epsilon_{1it}, \\
  &\ln g(1;\theta_i) = \theta_i + \epsilon_{0it}. \\
\end{align*}

where $E[\epsilon_{1it}|s_{it}, \theta_i]
= E[\ln g(1-s_{it};\theta_i)
- E[\ln g(1-s_{it};\theta_i)|s_{it}, \theta_i]|s_{it}, \theta_i] = 0$,
and $E[\epsilon_{0it}|\theta_i]
= E[\ln g(1;\theta_i) - E[\ln g(1;\theta_i) | \theta_i]|\theta_i] = 0$,
by construction.

Since we cannot both $g(1 - s_{it};\theta_i)$ and $g(1;\theta_i)$
for individual $i$ in year $t$,
the observed outcome $\ln g_{it}$ is

\begin{align*}
  \ln g_{it}
  &= \theta_i + \gamma_i R_{it} \ln (1 - s_{it})
  + (\epsilon_{0it} + R_{it}(\epsilon_{1it} - \epsilon_{0it})) \\
  &= \theta_i + \bar{\gamma} R_{it} \ln (1 - s_{it})
  + \{(\gamma_i - \bar{\gamma})R_{it}\ln (1 - s_{it})
  + (\epsilon_{0it} + R_{it}(\epsilon_{1it} - \epsilon_{0it}))\},
\end{align*}

where $\bar{\gamma} = E(\gamma_i)$.


```{r }
fixest::setFixest_fml(
  ..fullx = ~ log_pinc_all + sqage | year + panelid + area + industry
)

reducemod <- list(
  "(1)" = list(
    model = fixest::xpd(log_total_g ~ ext_benefit_tl:log_price + ..fullx),
    data = subset(df, i_ext_giving == 1)
  ),
  "(2)" = list(
    model = fixest::xpd(log_total_g ~ log_price + ..fullx),
    data = subset(df, ext_benefit_tl == 1 & i_ext_giving == 1)
  ),
  "(3)" = list(
    model = fixest::xpd(log_total_g ~ ..fullx),
    data = subset(df, ext_benefit_tl == 0 & i_ext_giving == 1)
  ),
  "(4)" = list(
    model = fixest::xpd(log_total_g ~ log_price + ..fullx),
    data = subset(df, ext_benefit_tl == 0 & i_ext_giving == 1)
  )
)

reducemod %>%
  purrr::map(~ fixest::feols(
    .$model, data = .$data,
    cluster = ~ panelid, se = "cluster"
  )) %>%
  modelsummary(
    title = "FE Estimation of Logged Donations (Intensive-margin)",
    coef_map = c(
      "ext_benefit_tl:log_price" = "Applying tax relief x log(first price)",
      "log_price" = "log(first price)",
      "log_pinc_all" = "log(income)"
    ),
    gof_omit = "^(?!R2 Adj.|FE|N|Std.Errors)",
    stars = c("*" = .1, "**" = .05, "***" = .01)
  ) %>%
  kableExtra::kable_styling() %>%
  kableExtra::add_header_above(
    c(" " = 1, "Pooling" = 1, "R = 1" = 1, "R = 0" = 2)
  ) %>%
  footnote(
    general_title = "",
    general = paste(
      "Notes: $^{*}$ $p < 0.1$, $^{**}$ $p < 0.05$, $^{***}$ $p < 0.01$.",
      "Standard errors are clustered at individual level."
    ),
    threeparttable = TRUE,
    escape = FALSE
  )
```

```{r }
reducemod_ext <- list(
  "(1)" = list(
    model = fixest::xpd(i_ext_giving ~ ext_benefit_tl:log_price + ..fullx),
    data = df
  ),
  "(2)" = list(
    model = fixest::xpd(i_ext_giving ~ ..fullx),
    data = subset(df, ext_benefit_tl == 0)
  ),
  "(3)" = list(
    model = fixest::xpd(i_ext_giving ~ log_price + ..fullx),
    data = subset(df, ext_benefit_tl == 0)
  )
)

est_reducemod_ext <- reducemod_ext %>%
  purrr::map(~ fixest::feols(
    .$model, data = .$data,
    cluster = ~ panelid, se = "cluster"
  ))

addtab <- est_reducemod_ext %>%
  purrr::map(function(x) {
    dbar <- mean(x$fitted.values + x$residuals)

    x %>%
      tidy() %>%
      filter(str_detect(term, "price")) %>%
      mutate(
        estimate = case_when(
          p.value <= .01 ~ sprintf("%1.3f***", estimate / dbar),
          p.value <= .05 ~ sprintf("%1.3f**", estimate / dbar),
          p.value <= .1 ~ sprintf("%1.3f*", estimate / dbar),
          TRUE ~ sprintf("%1.3f", estimate / dbar),
        ),
        std.error = sprintf("(%1.3f)", std.error / dbar)
      ) %>%
      select(estimate, std.error) %>%
      pivot_longer(everything())
  }) %>%
  reduce(left_join, by = "name") %>%
  setNames(c("term", sprintf("(%1d)", seq_len(length(est_reducemod_ext))))) %>%
  mutate(term = recode(
    term,
    "estimate" = "Implied price elasticity", .default = ""
  ))

est_reducemod_ext %>%
  modelsummary(
    title = "FE Estimation of Extensive-Margin Price Elasticities",
    coef_map = c(
      "ext_benefit_tl:log_price" = "Applying tax relief x log(first price)",
      "log_price" = "log(first price)",
      "log_pinc_all" = "log(income)"
    ),
    gof_omit = "^(?!R2 Adj.|FE|N|Std.Errors)",
    stars = c("*" = .1, "**" = .05, "***" = .01),
    add_rows = addtab
  ) %>%
  kableExtra::kable_styling() %>%
  kableExtra::add_header_above(
    c(" " = 1, "Pooling" = 1, "R = 0" = 2)
  ) %>%
  footnote(
    general_title = "",
    general = paste(
      "Notes: $^{*}$ $p < 0.1$, $^{**}$ $p < 0.05$, $^{***}$ $p < 0.01$.",
      "Standard errors are clustered at individual level."
    ),
    threeparttable = TRUE,
    escape = FALSE
  )
```

# First-Stage Estimation


```{r include = FALSE, eval = params$preview}
fixest::setFixest_fml(
  ..stage1 = ~ log_pinc_all + sqage + factor(area) + factor(industry)
)

poolstage1 <- fixest::feglm(
  fixest::xpd(ext_benefit_tl ~ employee + log_price + ..stage1),
  family = binomial(link = "probit"),
  data = subset(df, year <= 2017)
)

sepstage1 <- df %>%
  dplyr::filter(year <= 2017) %>%
  group_by(year) %>%
  do(sepmod = fixest::feglm(
    fixest::xpd(ext_benefit_tl ~ employee + log_price + ..stage1),
    family = binomial(link = "probit"),
    data = .
  ))

estdf <- df %>%
  dplyr::filter(year <= 2017 & !is.na(ext_benefit_tl)) %>%
  mutate(poolmod = list(poolstage1)) %>%
  left_join(sepstage1, by = "year") %>%
  group_by(year) %>%
  do(modelr::spread_predictions(
    ., first(.$poolmod), first(.$sepmod),
    type = "link"
  )) %>%
  rename(lpred_pool = "first(.$poolmod)", lpred_sep = "first(.$sepmod)") %>%
  mutate(
    # propensity score
    psc_pool = pnorm(lpred_pool), psc_sep = pnorm(lpred_sep),

    # inverse mills ratio for R = 1
    imr1_pool = dnorm(lpred_pool) / pnorm(lpred_pool),
    imr1_sep = dnorm(lpred_sep) / pnorm(lpred_sep),

    # inverse mills ratio for R = 0
    imr0_pool = dnorm(lpred_pool) / (1 - pnorm(lpred_pool)),
    imr0_sep = dnorm(lpred_sep) / (1 - pnorm(lpred_sep)),

    # generalized error
    gr_pool = if_else(ext_benefit_tl == 1, imr1_pool, imr0_pool),
    gr_sep = if_else(ext_benefit_tl == 1, imr1_sep, imr0_sep)

  ) %>%
  ungroup() %>%
  select(-poolmod, -sepmod)
```



```{r eval = params$preview}
sepstage1 %>%
  pull(sepmod, name = year) %>%
  list.merge(list("Pooled" = poolstage1), .) %>%
  modelsummary(
    title = "Probit Estimation of Selection of Applying for Tax Relief",
    coef_omit = "factor",
    coef_rename = c(
      "employee" = "1 = Wage earner",
      "log_price" = "log(first giving price)",
      "log_pinc_all" = "log(income)",
      "sqage" = "Square of age"
    ),
    gof_omit = "R2|AIC|BIC",
    stars = c("***" = .01, "**" = .05, "*" = .1),
    add_rows = tribble(
      ~"term", ~"Pooled", ~"2012", ~"2013", ~"2014", ~"2015", ~"2016", ~"2017",
      "Dummy of area", "X", "X", "X", "X", "X", "X", "X",
      "Dummy of industry", "X", "X", "X", "X", "X", "X", "X"
    )
  ) %>%
  kableExtra::kable_styling() %>%
  kableExtra::add_header_above(c(
    " " = 2, "Separated Probit Model" = 6
  )) %>%
  footnote(
    general_title = "",
    general = paste(
      "Notes: $^{*}$ $p < 0.1$, $^{**}$ $p < 0.05$, $^{***}$ $p < 0.01$."
    ),
    threeparttable = TRUE,
    escape = FALSE
  )
```


# FE-2SLS Approach


```{r intensive}
stage2 <- list(
  "(1)" = fixest::xpd(
    log_total_g ~ ..fullx | ext_benefit_tl:log_price ~ employee:log_price
  ),
  "(2)" = fixest::xpd(
    log_total_g ~ ..fullx | ext_benefit_tl:log_price ~ psc_pool:log_price
  ),
  "(3)" = fixest::xpd(
    log_total_g ~ ..fullx | ext_benefit_tl:log_price ~ psc_sep:log_price
  ),
  "(4)" = fixest::xpd(
    log_total_g ~ psc_pool:log_price + ..fullx
  ),
  "(5)" = fixest::xpd(
    log_total_g ~ psc_sep:log_price + ..fullx
  )
)

stage2 %>%
  purrr::map(~ fixest::feols(
    .,
    cluster = ~ panelid,
    data = subset(estdf, i_ext_giving == 1)
  )) %>%
  modelsummary(
    title = paste(
      "FE-2SLS Approach of Intensive-Margin"
    ),
    coef_map = c(
      "fit_ext_benefit_tl:log_price" =
        "Applying tax relief x log(first price)",
      "psc_pool:log_price" =
        "PS of applying tax relief x log(first price)",
      "psc_sep:log_price" =
        "PS of applying tax relief x log(first price)",
      "log_pinc_all" = "log(income)"
    ),
    gof_omit = "R2 Pseudo|R2 Within|AIC|BIC|Log|Std",
    stars = c("***" = .01, "**" = .05, "*" = .1),
    add_rows = tribble(
      ~"term", ~"(1)", ~"(2)", ~"(3)", ~"(4)", ~"(5)",
      "Square of age", "X", "X", "X", "X", "X",
      "Instrument", "Wage earner x Price",
      "PS x Price", "PS x Price", "", "",
      "Method of PS", "", "Pool", "Separate", "Pool", "Separate"
    )
  ) %>%
  kableExtra::kable_styling() %>%
  kableExtra::add_header_above(c(" " = 1, "FE-2SLS" = 3, "OLS" = 2)) %>%
  footnote(
    general_title = "",
    general = paste(
      "Notes: $^{*}$ $p < 0.1$, $^{**}$ $p < 0.05$, $^{***}$ $p < 0.01$.",
      "Standard errors are clustered at individual level."
    ),
    threeparttable = TRUE,
    escape = FALSE
  )
```

```{r extensive}
stage2_ext <- list(
  "(1)" = fixest::xpd(
    i_ext_giving ~ ..fullx | ext_benefit_tl:log_price ~ employee:log_price
  ),
  "(2)" = fixest::xpd(
    i_ext_giving ~ ..fullx | ext_benefit_tl:log_price ~ psc_pool:log_price
  ),
  "(3)" = fixest::xpd(
    i_ext_giving ~ ..fullx | ext_benefit_tl:log_price ~ psc_sep:log_price
  ),
  "(4)" = fixest::xpd(
    i_ext_giving ~ psc_pool:log_price + ..fullx
  ),
  "(5)" = fixest::xpd(
    i_ext_giving ~ psc_sep:log_price + ..fullx
  )
)

est_stage2_ext <- stage2_ext %>%
  purrr::map(~ fixest::feols(
    .,
    cluster = ~ panelid,
    data = estdf
  ))

addtab <- est_stage2_ext %>%
  purrr::map(function(x) {
    dbar <- mean(x$fitted.values + x$residuals)

    x %>%
      tidy() %>%
      filter(str_detect(term, "price")) %>%
      mutate(
        estimate = case_when(
          p.value <= .01 ~ sprintf("%1.3f***", estimate / dbar),
          p.value <= .05 ~ sprintf("%1.3f**", estimate / dbar),
          p.value <= .1 ~ sprintf("%1.3f*", estimate / dbar),
          TRUE ~ sprintf("%1.3f", estimate / dbar),
        ),
        std.error = sprintf("(%1.3f)", std.error / dbar)
      ) %>%
      select(estimate, std.error) %>%
      pivot_longer(everything())
  }) %>%
  reduce(left_join, by = "name") %>%
  setNames(c("term", sprintf("(%1d)", seq_len(length(est_stage2_ext))))) %>%
  mutate(term = recode(
    term,
    "estimate" = "Implied price elasticity", .default = ""
  )) %>%
  bind_rows(tibble::tribble(
    ~"term", ~"(1)", ~"(2)", ~"(3)", ~"(4)", ~"(5)",
    "Square of age", "X", "X", "X", "X", "X",
    "Instrument", "Wage earner x Price",
    "PS x Price", "PS x Price", "", "",
    "Method of PS", "", "Pool", "Separate", "Pool", "Separate"
  ), .)

est_stage2_ext %>%
  modelsummary(
    title = paste(
      "FE-2SLS Approach of Extensive-Margin"
    ),
    coef_map = c(
      "fit_ext_benefit_tl:log_price" =
        "Applying tax relief x log(first price)",
      "psc_pool:log_price" =
        "PS of applying tax relief x log(first price)",
      "psc_sep:log_price" =
        "PS of applying tax relief x log(first price)",
      "log_pinc_all" = "log(income)"
    ),
    gof_omit = "R2 Pseudo|R2 Within|AIC|BIC|Log|Std",
    stars = c("***" = .01, "**" = .05, "*" = .1),
    add_rows = addtab
  ) %>%
  kableExtra::kable_styling() %>%
  kableExtra::add_header_above(c(" " = 1, "FE-2SLS" = 3, "OLS" = 2)) %>%
  footnote(
    general_title = "",
    general = paste(
      "Notes: $^{*}$ $p < 0.1$, $^{**}$ $p < 0.05$, $^{***}$ $p < 0.01$.",
      "Standard errors are clustered at individual level."
    ),
    threeparttable = TRUE,
    escape = FALSE
  )
```

# CF Approach ($R_{it} = 1$)

## Sample Selection Bias Correction

This supplement estimates price elasticity
using data from only those who have applied for tax relief.
If there is both
a year in which the same individual applied for tax relief
and a year when it did not,
we use only the year when the person applied for the relief.

Since deduction applications are endogenous as described in this paper,
subsample estimation involves a sample selection bias.
Following @Wooldridge2010, we formally show this problem and its solution.
Consider the following model:
\begin{align}
  &Y_{it} = \beta  X_{it} + \mu_{i1} + \lambda_{t1} + e_{it1}, \\
  &R_{it} = 1[\gamma_1 Z_{it} + \gamma_2 X_{it} + \mu_{i2} + \lambda_{t2} + e_{it2} > 0].
\end{align}
where $Y_{it}$ is the logged value of giving amount ($\ln g_{it}$),
$X_{it}$ is the logged value of first giving price ($\ln p^f(y_{it})$),
and $R_{it}$ is the application dummy.
Thus, $\beta$ represents the price elasticity of giving,
which is our parameter of interest.
$Z_{it}$ is the wage earner dummy,
an instrument that allows arbitrary corrleation
with $\mu_{i1}$ and $\lambda_{i1}$ but
holds that exogeneity with respect to $u_{i1}$.
$\mu_i$ and $\eta_t$ is individual and time fixed effect, respectively.
$e_{it}$ is error term.
Assume that $E(e_{it1} |Z_{it}, X_{it}, \mu_{i1}, \lambda_{i1}) = 0$.
Note that, to clarify the problem,
we intentionally do not model covariates such as income.

Since we estimate the model only for those who applied for the deduction,
the conditional expectation of the outcome equation is as follows:
\begin{align}
  E(Y_{it} |Z_{it}, X_{it}, \mu_{i1}, \lambda_{i1}, R_{it} = 1)
  = \beta  X_{it} + \mu_{i1} + \lambda_{t1}
  + E(e_{it1} |Z_{it}, X_{it}, \mu_{i1}, \lambda_{i1}, R_{it} = 1).
\end{align}

The fixed effect estimator of $\beta$ is unbiased only if
$E(e_{it1} |Z_{it}, X_{it}, \mu_{i1}, \lambda_{i1}, R_{it} = 1) = 0$.
However, it is difficult to assume that
the idiosyncratic error of the donation amount
is independent of the tax deduction application
due to the simultaneous determination of
the tax deduction application and the donation amount.
Therefore, using the control function approach,
we eliminate this selection bias.

This approach makes the following assumptions
about the error term of the outcome variable:
\begin{align}
  E(e_{it1} | Z_{it}, X_{it}, \mu_{i1}, \lambda_{t1}, e_{it2})
  = E(e_{it1} | e_{it2}) = \rho e_{it2}.
\end{align}
This equation suggests two assumptions.
First, the two fixed effects, $\mu_{i1}$ and $\lambda_{t1}$,
and observables, $(X_{it}, Z_{it})$ are independent of
the two error terms, $(e_{it1}, e_{it2})$.
Second, $e_{it1}$ is linearly correlated with $e_{it2}$,
the degree of which is constant with respect to time.

Under this assumption,
we can write the conditional expectation of the error term, $e_{it1}$,
as follows:
\begin{align}
  E(e_{it1} | Z_{it}, X_{it}, \mu_{i1}, \lambda_{t1}, R_{it} = 1)
  = \rho E(e_{it2} | Z_{it}, X_{it}, R_{it} = 1).
\end{align}
Thus, the estimation model that eliminates the selection bias is as follows:
\begin{align}
  Y_{it} = \beta  X_{it} + \mu_{i1} + \lambda_{t1}
  + \rho E(e_{it2} | Z_{it}, X_{it}, R_{it} = 1) + u_{it1},
\end{align}
where, by construction, $E(u_{it1} | Z_{it}, X_{it}, R_{it} = 1) = 0$.
If we knew $E(e_{it2} | Z_{it}, X_{it}, R_{it} = 1)$,
then we can obtaine unbiased estimator of $\beta$.
The correction term $E(e_{it2} | Z_{it}, X_{it}, R_{it} = 1)$
can be obtained by the inverse Mills ratio (IMR).
To calculate the inverse Mills ratio, we use the probit estimation shown in
\@ref(tab:stage1) in Appendix A (pooled model and separate model).

## Results


```{r benchmark}
basemod <- list(
  "(1)" = fixest::xpd(log_total_g ~ log_price + ..fullx),
  "(2)" = fixest::xpd(log_total_g ~ log_price + gr_pool + ..fullx),
  "(3)" = fixest::xpd(log_total_g ~ log_price * gr_pool + ..fullx),
  "(4)" = fixest::xpd(log_total_g ~ log_price + gr_sep + ..fullx),
  "(5)" = fixest::xpd(log_total_g ~ log_price * gr_sep + ..fullx)
)

est_basemod1 <- basemod %>%
  purrr::map(~ fixest::feols(
    .,
    data = subset(estdf, ext_benefit_tl == 1 & i_ext_giving == 1),
    cluster = ~ panelid, se = "cluster"
  ))

est_basemod1 %>%
  modelsummary(
    title = "Intensive-Margin Model for R = 1",
    coef_map = c(
      "log_price" = "log(first price)",
      "log_pinc_all" = "log(income)",
      "log_price:gr_pool" = "log(first price) x Correction term",
      "log_price:gr_sep" = "log(first price) x Correction term",
      "gr_pool" = "Correction term",
      "gr_sep" = "Correction term"
    ),
    gof_omit = "^(?!R2 Adj.|FE|N|Std.Errors)",
    stars = c("*" = .1, "**" = .05, "***" = .01),
    add_rows = tribble(
      ~term, ~"(1)", ~"(2)", ~"(3)", ~"(4)", ~"(5)",
      "Square age", "X", "X", "X", "X", "X",
      "Method of IMR", "", "Pooled", "Pooled", "Separate", "Separate"
    )
  ) %>%
  kableExtra::kable_styling() %>%
  footnote(
    general_title = "",
    general = paste(
      "Notes: $^{*}$ $p < 0.1$, $^{**}$ $p < 0.05$, $^{***}$ $p < 0.01$.",
      "Standard errors are clustered at individual level."
    ),
    threeparttable = TRUE,
    escape = FALSE
  )
```


Table \@ref(tab:benchmark) shows the estimation results of price elasticity.
Model (1) does not add a selection correction term,
while models (2) and (4) add it to the explanatory variables.
We obtain the inverse mills ratio from the pooled probit model
and the separated probit model, respectively.
Since the coefficient of the correction term is statistically insignificant,
the selection bias of the application of tax relief is not severe.
Therefore, the estimated elasticity is in the range of -1.3 to -1.6
with or without the correction term.
The estimated value is very close to the result of this paper.

Models (3) and (5) considered
the heterogeneity of price elasticity among individuals.
Based on the model in the previous subsection,
we can write a (correlated) random coefficient model
that allows this heterogeneity as follows:
\begin{align}
  Y_{it} = \bar{\beta} X_{it} + \mu_{i1} + \lambda_{t1}
  + \rho E(e_{it2} | Z_{it}, X_{it}, R_{it} = 1)
  + \{(\beta_i - \bar{\beta}) X_{it} +  u_{it1}\},
\end{align}
where $\bar{\beta} = E(\beta_i | R_i = 1)$.
Then, since $(\beta_i - \bar{\beta}) X_{it}$ is included in the error term,
we cannot obtain unbiased estimator of $\bar{\beta}$,
which is a parameter of our interest,
by controlling only the selection correction term.

@Wooldridge2015 proposes an estimation method that solves this problem
by making the following assumptions in the elements of this new error term:
\begin{align}
  E(\beta_i - \bar{\beta} | Z_{it}, X_{it}, \mu_{i1}, \lambda_{t1}, e_{it2})
  = E(\beta_i - \bar{\beta} | e_{it2}) = \eta e_{it2}.
\end{align}
Thus, the estimation model that eliminates both the selection bias and
the bias from random coefficient is as follows:
\begin{align}
  Y_{it} =& \beta  X_{it} + \mu_{i1} + \lambda_{t1} \\
  &+ \rho \lambda(Z_{it}, X_{it}) + \eta \lambda(Z_{it}, X_{it}) \times X_{it}
  + \tilde{u}_{it1},
\end{align}
where $\lambda(Z_{it}, X_{it})$ is the inverse Mills ratio.
Note that $E(\tilde{u}_{it1} | Z_{it}, X_{it}, R_{it} = 1) = 0$
by construction.
Therefore,
by simply adding an intersection
between the correction term and the giving price to models (3) and (4),
we can eliminate the bias resulting from the heterogeneous elasticity
and estimate the unbiased average elasticity.

The average elasticity estimated by models (3) and (5) is about -1.5,
which is consistent with the results of this paper.
Also, since the coefficients of the intersection term
between the correction term and the giving price
are statistically insignificant,
the price elasticity is unlikely to vary significantly among individuals.

# CF Approach ($R_{it} = 0$)


```{r }
est_basemod0 <- basemod %>%
  purrr::map(~ fixest::feols(
    .,
    data = subset(estdf, ext_benefit_tl == 0 & i_ext_giving == 1),
    cluster = ~ panelid, se = "cluster"
  ))

est_basemod0 %>%
  modelsummary(
    title = "Intensive-Margin Model for R = 0",
    coef_map = c(
      "log_price" = "log(first price)",
      "log_pinc_all" = "log(income)",
      "log_price:gr_pool" = "log(first price) x Correction term",
      "log_price:gr_sep" = "log(first price) x Correction term",
      "gr_pool" = "Correction term",
      "gr_sep" = "Correction term"
    ),
    gof_omit = "^(?!R2 Adj.|FE|N|Std.Errors)",
    stars = c("*" = .1, "**" = .05, "***" = .01),
    add_rows = tribble(
      ~term, ~"(1)", ~"(2)", ~"(3)", ~"(4)", ~"(5)",
      "Square age", "X", "X", "X", "X", "X",
      "Method of IMR", "", "Pooled", "Pooled", "Separate", "Separate"
    )
  ) %>%
  kableExtra::kable_styling() %>%
  footnote(
    general_title = "",
    general = paste(
      "Notes: $^{*}$ $p < 0.1$, $^{**}$ $p < 0.05$, $^{***}$ $p < 0.01$.",
      "Standard errors are clustered at individual level."
    ),
    threeparttable = TRUE,
    escape = FALSE
  )
```


# Effect of Applying for Tax Relief


```{r }
rawvalue <- function(x) x

preddt <- estdf %>%
  modelr::add_predictions(est_basemod1[["(1)"]], var = "pred11") %>%
  modelr::add_predictions(est_basemod1[["(2)"]], var = "pred12") %>%
  modelr::add_predictions(est_basemod1[["(3)"]], var = "pred13") %>%
  modelr::add_predictions(est_basemod1[["(4)"]], var = "pred14") %>%
  modelr::add_predictions(est_basemod1[["(5)"]], var = "pred15") %>%
  modelr::add_predictions(est_basemod0[["(1)"]], var = "pred01") %>%
  modelr::add_predictions(est_basemod0[["(2)"]], var = "pred02") %>%
  modelr::add_predictions(est_basemod0[["(3)"]], var = "pred03") %>%
  modelr::add_predictions(est_basemod0[["(4)"]], var = "pred04") %>%
  modelr::add_predictions(est_basemod0[["(5)"]], var = "pred05") %>%
  mutate(
    efmod1 = pred11 - pred01,
    efmod2 = pred12 - pred02,
    efmod3 = pred13 - pred03,
    efmod4 = pred14 - pred04,
    efmod5 = pred14 - pred05
  )

ate <- preddt %>%
  summarize_at(
    vars(starts_with("efmod")),
    list(~ mean(., na.rm = TRUE))
  ) %>%
  mutate(estimand = "ATE")

preddt %>%
  group_by(ext_benefit_tl) %>%
  summarize_at(
    vars(starts_with("efmod")),
    list(~mean(., na.rm = TRUE))
  ) %>%
  mutate(estimand = if_else(ext_benefit_tl == 1, "ATT", "ATU")) %>%
  select(-ext_benefit_tl) %>%
  bind_rows(ate) %>%
  pivot_longer(
    -estimand,
    names_to = "model", names_prefix = "efmod",
    values_to = "effect"
  ) %>%
  mutate(model = sprintf("(%1s)", model)) %>%
  datasummary(
    model * effect ~ rawvalue * estimand,
    data = .,
    fmt = 3
  ) %>%
  kableExtra::kable_styling()
```


# Welfare Analysis by @Almunia2020

```{r }
apemod <- list(
  "(1)" = fixest::xpd(i_total_giving ~ price + ..fullx),
  "(2)" = fixest::xpd(i_total_giving ~ price + gr_pool + ..fullx),
  "(3)" = fixest::xpd(i_total_giving ~ price * gr_pool + ..fullx),
  "(4)" = fixest::xpd(i_total_giving ~ price + gr_sep + ..fullx),
  "(5)" = fixest::xpd(i_total_giving ~ price * gr_sep + ..fullx)
)

est_apemod0 <- apemod %>%
  purrr::map(~ fixest::feols(
    .,
    data = subset(estdf, ext_benefit_tl == 0 & i_ext_giving == 1),
    cluster = ~panelid, se = "cluster"
  ))

est_apemod0 %>%
  modelsummary(
    title = "Partial Effect of Price (Subsets with R = 0)",
    coef_map = c(
      "price" = "First price",
      "log_pinc_all" = "log(income)",
      "price:gr_pool" = "First price x Correction term",
      "price:gr_sep" = "First price x Correction term",
      "gr_pool" = "Correction term",
      "gr_sep" = "Correction term"
    ),
    gof_omit = "^(?!R2 Adj.|FE|N|Std.Errors)",
    stars = c("*" = .1, "**" = .05, "***" = .01),
    add_rows = tribble(
      ~term, ~"(1)", ~"(2)", ~"(3)", ~"(4)", ~"(5)",
      "Square age", "X", "X", "X", "X", "X",
      "Method of IMR", "", "Pooled", "Pooled", "Separate", "Separate"
    )
  ) %>%
  kableExtra::kable_styling() %>%
  footnote(
    general_title = "",
    general = paste(
      "Notes: $^{*}$ $p < 0.1$, $^{**}$ $p < 0.05$, $^{***}$ $p < 0.01$.",
      "Standard errors are clustered at individual level."
    ),
    threeparttable = TRUE,
    escape = FALSE
  )
```



```{r }
elast <- est_basemod1 %>%
  purrr::map(function(x) {
    tidy(x) %>%
      dplyr::filter(term == "log_price") %>%
      dplyr::select("elast" = estimate)
  }) %>%
  reduce(bind_rows) %>%
  mutate(model = names(est_basemod1))

partef <- est_apemod0 %>%
  purrr::map(function(x) {
    est <- tidy(x) %>%
      dplyr::filter(term == "price") %>%
      dplyr::select("partef" = estimate)

    n <- glance(x) %>% select(nobs)

    return(bind_cols(est, n))
  }) %>%
  reduce(bind_rows) %>%
  mutate(
    model = names(est_apemod0),
    partef = partef * nobs
  ) %>%
  dplyr::select(-nobs)

elast %>%
  left_join(partef, by = "model") %>%
  mutate(g1 = with(
    subset(df, ext_benefit_tl == 1),
    sum(i_total_giving, na.rm = TRUE)
  )) %>%
  mutate(
    devide = partef / g1,
    elast = abs(elast)
  ) %>%
  datasummary(
    model ~ (` ` = rawvalue) * (
      (`Elasticity (R = 1)` = elast) +
      (`Partial Effect (R = 0)` = partef) +
      (`Sum of Giving (R = 1)` = g1) +
      (`Partial Effect (R = 0) / Sum of Giving (R = 1)` = devide)),
    data = .,
    fmt = 3
  ) %>%
  kableExtra::kable_styling() %>%
  footnote(
    general_title = "",
    general = paste(
      "Partial effect for R = 0 is multiplied by observations."
    ),
    threeparttable = TRUE,
    escape = FALSE
  )
```


